### 2016-02-15 notes/Eigenvector_algorithm.tex
Added notes file.

\documentclass[11pt]{amsart}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}

\title{\LaTeX}
\date{}

\def\R{\mathbb{R}}
\def\T{\mathbb{T}}

\begin{document}

\begin{center}
Eigen-vector and Eigen-value Calculation Algorithm
\end{center}

\section{Method}
Each matrix has a unique QR factorization (check on this). The method used for computing the eigen-* of a symmetric matrix is with a repeated computation of QR decompositions. A given matrix $A$ can be represented in its decomposted form $A = QR$. Then $Q'AQ = RQ$ ($Q' = Q^{-1}$). Representing $A_1 = RQ$ and iteratively repeating the process will eventually converge to a diagonal matrix whose diagonal represents the eigen-values and the product of the $Q_i$ terms on the right represents the respective eigen-vectors.  Proofs of these statements can be found in any standard text on or relating to numerical linear algebra.

The method used here for QR Factorization is with Householder reflections.

\section{QR Factorization}
The collision operator of the boltzmann equation is

\begin{equation}
\label{BoltzmannRHS}
\int_{\mathbb{R}^3} \int_0^{2 \pi} \int_0^{\frac{\pi}{2}} \left( f' f_1' - f f_1 \right) \sigma g sin(\theta) d \theta d \epsilon d u'
\end{equation}
%
Where $g$ is the relative velocity of colliding molecules and $\sigma = b/(sin(\theta) \frac{\partial \theta}{\partial b})$ is the differential cross section where $b$ is the radius of the molecule.
\begin{equation*}
f_m \int_{\mathbb{R}^3} \int_0^{2 \pi} \int_0^{\frac{\pi}{2}} f_{M1} \sigma g sin(\theta) d \theta d \epsilon d u' - f \int_{\mathbb{R}^3} \int_0^{2 \pi} \int_0^{\frac{\pi}{2}} f_1 \sigma g sin(\theta) d \theta d \epsilon d u'
\end{equation*}
%

\end{document}

### 2016-05-14 notes/paper/paper.tex
Updated the paper tex document template. Now have the basic skeleton with some content.

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{pinyin}
\usepackage{natbib}
%
\begin{document}
%
% paper title
\title{Classifying Activities Using Body-Worn Accelerometers for Real-Time Application}
%
\author{Craig~Euler, C.T. Lin, Melissa Flores, et al.}
%
% make the title area
\maketitle
%
\begin{abstract}
Body worn sensors have been used in the market for many years now. Most of which are used specifically for activity monitoring or fitness. In this paper, we present a method for real-time activity classification, from accelerometers worn by the user, by using the matched-filter method. We also discuss the methods used to improve computational efficiency, and the unsupervised learning method for training the device to recognize motion patterns provided by the user.
\end{abstract}
%
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}
\IEEEpeerreviewmaketitle
%
\section{Introduction}
Body worn sensors have been used in the market for many years now. Most of which are used specifically for activity monitoring or fitness. While pedometers are common and effective devices used, not many actively identify the activity of the individual for real-time processing. In this paper, we developed a method to identify the individual’s activity in real-time and feed that back to the person or device for further analysis. Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms. These devices (Fit-Bit, Apple watch, Moov, Jawbone, etc.) usually have the individual input the activity they are performing.
%
\subsection{Activity Identification}
The matched-filter method is commonly used for extracting a signal out of noisy data. We employ this method for identifying a user’s activity from data generated by body-worn accelerometers. Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set. We will discuss how we develop our set of templates for use in our matched-filter.
%
\subsection{Dimensionality Reduction}
e manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction. We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane. By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our x and y axis accordingly. Because most common activities are mostly confined to two dimensions, this will improve our signal identification.
\cite{bgk}
%
\section{Conclusion}
conclusion text here
%
\appendices
%
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
%
\bibliographystyle{plain}
\bibliography{reference}
\end{document}

### 2016-05-15 mc_code/sensor.h
Started training example code. Some modifications to the training code arguments list and to the Makefile to allow building multiple executables.

@@ -34,4 +34,17 @@ void sensor_main(
  /*[ O]*/ int        *activity,          /* Determined activity                       */
  /*[ O]*/ void       *workspace);        /* pre-allocated buffer space. Size = TBD    */
 
+void training_main(
+ /*[I ]*/ const float  sampling_freq,          /* Sampling frequency                          */
+ /*[I ]*/ const float  data_time_length,       /* data time length in seconds                 */
+ /*[I ]*/ const float  total_data_time_length, /* total time length of the incoming data      */
+ /*[I ]*/ const float *ax,                     /* Acceleration data in x                      */
+ /*[I ]*/ const float *ay,                     /* Acceleration data in x                      */
+ /*[I ]*/ const float *az,                     /* Acceleration data in x                      */
+ /*[I ]*/ const float  ref_time_length,        /* Time length for the reference               */
+ /*[ O]*/ float       *reference_x,            /* Reference x                                 */
+ /*[ O]*/ float       *reference_y,            /* Reference y                                 */
+ /*[I ]*/ const int    num_samples,            /* Number of samples to test for reference     */
+ /*[**]*/ void        *workspace);
+
 #endif

### 2016-05-15 mc_code/training_example.c

@@ -1,0 +1,40 @@
+#include "sensor.h"
+#include <stdlib.h>
+
+int main()
+{
+
+   const float sampling_freq    = 100.0f;
+   const float data_time_length = 4.0f;
+   const float total_data_time_length = 30.0f;
+   float *ax = (float*)malloc( 8000 );
+   float *ay = (float*)malloc( 8000 );
+   float *az = (float*)malloc( 8000 );
+   const float ref_time_length = 1.5f;
+   float *reference_x = (float*)malloc( (int)(ref_time_length * sampling_freq) );
+   float *reference_y = (float*)malloc( (int)(ref_time_length * sampling_freq) );
+   const int num_samples = 40;
+   void  *workspace = malloc( 20000 );
+
+training_main(
+         sampling_freq,          /* Sampling frequency                          */
+         data_time_length,       /* data time length in seconds                 */
+         total_data_time_length, /* total time length of the incoming data      */
+         ax,                     /* Acceleration data in x                      */
+         ay,                     /* Acceleration data in x                      */
+         az,                     /* Acceleration data in x                      */
+         ref_time_length,        /* Time length for the reference               */
+         reference_x,            /* Reference x                                 */
+         reference_y,            /* Reference y                                 */
+         num_samples,            /* Number of samples to test for reference     */
+         workspace);
+
+   free( ax );
+   free( ay );
+   free( az );
+   free( reference_x );
+   free( reference_y );
+   free( workspace );
+
+   return 0;
+}

### 2016-05-15 mc_code/training_main.c

@@ -10,7 +10,6 @@ void training_main(
  /*[I ]*/ const float  sampling_freq,          /* Sampling frequency                          */
  /*[I ]*/ const float  data_time_length,       /* data time length in seconds                 */
  /*[I ]*/ const float  total_data_time_length, /* total time length of the incoming data      */
- /*[I ]*/ const float  time_inc,               /* Time increment for next energy calculation  */
  /*[I ]*/ const float *ax,                     /* Acceleration data in x                      */
  /*[I ]*/ const float *ay,                     /* Acceleration data in x                      */
  /*[I ]*/ const float *az,                     /* Acceleration data in x                      */

### 2016-05-15 mc_code/training_example.c
Created training example code.

@@ -1,5 +1,9 @@
+#include "unit_test.h"
 #include "sensor.h"
 #include <stdlib.h>
+#include <stdio.h>
+
+#define TWO_PI 6.283185307179586f
 
 int main()
 {
@@ -7,16 +11,43 @@ int main()
    const float sampling_freq    = 100.0f;
    const float data_time_length = 4.0f;
    const float total_data_time_length = 30.0f;
-   float *ax = (float*)malloc( 8000 );
-   float *ay = (float*)malloc( 8000 );
-   float *az = (float*)malloc( 8000 );
+   float *ax = (float*)malloc( 20000 );
+   float *ay = (float*)malloc( 20000 );
+   float *az = (float*)malloc( 20000 );
    const float ref_time_length = 1.5f;
-   float *reference_x = (float*)malloc( (int)(ref_time_length * sampling_freq) );
-   float *reference_y = (float*)malloc( (int)(ref_time_length * sampling_freq) );
-   const int num_samples = 40;
-   void  *workspace = malloc( 20000 );
+   float *reference_x = (float*)malloc( 600 );
+   float *reference_y = (float*)malloc( 600 );
+   const int num_samples = 4;
+   void  *workspace = malloc( 200000 );
 
-training_main(
+   /*
+   ** Example data set
+   */
+   sinwave(
+       ax,
+       TWO_PI * 4.0f, // omega
+       0.0f,          // phase
+       1.0f,          // amplitude
+       total_data_time_length,
+       sampling_freq);
+
+   sinwave(
+       ay,
+       TWO_PI * 4.0f, // omega
+       0.0f,          // phase
+       1.0f,          // amplitude
+       total_data_time_length,
+       sampling_freq);
+
+   sinwave(
+       az,
+       TWO_PI * 4.0f, // omega
+       0.0f,          // phase
+       1.0f,          // amplitude
+       total_data_time_length,
+       sampling_freq);
+
+   training_main(
          sampling_freq,          /* Sampling frequency                          */
          data_time_length,       /* data time length in seconds                 */
          total_data_time_length, /* total time length of the incoming data      */

### 2016-05-15 notes/paper/paper.tex
Added more to the paper.

@@
 %
+\section{System Hardware}
+The sensor used for this analysis is a three-axis accelerometer unit from Kinetisense.
+The unit’s acceleration range is -5g to +5g with a sampling rate of 128Hz.
+Samples of walking, sitting, running, and bicycling have been recorded with the device and used for the analysis in this paper.
+%
 \subsection{Activity Identification}
@@
 %
+\section{Training the Module}
+Each person has a unique physical signature for each physical activity they perform.
+For our application, we develop a reference signature for our matched filter directly from the person’s motion signature.
+We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
+For a given activity, we attempt to find the representative periodic signal s of our individual’s activity to be our template.
+We assume there is a close enough representative signal s’ = s + e’ to be taken over some pre-set finite length interval I present in our training set X.
+Because the activities we are interested in classifying are periodic and range closely around 1.0 seconds we choose an interval I near 1.0 seconds.
+We divide our training set X into N sub intervals ${s_1, s_2, …, s_N}$ and we test each one against all the other ones.
+%
 \section{Conclusion}

### 2016-05-16 notes/paper/paper.tex
added more to the paper

@@
 \begin{abstract}
-Body worn sensors have been used in the market for many years now.
-Most of which are used specifically for activity monitoring or fitness.
-In this paper, we present a method for real-time activity classification, from accelerometers worn by the user, by using the matched-filter method.
-We also discuss the methods used to improve computational efficiency, and the unsupervised learning method for training the device to recognize motion patterns provided by the user.
+Body worn sensors have been used in the market for many years now. Many of which are used 
+for activity monitoring or fitness. In this paper, we present a method for real-time activity 
+classification using a matched-filter algorithm from data obtained with three-axis accelerometers 
+worn by the user.
+We achieve invariance to sensor orientation and improve computational efficiency 
+with dimensionality reduction. An instance-based learning algorithm is used to train 
+the device to learn the individual's motion patterns.
 \end{abstract}
@@
 Most of which are used specifically for activity monitoring or fitness. 
-While pedometers are common and effective devices used, not many actively identify the activity of the individual for real-time processing.
-In this paper, we developed a method to identify the individual’s activity in real-time and feed that back to the person or device for further analysis.
-Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
-These devices (Fit-Bit, Apple watch, Moov, Jawbone, etc.) usually have the individual input the activity they are performing.
+While pedometers are common and effective devices used, not many actively identify the activity 
+of the individual for real-time processing. In this paper, we developed a method to 
+identify the individual’s activity in real-time and feed that back to the person or device 
+for further analysis. Having an a priori knowledge of the activity the individual is performing 
+is useful for many current fitness algorithms. These devices (Fit-Bit, Apple watch, Moov, 
+Jawbone, etc.) usually have the individual input the activity they are performing.
 %
@@
 The unit’s acceleration range is -5g to +5g with a sampling rate of 128Hz. 
-Samples of walking, sitting, running, and bicycling have been recorded with the device and used for the analysis in this paper.
+Samples of walking, sitting, running, and bicycling have been recorded with the device 
+and used for the analysis in this paper.
 %
@@
 We employ this method for identifying a user’s activity from data generated by body-worn accelerometers. 
-Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
-We will discuss how we develop our set of templates for use in our matched-filter.
+Because the matched-filter method requires use of an existing reference template to identify the desired 
+signal, we must develop our template from a training set. We will discuss how we develop our set of 
+templates for use in our matched-filter.
 %
 \subsection{Dimensionality Reduction}
-e manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
-We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.
-By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our x and y axis accordingly.
-Because most common activities are mostly confined to two dimensions, this will improve our signal identification.
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the 
+same time through a process of dimensionality reduction. We base our assumption that over a short period 
+of time a user’s limb movement is constrained mostly to a two-dimensional plane. 
+By identifying the plane of motion, we then project the acceleration data onto this plane and re-define 
+our x and y axis accordingly. Because most common activities are mostly confined to two dimensions, 
+this will improve our signal identification.
 \cite{bgk}
@@
 Each person has a unique physical signature for each physical activity they perform. 
-For our application, we develop a reference signature for our matched filter directly from the person’s motion signature.
-We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal s of our individual’s activity to be our template.
-We assume there is a close enough representative signal s’ = s + e’ to be taken over some pre-set finite length interval I present in our training set X.
-Because the activities we are interested in classifying are periodic and range closely around 1.0 seconds we choose an interval I near 1.0 seconds.
-We divide our training set X into N sub intervals ${s_1, s_2, …, s_N}$ and we test each one against all the other ones.
+For our application, we develop a reference signature for our matched filter directly from the 
+person’s motion signature. We do this by having the individual perform the specific activity 
+over a specified amount of time and select the sub-interval of time that we find best represents 
+the user's motion signature. For a given activity, we attempt to find the representative periodic 
+signal s of our individual’s activity to be our template. We assume there is a close enough 
+representative signal s’ = s + e’ to be taken over some pre-set finite length interval I present 
+in our training set X. Because the activities we are interested in classifying are periodic and 
+range closely around 1.0 seconds we choose an interval I near 1.0 seconds. We divide our training 
+set X into N sub intervals ${s_1, s_2, …, s_N}$ and we test each one against all the other ones.
 %

### 2016-05-23 notes/paper/paper.tex
Arranged text lines in paper to one line.

--- 2016-05-15 notes/paper/paper.tex
@@
 Body worn sensors have been used in the market for many years now.
-Most of which are used specifically for activity monitoring or fitness.
-In this paper, we present a method for real-time activity classification, from accelerometers worn by the user, by using the matched-filter method.
-We also discuss the methods used to improve computational efficiency, and the unsupervised learning method for training the device to recognize motion patterns provided by the user.
+Many of which are used for activity monitoring or fitness.
+In this paper, we present a method for real-time activity classification using a matched-filter algorithm from data obtained with three-axis accelerometers worn by the user.
+We achieve invariance to sensor orientation and improve computational efficiency with dimensionality reduction.
+An instance-based learning algorithm is used to train the device to learn the individual's motion patterns.
 \end{abstract}
@@
 \subsection{Dimensionality Reduction}
-e manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
 We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.

### 2016-05-23 notes/paper/paper.tex
Added more to the paper.

--- 2016-05-15 notes/paper/paper.tex
@@
 \usepackage{natbib}
+\usepackage{notoccite}
+\usepackage{amssymb}
 %
@@
 % paper title
-\title{Classifying Activities Using Body-Worn Accelerometers for Real-Time Application}
+\title{Real-Time Application of Activity Classification from Body-Worn Accelerometers}
 %
-\author{Craig~Euler, C.T. Lin, Melissa Flores, et al.}
+\author{Craig~Euler, C.T. Lin, Melissa Flores, et al? (Ruben, Brian, Sydney, Steve?)}
 %
@@
 Body worn sensors have been used in the market for many years now.
-Most of which are used specifically for activity monitoring or fitness.
-In this paper, we present a method for real-time activity classification, from accelerometers worn by the user, by using the matched-filter method.
-We also discuss the methods used to improve computational efficiency, and the unsupervised learning method for training the device to recognize motion patterns provided by the user.
+Many of which are used for activity monitoring or fitness.
+In this paper, we make use of a matched-filtering algorithm for real-time activity classification from data obtained with three-axis accelerometers worn by the user.
+We achieve invariance to sensor orientation with dimensionality reduction.
+We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity filters for our matched filter.
+We improve computational efficiency with dimensionality reduction, temporal decomposition, and pre-processing of our filters for later use.
+An assessment of our computational costs are provided as processing flop counts for the real-time specific parts of the algorithms.
 \end{abstract}
@@
 \section{Introduction}
-Body worn sensors have been used in the market for many years now.
-Most of which are used specifically for activity monitoring or fitness.
-While pedometers are common and effective devices used, not many actively identify the activity of the individual for real-time processing.
-In this paper, we developed a method to identify the individual’s activity in real-time and feed that back to the person or device for further analysis.
+Various methods for activity classification exist.
+Custom dicision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
+In this paper, we employ the use of a matched-filter method to identify an individual’s activity in real-time.
+The matched-filtering method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
+Computational resources are limited on micro-processors so we've designed our algorithms to be as efficient as possible.
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
@@
 %
-\section{System Hardware}
-The sensor used for this analysis is a three-axis accelerometer unit from Kinetisense.
-The unit’s acceleration range is -5g to +5g with a sampling rate of 128Hz.
-Samples of walking, sitting, running, and bicycling have been recorded with the device and used for the analysis in this paper.
-%
-\subsection{Activity Identification}
+\section{Activity Classification via Matched Filtering}
 The matched-filter method is commonly used for extracting a signal out of noisy data.
@@
 %
-\subsection{Dimensionality Reduction}
-e manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
-We base our assumption that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.
-By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our x and y axis accordingly.
-Because most common activities are mostly confined to two dimensions, this will improve our signal identification.
-\cite{bgk}
+\section{Dimensionality Reduction}
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
+We assume that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.
+By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our $x$ and $y$ axis accordingly.
+By this assumption, activities that are mostly confined to two dimensions will improve our signal identification.
+
+If we let $\{\vec{a}_i\}_{i=0}^{N}$ represent our demeaned acceleration data over some time window $T$ in $\mathbb{R}^3$ then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \vec{a} \vec{a}^T$.
+The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some text book here].
+By projecting our data on the plain defined by the two most dominant eigen vectors, we've effectively reduced our representation of our data to two dimensions.
 %
@@
 %
+\section{System Hardware}
+The sensor used for this analysis is a three-axis accelerometer unit from Kinetisense.
+The unit’s acceleration range is -5g to +5g with a sampling rate of 128Hz.
+Samples of walking, sitting, running, and bicycling have been recorded with the device and used for the analysis in this paper.
+%
+\section{Algorithm Software Structure}
+%
+The algorithms are broken into three main modules: The training, pre-processing of the data used as references for the matched filtering, and the activity classification itself.
+
+The training module, like the pre-processing module, does not need to be in real time.
+This algorithm is the most demanding on computational resources and is rarely ran so this can be performed on a smart phone or tablet.
+The purpose of the training module is to derive the reference signal to be used on the micro-controller for real-time processing.
+The training process uses the same algorithm kernels as the activity classification.
+%
+\section{Results}
+%
+ROC curves, timing results?, flop counts.
+%
 \section{Conclusion}
-conclusion text here
+conclusion text.
 %

### 2016-05-25 notes/paper/paper.tex
Remove *~ files with make clean capability added to the Makefile. Updated the source paper.tex file to break up the paragraph's sentences into individual lines for easier diff tracking with Git.
updates to the paper.

@@
 \usepackage{amssymb}
+\usepackage{textcomp}
 %
@@
 \end{abstract}
-%
-\begin{IEEEkeywords}
-IEEEtran, journal, \LaTeX, paper, template.
-\end{IEEEkeywords}
-\IEEEpeerreviewmaketitle
 %
@@
 \section{Training the Module}
-Each person has a unique physical signature for each physical activity they perform.
-For our application, we develop a reference signature for our matched filter directly from the person’s motion signature.
+We are able to identify an individual\textquotesingle's activity by matching the signal to a reference template.
+For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle’s motion signature.
 We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
 For a given activity, we attempt to find the representative periodic signal s of our individual’s activity to be our template.
-We assume there is a close enough representative signal s’ = s + e’ to be taken over some pre-set finite length interval I present in our training set X.
-Because the activities we are interested in classifying are periodic and range closely around 1.0 seconds we choose an interval I near 1.0 seconds.
-We divide our training set X into N sub intervals ${s_1, s_2, …, s_N}$ and we test each one against all the other ones.
 %

### 2016-05-29 code/matchedfilter/matchedfilter.cpp
In the process of adding the downsample factor to the C++ version of the code.

@@ -1,6 +1,7 @@
 #include "matchedfilter.h"
 #include "taper.h"
 #include "filter.h"
+#include "down_sample.h"
 #include <iostream>
 #include <string>
 #include <fstream>
@@ -49,6 +50,39 @@ static float norm_ref( float *reference,
 /******************************************************************************/
 
 /*
+** Function NAME: downsample
+*/
+void matchedfilter::downsample(int   downsample_factor,
+                               MEMORY mem_buffer)
+{
+
+   if (downsample_factor <= 1) return;
+
+   float l_sampling_freq;
+
+   float *workspace = mem_buffer.allocate_float( 2 * downsample_factor );
+
+   l_sampling_freq = down_sample (ref_ax,
+                                  samp_freq_ref,
+                                  time_window_ref,
+                                  downsample_factor,
+                                  workspace);
+
+   l_sampling_freq = down_sample (ref_ax,
+                                  samp_freq_ref,
+                                  time_window_ref,
+                                  downsample_factor,
+                                  workspace);
+
+   samp_freq_ref = l_sampling_freq;
+   N_window_ref /= downsample_factor;
+   dt_ref       *= downsample_factor;
+
+}
+
+/******************************************************************************/
+
+/*
  * Constructor NAME: matchedfilter
  */
 matchedfilter::matchedfilter (int N_data, int activity_ID_in)
@@ -84,12 +118,12 @@ void matchedfilter::load_ref (float *ax_in, float *ay_in,
    dt_ref          = dt_in;
    samp_freq_ref   = samp_freq_in;
 
-   for (int k=0; k<N_window_ref; k++) {
+   for (int k = 0; k < N_window_ref; k++) {
       ref_ax[k] = ax_in[k];
       ref_ay[k] = ay_in[k];
    }
 
-   for (int k=N_window_ref; k<N_data_ref; k++) {
+   for (int k = N_window_ref; k < N_data_ref; k++) {
       ref_ax[k] = 0.0;
       ref_ay[k] = 0.0;
    }

### 2016-05-29 code/matchedfilter/matchedfilter.h

@@ -18,28 +18,21 @@ class matchedfilter {
                      float time_window_in, int N_window_in, int N_data_in);
 
       float *access_ax (void);
-
       float *access_ay (void);
-
-      float get_norm_ax (void);
-
-      float get_norm_ay (void);
-
-      void set_correlation (float corr);
-
-      float get_correlation (void); // Return correlation in x
-
-      int get_N_window (void);
-
-      void set_ID(int);  // set the activity ID
-      int  get_ID(void); // get the activity ID
-
-      bool write(std::string); // write the data to file
-
-      void write_corr (std::string file,
-                       bool initial_write);
+      float  get_norm_ax (void);
+      float  get_norm_ay (void);
+      void   set_correlation (float corr);
+      float  get_correlation (void); // Return correlation in x
+      int    get_N_window (void);
+      void   set_ID(int);  // set the activity ID
+      int    get_ID(void); // get the activity ID
+      bool   write(std::string); // write the data to file
+      void   write_corr (std::string file,
+                         bool initial_write);
 
       void print_all (void);
+      void downsample(int   downsample_factor,
+                      MEMORY mem_buffer);
 
       void apply_taper (float *taper_buff,
                         float cutoff_freq,

### 2016-05-29 code/mf_main.cpp

@@ -71,6 +71,9 @@ int main(int argc, char *argv[]) {
       ref_path = InRefs.get_ref_path(i_ref);
       MF = new matchedfilter (ref_path.c_str(), N_window);
 
+      MF->downsample( PARAMETERS.get_downsample_factor(),
+                      mem_buffer);
+
       MF->filter (
           NUM_TENT_FILT_POINTS,
           mem_buffer);

### 2016-05-29 code/utilities/down_sample.cpp

@@ -1,0 +1,33 @@
+#include "down_sample.h"
+#include <stdio.h>
+
+int down_sample (float *data,
+                 float  sampling_freq,
+                 float  time_length,
+                 int    downsamp_fact,
+                 float *workspace)
+{
+
+   if (downsamp_fact <= 1) return sampling_freq;
+
+   sampling_freq /= (float)downsamp_fact;
+   float *weights = workspace;
+   int window = 2 * downsamp_fact - 1;
+   int ind, new_ind, k;
+   int N = (int)(sampling_freq * time_length);
+   float norm = 1.0f / (float)(downsamp_fact * downsamp_fact);
+
+   for (k = 0; k <= window / 2; k++) weights[k] = (float)(k + 1);
+   for (k = 0, ind = window - 1; k < window / 2; k++, ind--) weights[ind] = (float)(k + 1);
+   for (k = 0; k < window ; k++) weights[k] *= norm;
+
+   float val;
+   for (new_ind = 0, ind = 0; new_ind < N; ind += downsamp_fact, new_ind++)
+   {
+      val = 0.0f;
+      for (k = 0; k < window; k++) val += data[ind + k] * weights[k];
+      data[new_ind] = val;
+   }
+
+   return sampling_freq;
+}

### 2016-05-29 code/utilities/down_sample.h

@@ -1,0 +1,10 @@
+#ifndef DOWN_SAMPLE_H
+#define DOWN_SAMPLE_H
+
+int down_sample (float *data,
+                 float  sampling_freq,
+                 float  time_length,
+                 int    downsamp_fact,
+                 float *workspace);
+
+#endif

### 2016-05-29 code/utilities/fileio.cpp

@@ -295,6 +295,7 @@ namespace fio {
     ref_path      = get_parameter_s   ("ref_path"   ); // used for training
     activity_ID   = get_parameter_s   ("activity_ID"); // used for training
     select_sensor = get_parameter_i   ("sensor"     ); // which sensor to use
+    downsample_factor = get_parameter_i ("downsample_factor");
 
     b_tag         = (tag         != "-1")  ? true : false;
     b_time_window = (time_window >= 0.0f)  ? true : false;
@@ -311,6 +312,7 @@ namespace fio {
     b_ref_path    = (ref_path    != "-1")  ? true : false;
     b_activity_ID = (activity_ID != "-1")  ? true : false;
     b_select_sensor = (select_sensor >= 0) ? true : false;
+    b_downsample_factor = (downsample_factor >= 0) ? true : false;
 
     input.close();
 
@@ -348,6 +350,7 @@ namespace fio {
     if (b_activity_ID) std::cout << "activity_ID = " << activity_ID << std::endl;
     if (b_samp_freq)   std::cout << "dt          = " << dt          << std::endl;
     if (b_taper)       std::cout << "applying data smoothing"       << std::endl;
+    if (b_downsample_factor) std::cout << "downsample factor = " << downsample_factor << std::endl;
                        std::cout << "Kinetisense sensor " << select_sensor << std::endl;
     std::cout << std::endl;
 
@@ -648,12 +651,24 @@ namespace fio {
     return sex;
  }
 
+/******************************************************************/
+
  /*
   * Function NAME: get_sensor
   */
  int parameters::get_sensor (void)
  {
     return select_sensor;
+ }
+
+/******************************************************************/
+
+ /*
+  * Function NAME: get_downsample_factor
+  */
+ int parameters::get_downsample_factor (void)
+ {
+    return downsample_factor;
  }
 
 /******************************************************************/

### 2016-05-29 code/utilities/fileio.h

@@ -191,6 +191,7 @@ namespace fio {
       std::string get_ref_path (void);
       std::string get_activity_ID (void);
       int         get_sensor (void);
+      int         get_downsample_factor (void);
 
    private:
 
@@ -211,6 +212,7 @@ namespace fio {
       std::string ref_path;    bool b_ref_path;
       std::string activity_ID; bool b_activity_ID;
       int   select_sensor;     bool b_select_sensor;
+      int   downsample_factor; bool b_downsample_factor;
 
       float dt;
       bool  b_taper;

### 2016-05-29 code/utilities/filter.cpp

@@ -13,9 +13,9 @@ namespace util {
  */
 
 void filter (float *data,
-                   int    points,
-                   int    N,
-                   MEMORY mem_buffer)
+             int    points,
+             int    N,
+             MEMORY mem_buffer)
 {
 
    float *z    = mem_buffer.allocate_float( N );

### 2016-05-30 code/matchedfilter/match_filt_training.cpp
Downsampling fully implemented. At this point, it appears to be working for the sensor part of the processing. The training part of the code hasn't been tested for downsampling but this is of low priority.

@@ -162,6 +162,7 @@ void match_filt_training(
                dt,
                samp_freq,
                N_window,
+               false,
                mem_buffer);
 
        sum_corr += MF->get_correlation();

### 2016-05-30 code/matchedfilter/matchedfilter.cpp

@@ -68,15 +68,23 @@ void matchedfilter::downsample(int   downsample_factor,
                                   downsample_factor,
                                   workspace);
 
-   l_sampling_freq = down_sample (ref_ax,
+   l_sampling_freq = down_sample (ref_ay,
                                   samp_freq_ref,
                                   time_window_ref,
                                   downsample_factor,
                                   workspace);
 
+std::cout << "N_window_ref = " << N_window_ref << ", N_data_ref = " << N_data_ref << std::endl;
+
    samp_freq_ref = l_sampling_freq;
    N_window_ref /= downsample_factor;
    dt_ref       *= downsample_factor;
+   N_data_ref   /= downsample_factor;
+
+std::cout << "N_window_ref = " << N_window_ref << ", N_data_ref = " << N_data_ref << std::endl;
+
+   for (int k = N_window_ref; k < N_data_ref; k++) ref_ax[k] = 0.0f;
+   for (int k = N_window_ref; k < N_data_ref; k++) ref_ay[k] = 0.0f;
 
 }
 
@@ -424,6 +432,40 @@ void matchedfilter::print_all (void)
    std::cout << "nor_ref_ax =      " << norm_ref_ax     << std::endl;
    std::cout << "norm_ref_ay =     " << norm_ref_ay     << std::endl;
    std::cout << "correlation =     " << correlation     << std::endl;
+}
+
+/******************************************************************************/
+
+/*
+** Function NAME: print_reference_x
+*/
+void matchedfilter::print_reference_x (void)
+{
+
+   std::cout << "reference_x = ";
+   for (int k = 0; k < N_data_ref; k++)
+   {
+      std::cout << ref_ax[k] << ", ";
+   }
+   std::cout << std::endl;
+
+}
+
+/******************************************************************************/
+
+/*
+** Function NAME: print_reference_y
+*/
+void matchedfilter::print_reference_y (void)
+{
+
+   std::cout << "reference_x = ";
+   for (int k = 0; k < N_data_ref; k++)
+   {
+      std::cout << ref_ay[k] << ", ";
+   }
+   std::cout << std::endl;
+
 }
 
 /******************************************************************************/

### 2016-05-30 code/matchedfilter/matchedfilter.h

@@ -31,6 +31,8 @@ class matchedfilter {
                          bool initial_write);
 
       void print_all (void);
+      void print_reference_x (void);
+      void print_reference_y (void);
       void downsample(int   downsample_factor,
                       MEMORY mem_buffer);
 

### 2016-05-30 code/matchedfilter/run_mf.cpp

@@ -20,6 +20,7 @@ void run_mf (matchedfilter *MF,
              float          dt,
              float          samp_freq,
              int            N_data,
+             bool           debug,
              MEMORY         mem_buffer)
 {
 
@@ -63,14 +64,10 @@ void run_mf (matchedfilter *MF,
                              cross_correlation_primary,
                              N_data);
 
-
-
    phase::phase_correlation (MF->access_ay(),
                              secondary_acceleration,
                              cross_correlation_secondary,
                              N_data);
-
-
 
    for (int k = 0; k < N_data_reference; k++)
    {
@@ -90,7 +87,6 @@ void run_mf (matchedfilter *MF,
 
    float max       = cross_correlation[0];
 
-
    for (int index = 1; index < N_data_reference; index++)
    {
       if (cross_correlation[index] > max)
@@ -100,7 +96,6 @@ void run_mf (matchedfilter *MF,
 
       }
    }
-
 
    float correlation = sqrtf( max );
 

### 2016-05-30 code/matchedfilter/run_mf.h

@@ -9,6 +9,7 @@ void run_mf (matchedfilter *MF,
              float          dt,
              float          samp_freq,
              int            N_data,
+             bool           debug,
              MEMORY         mem_buffer);
 
 #endif

### 2016-05-30 code/mf_main.cpp

@@ -17,6 +17,7 @@
 #include "taper.h"
 #include "filter.h"
 #include "run_mf.h"
+#include "down_sample.h"
 #include "define_parameters.h"
 
 extern "C" {
@@ -40,6 +41,8 @@ int main(int argc, char *argv[]) {
    std::string data_path   = PARAMETERS.get_data_path();
    float start_time      = 0.0f;
    int   N_window        = PARAMETERS.get_N_window();
+   int   downsample_factor = PARAMETERS.get_downsample_factor();
+   int N_window_downsampled = N_window / downsample_factor;
    float *ax             = new float[N_window + 2];
    float *ay             = new float[N_window + 2];
    float *az             = new float[N_window + 2];
@@ -54,7 +57,7 @@ int main(int argc, char *argv[]) {
    int   select_sensor;
    matchedfilter *MF;
 
-   MEMORY mem_buffer(6 * (N_window + 2));
+   MEMORY mem_buffer((100 + 6) * (N_window + 2));
 
    /* Setup Kinetisense data */
 
@@ -71,14 +74,20 @@ int main(int argc, char *argv[]) {
       ref_path = InRefs.get_ref_path(i_ref);
       MF = new matchedfilter (ref_path.c_str(), N_window);
 
+      std::cout << "before downsample:" << std::endl;
+      MF->print_reference_x();
+
       MF->downsample( PARAMETERS.get_downsample_factor(),
                       mem_buffer);
+
+      std::cout << "after downsample:" << std::endl;
+      MF->print_reference_x();
 
       MF->filter (
           NUM_TENT_FILT_POINTS,
           mem_buffer);
 
-      MF->apply_fft(N_window);
+      MF->apply_fft(N_window_downsampled);
       MF_activities.append ( MF );
 
    }
@@ -87,6 +96,9 @@ int main(int argc, char *argv[]) {
 
    TIME preproc_time    ( -1 );
    TIME match_filt_time ( -1 );
+
+   // TODO: re-work down_sample function to properly handle the memory management object
+   float *float_workbuffer = mem_buffer.allocate_float( N_window );
 
    /* Iterate through the data */
 
@@ -102,8 +114,25 @@ int main(int argc, char *argv[]) {
       /*
        * PRE-PROCESSING
        */
-
       preproc_time.start();
+
+      down_sample(ax,
+                  PARAMETERS.get_samp_freq(),
+                  PARAMETERS.get_time_window(),
[…]

### 2016-05-30 code/preprocessing/preproc.cpp

@@ -38,6 +38,9 @@ void preproc(
 
    float dt        = PARAMETERS->get_dt();
    float window    = PARAMETERS->get_time_window();
+   int   downsample_factor = PARAMETERS->get_downsample_factor();
+
+   dt *= downsample_factor;
 
    /* Demean the data */
 

### 2016-05-30 code/utilities/fileio.cpp

@@ -318,6 +318,7 @@ namespace fio {
 
     // defaults
     if ( !b_select_sensor ) select_sensor = 2;
+    if ( !b_downsample_factor ) downsample_factor = 1;
 
     if (b_samp_freq) dt = 1.0f / samp_freq; else dt = -1.0f; // seconds
     b_taper        = (b_cutoff_freq) ? true : false;

### 2016-05-30 code/utilities/memory_management.cpp

@@ -25,12 +25,15 @@ float *MEMORY::allocate_float (size_t N)
    /*
    ** Check if there is enough allocated memory
    */
+   size_t memory_left = N_floats - (size_t)(float_ptr - float_ptr_base);
 
-   if ( N > N_floats - (size_t)(float_ptr - float_ptr_base) )
+   if ( N > memory_left )
    {
-      std::cout << "Error: Attempting to reserve more memory " <<
-                   "than what has been allocated."             <<
-                   std::endl;
+      std::cout << "Error: Attempting to reserve more memory (" << N << ")" <<
+                   "than what is left ( " << memory_left <<
+                   " floats) from the total (" << N_floats << " floats)."
+                   << std::endl;
+
       return NULL;
 
    } else {

### 2016-05-30 code/matchedfilter/matchedfilter.cpp
Cleaned up some unnecessary print statements.

@@ -74,14 +74,10 @@ void matchedfilter::downsample(int   downsample_factor,
                                   downsample_factor,
                                   workspace);
 
-std::cout << "N_window_ref = " << N_window_ref << ", N_data_ref = " << N_data_ref << std::endl;
-
    samp_freq_ref = l_sampling_freq;
    N_window_ref /= downsample_factor;
    dt_ref       *= downsample_factor;
    N_data_ref   /= downsample_factor;
-
-std::cout << "N_window_ref = " << N_window_ref << ", N_data_ref = " << N_data_ref << std::endl;
 
    for (int k = N_window_ref; k < N_data_ref; k++) ref_ax[k] = 0.0f;
    for (int k = N_window_ref; k < N_data_ref; k++) ref_ay[k] = 0.0f;

### 2016-05-30 code/mf_main.cpp

@@ -74,14 +74,8 @@ int main(int argc, char *argv[]) {
       ref_path = InRefs.get_ref_path(i_ref);
       MF = new matchedfilter (ref_path.c_str(), N_window);
 
-      std::cout << "before downsample:" << std::endl;
-      MF->print_reference_x();
-
       MF->downsample( PARAMETERS.get_downsample_factor(),
                       mem_buffer);
-
-      std::cout << "after downsample:" << std::endl;
-      MF->print_reference_x();
 
       MF->filter (
           NUM_TENT_FILT_POINTS,

### 2016-05-30 code/mf_main.cpp
Added a TODO item.

@@ -1,7 +1,3 @@
-/*
- * start_time    - seconds from start
- * N_window      - Number of data points of the signal
- */
 
 #include <iostream>
 #include <stdlib.h>

### 2016-05-30 code/utilities/down_sample.cpp

@@ -1,6 +1,7 @@
 #include "down_sample.h"
 #include <stdio.h>
 
+//TODO: Put this in its own namespace. Possibly util. And address the workspace
 int down_sample (float *data,
                  float  sampling_freq,
                  float  time_length,

### 2016-06-05 code/matchedfilter/matchedfilter.cpp
Updated some protection

@@ -353,6 +353,10 @@ float matchedfilter::get_correlation (void)
 {
    if ( correlation_computed )
    {
+      if (isnan(correlation))
+      {
+         std::cout << "correlation is NaN" << std::endl;
+      }
       return correlation;
    } else {
       std::cout << "Error: Correlations not computed yet" << std::endl;

### 2016-06-05 code/matchedfilter/run_mf.cpp

@@ -80,10 +80,17 @@ void run_mf (matchedfilter *MF,
       cross_correlation[k] *= cross_correlation[k];
    }
 
+   bool unstable = false;
    for (int k = 0; k < N_data_reference; k++)
    {
-      cross_correlation[k] /= norm_squared[k];
+      if (norm_squared[k] > 0.0001f) cross_correlation[k] /= norm_squared[k];
+      else
+      {
+         cross_correlation[k] = 0.0f;
+         unstable = true;
+      }
    }
+   if (unstable) std::cout << __FILE__ << ":Possible instability in normalization averted" << std::endl;
 
    float max       = cross_correlation[0];
 

### 2016-06-05 code/mf_main.cpp

@@ -93,8 +93,8 @@ int main(int argc, char *argv[]) {
    /* Iterate through the data */
 
    for (itt=0;
-           KIN.valid_start_end (start_time, PARAMETERS.get_time_window());
-              itt++, start_time += TIME_INC)
+        KIN.valid_start_end (start_time, PARAMETERS.get_time_window());
+        itt++, start_time += TIME_INC)
    {
 
       KIN.load_sens_ax (ax, start_time, PARAMETERS.get_sensor(), N_window);

### 2016-06-05 code/utilities/read_kinetisense.cpp

@@ -80,12 +80,18 @@ float **kinIO::read_kinetisense(
    std::ifstream kin_data;
    kin_data.open (path);
 
+   if (!kin_data.is_open())
+   {
+      std::cout << "Error: Could not open file:" << std::endl;
+      std::cout << path << std::endl;
+      return NULL;
+   }
+
    kin_data.seekg(0);
 
    /*
    **  Read the header
    */
-
    std::getline (kin_data, header);
 
    std::cout << "parsing header:" << std::endl;

### 2016-06-05 notes/paper/paper.tex
Added ROC curve image to the paper for walking vs. jogging
Added biking ROC curve to the paper.

@@
 \usepackage{textcomp}
+\usepackage{floatrow}
 %
@@
 ROC curves, timing results?, flop counts.
+\begin{figure}[!tbp]
+\RawFloats
+  \centering
+     \begin{minipage}[b]{0.45\textwidth}
+        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
+        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
+     \end{minipage}
+     \hfill
+     \begin{minipage}[b]{0.45\textwidth}
+     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
+        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
+     \end{minipage}
+\end{figure}
+%\FloatBarrier
+reference to figure \ref{ROC_walk_to_run_fig}
 %

### 2016-06-05 notes/paper/paper.tex
Added some words for the performance results.

@@
 %
-\section{Results}
+\section{Matched-Filter Performance}
 %
-ROC curves, timing results?, flop counts.
+To demonstrate how effective the matched-filter is for classification, walking, jogging, and bicycling data has been collected from a single individual.
+One instance of walking data has been used to train the classifier on and a seperate instance of walking data has been used for comparison.
+Figure \ref{ROC_walk_to_run_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_bike_fig} shows the comparison to bicycling.
+Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from for bicycling.
 \begin{figure}[!tbp]

### 2016-06-06 notes/paper/paper.tex
Added more detail to the paper. More specifically, more mathematical detail.

@@
 \usepackage{floatrow}
+\usepackage{amsmath}
 %
@@
 %
-\author{Craig~Euler, C.T. Lin, Melissa Flores, et al? (Ruben, Brian, Sydney, Steve?)}
+\author{Craig~Euler, C.T. Lin, Melissa Flores, et al? (Ruben, Bryan, Sydney, Steve?)}
 %
@@
 We will discuss how we develop our set of templates for use in our matched-filter.
+
+The matched filter is based on the cross correlation of the data $\vec{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\vec{x} = \{x\}_{k=0}^{M-1}$.
+% put this later when we refer to the convolution theorem
+If we define $\vec{x}'$ to be $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ be no more than half the length of $\vec{y}$ for preventing corruption with circular indexing, then the cross correlation of $\vec{x}$ with $\vec{y}$ is defined as:
+%
+\begin{equation} \label{cross_correlation_eq}
+(\vec{x} \star \vec{y}) = \{\sum_{i=0}^{M}(x_{i} y_{(i+k)\%N})\}_{k=0}^{N-M}
+\end{equation}
+%
+which is simply a moving dot product. Here we use $(i+k)\%N$ to represent $i+k$ modulo $N$.
+We can then normalize \eqref{cross_correlation_eq} by the following:
+%
+\begin{equation} \label{norm_cross_correlation_eq}
+\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{\sqrt{||\vec{x}|| \sum_{p=0}^M y_{p+k}^2}}
+\end{equation}
+%
+where \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has removed any biased toward high energy.
+We are most interested where our reference best matches our data. The resulting max correlation yeilds our matched-filter output:
+%
+\begin{equation} \label{matched_filter_eq}
+MF := \underset{k \in [0, M-N]}{max} \{\widehat{(\vec{x} \star \vec{y})}_k\}
+\end{equation}
 %

### 2016-06-06 notes/paper/paper.tex
Added more to the paper.

--- 2016-06-05 notes/paper/paper.tex
@@
 %
-\author{Craig~Euler, C.T. Lin, Melissa Flores, et al? (Ruben, Brian, Sydney, Steve?)}
+\author{Craig~Euler, C.T. Lin, Melissa Flores, Bryan, Ruben, Sydney, Steve}
 %
@@
 We will discuss how we develop our set of templates for use in our matched-filter.
+
+The matched filter is based on the cross correlation of the data $\vec{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\vec{x} = \{x\}_{k=0}^{M-1}$.
+The cross correlation of $\vec{x}$ with $\vec{y}$ is defined as:
+%
+\begin{equation} \label{cross_correlation_eq}
+(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{(i+k)\%N}) \right \}_{k=0}^{N-M}
+\end{equation}
+%
+which is simply a moving dot product. Here we use $(i+k)\%N$ to represent $i+k$ modulo $N$.
+We can then normalize \eqref{cross_correlation_eq} by the following:
+%
+\begin{equation} \label{norm_cross_correlation_eq}
+\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k} || }, \quad k = 0,1,...,N-M-1
+\end{equation}
+%
+where $|| \cdot ||$ is the usual $L_2$ norm. \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has any bias toward high energy removed.
+We can improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq}:
+%
+\begin{equation} \label{conv_theorem}
+(\vec{x} \star \vec{y}) = FFT^{-1}(FFT(\vec{x}') FFT(\vec{y})^*)
+\end{equation}
+%
+Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than half the length of $\vec{y}$ to prevent corruption from circular indexing.
+We are most interested where our reference best matches our data.
+The resulting max correlation yeilds our matched-filter output:
+%
+\begin{equation} \label{matched_filter_eq}
+MF := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
+\end{equation}
 %
@@
 We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal s of our individual’s activity to be our template.
+For a given activity, we attempt to find the representative periodic signal $x$ of our individual’s activity to be our template.
+
+If $\vec{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\vec{t}$:
+%
+\begin{equation} \label{subsets_of_training_eq}
+X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=nI \right \}
+\end{equation}
+%
+where $I$ is a positive, fixed integer and $n$ varies such that $0 \leq nI$ and $nI + M - 1 \leq N_t$
 %

### 2016-06-06 notes/paper/paper.tex
added more to the paper.

@@
 %
-\author{Craig~Euler, C.T. Lin, Melissa Flores, Bryan, Ruben, Sydney, Steve}
+\author{Craig~Euler, C.T. Lin, Melissa Flores, Bryan, Ruben, Sidney, Steve}
 %
@@
 Various methods for activity classification exist.
-Custom dicision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
+Custom decision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
 In this paper, we employ the use of a matched-filter method to identify an individual’s activity in real-time.
 The matched-filtering method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
-Computational resources are limited on micro-processors so we've designed our algorithms to be as efficient as possible.
+Computational resources are limited on micro-processors so we\textquotesingle ve designed our algorithms to be as efficient as possible.
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
@@
 where $|| \cdot ||$ is the usual $L_2$ norm. \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has any bias toward high energy removed.
-We can improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq}:
+We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
 %
@@
 %
-Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than half the length of $\vec{y}$ to prevent corruption from circular indexing.
+Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$ to prevent corruption from circular indexing.
 We are most interested where our reference best matches our data.
-The resulting max correlation yeilds our matched-filter output:
+The resulting max correlation yields our matched-filter output:
 %
 \begin{equation} \label{matched_filter_eq}
-MF := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
+MF(\vec{x},\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
 \end{equation}
@@
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
-We assume that over a short period of time a user’s limb movement is constrained mostly to a two-dimensional plane.
+We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
 By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our $x$ and $y$ axis accordingly.
@@
 The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some text book here].
-By projecting our data on the plain defined by the two most dominant eigen vectors, we've effectively reduced our representation of our data to two dimensions.
+By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
 %
 \section{Training the Module}
-We are able to identify an individual\textquotesingle's activity by matching the signal to a reference template.
-For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle’s motion signature.
+We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
+For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle s motion signature.
 We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal $x$ of our individual’s activity to be our template.
+For a given activity, we attempt to find the representative periodic signal $s$ of our individual’s activity to be our template for our matched-filter.
 
@@
 %
-\begin{equation} \label{subsets_of_training_eq}
-X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=nI \right \}
+\begin{equation} \label{X_subsets_of_training_eq}
+X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=mI \right \}
 \end{equation}
 %
-where $I$ is a positive, fixed integer and $n$ varies such that $0 \leq nI$ and $nI + M - 1 \leq N_t$
+and $Y$ of $\vec{t}$:
+%
+\begin{equation} \label{Y_subsets_of_training_eq}
+Y := \left \{ \{t_k\}_{k=p}^{p+N-1} | p=nI \right \}
+\end{equation}
+%
+where $M \leq N$, $I$ is a positive, fixed integer, and $(n,m) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$.
+Then we can determine the representative signal $\vec{s} \in X$ for our activity that satisfies the condition:
+%
+\begin{equation} \label{s_condition}
+\sum_{y \in Y}MF(\vec{s}, \vec{y}) \geq \sum_{y \in Y}MF(\vec{x},\vec{y}) \quad \forall \vec{x} \in X
+\end{equation}
+
+We chose this method for its simplicity and robustness against outliers in our training set.
+We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
 %
@@
 To demonstrate how effective the matched-filter is for classification, walking, jogging, and bicycling data has been collected from a single individual.
-One instance of walking data has been used to train the classifier on and a seperate instance of walking data has been used for comparison.
+One instance of walking data has been used to train the classifier on and a separate instance of walking data has been used for comparison.
 Figure \ref{ROC_walk_to_run_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_bike_fig} shows the comparison to bicycling.

### 2016-06-06 notes/paper/paper.tex
incremental changes to the paper.

@@
 \begin{equation} \label{cross_correlation_eq}
-(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{(i+k)\%N}) \right \}_{k=0}^{N-M}
+(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{i+k}) \right \}_{k=0}^{N-M-1}
 \end{equation}
 %
-which is simply a moving dot product. Here we use $(i+k)\%N$ to represent $i+k$ modulo $N$.
+which is simply a moving dot product.
 We can then normalize \eqref{cross_correlation_eq} by the following:
@@
 If we let $\{\vec{a}_i\}_{i=0}^{N}$ represent our demeaned acceleration data over some time window $T$ in $\mathbb{R}^3$ then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \vec{a} \vec{a}^T$.
-The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some text book here].
+The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
 By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.

### 2016-06-08 notes/paper/paper.tex
Added more to the paper.

@@
 \begin{equation} \label{cross_correlation_eq}
-(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{i+k}) \right \}_{k=0}^{N-M-1}
+(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
 \end{equation}
@@
 %
-Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$ to prevent corruption from circular indexing.
-We are most interested where our reference best matches our data.
-The resulting max correlation yields our matched-filter output:
+Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$.
+We are most interested where our reference $\vec{x}$ best matches our data $\vec{y}$.
+The resulting max correlation yields our matched-filter for our reference define as:
 %
 \begin{equation} \label{matched_filter_eq}
-MF(\vec{x},\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
+MF_{\vec{x}}(\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
 \end{equation}
@@
 \begin{equation} \label{s_condition}
-\sum_{y \in Y}MF(\vec{s}, \vec{y}) \geq \sum_{y \in Y}MF(\vec{x},\vec{y}) \quad \forall \vec{x} \in X
+\sum_{y \in Y}MF_{\vec{s}}(\vec{y}) \geq \sum_{y \in Y}MF_{\vec{x}}(\vec{y}) \quad \forall \vec{x} \in X
 \end{equation}
@@
 %
+% Decimation with a tent filter for throughput performance
 \section{System Hardware}

### 2016-06-13 notes/paper/paper.tex
Updated what is currently in figure 1

@@
 \usepackage{graphicx}
+\usepackage{subfig}
+\usepackage{caption}
 \usepackage[english]{babel}
@@
 % paper title
-\title{Real-Time Application of Activity Classification from Body-Worn Accelerometers}
+\title{Real-Time Activity Classification using Body-Worn Accelerometers}
 %
-\author{Craig~Euler, C.T. Lin, Melissa Flores, Bryan, Ruben, Sidney, Steve}
+\author{Craig~Euler, C.T. Lin, Melissa~Flores, Bryan~Juarez}
 %
@@
 %
-\section{Activity Classification via Matched Filtering}
+\section{Activity Classification Method}
 The matched-filter method is commonly used for extracting a signal out of noisy data.
@@
 One instance of walking data has been used to train the classifier on and a separate instance of walking data has been used for comparison.
-Figure \ref{ROC_walk_to_run_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_bike_fig} shows the comparison to bicycling.
+Figure \ref{ROC_walk_to_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_fig} shows the comparison to bicycling.
 Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from for bicycling.
-\begin{figure}[!tbp]
-\RawFloats
+%
+%\begin{figure}[!tbp]
+%\RawFloats
+%  \centering
+%     \begin{minipage}[b]{0.45\textwidth}
+%        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
+%        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
+%     \end{minipage}
+%     \hfill
+%     \begin{minipage}[b]{0.45\textwidth}
+%     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
+%        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
+%     \end{minipage}
+%\caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
+%\end{figure}
+%
+\begin{figure}[!ht]
+  %\captionsetup[subfigure]{labelformat=empty}
   \centering
-     \begin{minipage}[b]{0.45\textwidth}
-        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
-        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
-     \end{minipage}
-     \hfill
-     \begin{minipage}[b]{0.45\textwidth}
-     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
-        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
-     \end{minipage}
+  \subfloat[]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+  \quad
+  \subfloat[]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
+  \centering
+  \quad
+  \subfloat[]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+  \centering
+  \quad
+  \subfloat[]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
+  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation factor of 8}
+  \label{ROC_walk_to_fig}
 \end{figure}
+%
 %\FloatBarrier
-reference to figure \ref{ROC_walk_to_run_fig}
+reference to figure \ref{ROC_walk_to_fig}
 %

### 2016-06-13 notes/paper/paper.tex
Added decimation section among other changes.

@@
 % paper title
-\title{Real-Time Activity Classification using Body-Worn Accelerometers}
+\title{Real-Time Activity Classification using a Match-Filter with Body-Worn Accelerometers}
 %
@@
 \section{Introduction}
-Various methods for activity classification exist.
+Various methods for activity classification using body-worn sensors exist.
 Custom decision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-In this paper, we employ the use of a matched-filter method to identify an individual’s activity in real-time.
-The matched-filtering method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
-Computational resources are limited on micro-processors so we\textquotesingle ve designed our algorithms to be as efficient as possible.
+In this paper, we make use of a matched-filter method to identify an individual\textquotesingle s activity in real-time.
+The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
+Many of the algorithms and software structure were tailored to computational efficiency to accomidate the resource limitations on the MSP 432 micro-processor.
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
-These devices (Fit-Bit, Apple watch, Moov, Jawbone, etc.) usually have the individual input the activity they are performing.
+Devices such as the Fit-Bit, Apple watch, Moov, Jawbone, etc. usually have the individual actively input the activity they are performing.
+
+The algorithms described in this paper are broken into two main modules: Training the device to identify the user\textquotesingle s activity, and the real-time activity classification itself.
+
+The training module does not need to be performed in real time.
+This algorithm is the most demanding on computational resources and is only ran when training or re-training the unit to identify the user\textquotesingle s activity, so this can be performed on an external device such as a smart phone or tablet.
+The purpose of the training module is to create the reference signal to be used on the micro-controller for real-time processing.
+
+The second module is the real-time activity classification on the unit.
+This module reads in the reference(s) stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
+Both of these modules use the same principles and hence the same algorithm kernels.
 %
-\section{Activity Classification Method}
+\section{Algorithms}
+\subsection{Activity Classification Method}
 The matched-filter method is commonly used for extracting a signal out of noisy data.
-We employ this method for identifying a user’s activity from data generated by body-worn accelerometers.
+We use this method for identifying a user\textquotesingle s activity from data generated by body-worn accelerometers.
 Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
@@
 %
-\section{Dimensionality Reduction}
+\subsection{Dimensionality Reduction}
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
@@
 %
-\section{Training the Module}
+\subsection{Decimation}
+Decimation is a process of reducing the sampling rate of a signal.
+The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
+There is a tradeoff between performance and throughput when we decimate our signal, therefore We use decimation solely for the purpose of improving our throughput.
+
+For our application, we use a triangle filter prior to downsampling. This is achieved by convolving our data with the following weights:
+%
+\begin{equation} \label{trignal_filter_weights}
+w_k^N =
+\begin{cases}
+  \frac{k+1}{N^2}, & \text{if}\ 0 \leq k < N \\
+  \frac{2N - (k + 1)}{N^2}, & \text{if} N \leq k < 2N - 1
+\end{cases}
+\end{equation}
+%
+For a decimation value of $N$. Then the data is downsampled by $N$. This results in:
+%
+\begin{equation} \label{decimated_signal}
+s_k^1 = \sum_{p=0}^{2N-1} w_{p+N(1-k)}^N s_{kN - (p+1)}^0 ?
+\end{equation}
+%
+where $\{s_k^1\}_{k=0}^{M/N}$? is the decimated signal of $\{s_k^0\}_{k=0}^M$?.
+\subsection{Training the Module}
 We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
@@
 % Decimation with a tent filter for throughput performance
-\section{System Hardware}
-The sensor used for this analysis is a three-axis accelerometer unit from Kinetisense.
-The unit’s acceleration range is -5g to +5g with a sampling rate of 128Hz.
-Samples of walking, sitting, running, and bicycling have been recorded with the device and used for the analysis in this paper.
 %
-\section{Algorithm Software Structure}
+\section{Performance and Throughput}
 %
-The algorithms are broken into three main modules: The training, pre-processing of the data used as references for the matched filtering, and the activity classification itself.
-
-The training module, like the pre-processing module, does not need to be in real time.
-This algorithm is the most demanding on computational resources and is rarely ran so this can be performed on a smart phone or tablet.
-The purpose of the training module is to derive the reference signal to be used on the micro-controller for real-time processing.
-The training process uses the same algorithm kernels as the activity classification.
-%
-\section{Matched-Filter Performance}
-%
-To demonstrate how effective the matched-filter is for classification, walking, jogging, and bicycling data has been collected from a single individual.
-One instance of walking data has been used to train the classifier on and a separate instance of walking data has been used for comparison.
-Figure \ref{ROC_walk_to_fig} shows the effectiveness of the classifier when comparing walking to jogging and figure \ref{ROC_walk_to_fig} shows the comparison to bicycling.
+The Kinetisense sensor was used for the performance analysis in this paper.
+This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
+Samples of walking, jogging, and bicycling have been recorded with this unit for the purpose of analyzing the performance.
+A separate instance of walking data has been used specifically for training the classifier.
+In figure \ref{fig:MF_performance}, \subref{fig:frac_walking_jogging} and \subref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
+As we would expect, walking data matches better to walking data than the other activities.
+ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illistrate the effectiveness of the matched-filter as a classifier.
+Figure \ref{fig:MF_performance} shows the comparison to bicycling.
 Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from for bicycling.
@@
   \centering
-  \subfloat[]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
   \quad
-  \subfloat[]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
+  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
   \centering
   \quad
-  \subfloat[]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
   \centering
   \quad
-  \subfloat[]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
-  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation factor of 8}
-  \label{ROC_walk_to_fig}
+  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
+  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with a decimation factor of 8}
+  \label{fig:MF_performance}
 \end{figure}
@@
 %\FloatBarrier
-reference to figure \ref{ROC_walk_to_fig}
+reference to figure \ref{fig:MF_performance}
 %

### 2016-06-16 notes/paper/paper.tex
little things here and there.
Little changes here and there.

@@
 % paper title
-\title{Real-Time Activity Classification using a Match-Filter with Body-Worn Accelerometers}
+\title{Real-Time Activity Classification by Match Filtering using Body-Worn Accelerometers}
 %
-\author{Craig~Euler, C.T. Lin, Melissa~Flores, Bryan~Juarez}
+\author{Craig~Euler, C.T.~Lin, Bryan~Juarez}
 %
@@
 \begin{equation} \label{norm_cross_correlation_eq}
-\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k} || }, \quad k = 0,1,...,N-M-1
+\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k-1} || }, \quad k = 0,1,...,N-M-1
 \end{equation}
 %
-where $|| \cdot ||$ is the usual $L_2$ norm. \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has any bias toward high energy removed.
+where $|| \cdot ||$ is the usual $\ell_2$ norm. \eqref{norm_cross_correlation_eq} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
 We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
@@
 We are most interested where our reference $\vec{x}$ best matches our data $\vec{y}$.
-The resulting max correlation yields our matched-filter for our reference define as:
+We use the resulting max correlation to define our metric for  our matched-filter output as:
 %
 \begin{equation} \label{matched_filter_eq}
-MF_{\vec{x}}(\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
+MF_{\vec{x}}(\vec{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
 \end{equation}
@@
 \subsection{Decimation}
+Decimation is the first step applied to our data before any additional processing takes place.
 Decimation is a process of reducing the sampling rate of a signal.
 The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
-There is a tradeoff between performance and throughput when we decimate our signal, therefore We use decimation solely for the purpose of improving our throughput.
+There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of improving our throughput.
 
@@
   \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
-  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with a decimation factor of 8}
+  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation 8}
   \label{fig:MF_performance}

### 2016-06-17 notes/paper/paper.tex
Added more to the paper.

@@
 
-The matched filter is based on the cross correlation of the data $\vec{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\vec{x} = \{x\}_{k=0}^{M-1}$.
-The cross correlation of $\vec{x}$ with $\vec{y}$ is defined as:
+The matched filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
+The cross correlation of $\textbf{x}$ with $\textbf{y}$ is defined as:
 %
 \begin{equation} \label{cross_correlation_eq}
-(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
+(\textbf{x} \star \textbf{y}) = \left \{\sum_{i=0}^{M}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
 \end{equation}
@@
 \begin{equation} \label{norm_cross_correlation_eq}
-\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k-1} || }, \quad k = 0,1,...,N-M-1
+\widehat{(\textbf{x} \star \textbf{y})}_k = \frac{(\textbf{x} \star \textbf{y})_k}{||\textbf{x}|| \ || \widetilde{\textbf{y}}_k || }, \quad k = 0,1,...,N-M-1
 \end{equation}
 %
-where $|| \cdot ||$ is the usual $\ell_2$ norm. \eqref{norm_cross_correlation_eq} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
+where $|| \cdot ||$ is the usual $\ell_2$ norm and $\widetilde{\textbf{y}}_k = \{y_p\}_{p=k}^{M+k-1}$.
+\eqref{norm_cross_correlation_eq} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
 We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
@@
 \begin{equation} \label{conv_theorem}
-(\vec{x} \star \vec{y}) = FFT^{-1}(FFT(\vec{x}') FFT(\vec{y})^*)
+(\textbf{x} \star \textbf{y}) = FFT^{-1}(FFT(\textbf{x}') FFT(\textbf{y})^*)
 \end{equation}
 %
-Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$.
-We are most interested where our reference $\vec{x}$ best matches our data $\vec{y}$.
+Where $\textbf{x}'$ is $\textbf{x}$ that has been zero padded to the length of $\textbf{y}$ with the added restriction that the length of $\textbf{x}$ is no more than the length of $\textbf{y}$ and $FFT$ is the Fast Fourier Transform algorithm.
+We are most interested where our reference $\textbf{x}$ best matches our data $\textbf{y}$.
 We use the resulting max correlation to define our metric for  our matched-filter output as:
@@
 \begin{equation} \label{matched_filter_eq}
-MF_{\vec{x}}(\vec{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
+MF_{\textbf{x}}(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}_k \right \}
 \end{equation}
+%
+If \eqref{matched_filter_eq} passes a threshold, the corresponding signal is a match.
 %
@@
 We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
-By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our $x$ and $y$ axis accordingly.
+By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
 By this assumption, activities that are mostly confined to two dimensions will improve our signal identification.
 
-If we let $\{\vec{a}_i\}_{i=0}^{N}$ represent our demeaned acceleration data over some time window $T$ in $\mathbb{R}^3$ then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \vec{a} \vec{a}^T$.
+If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \textbf{a} \textbf{a}^T$.
 The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
 By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
+
+To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by the following:
 %
+\begin{equation} \label{cross_correlation_eq_2}
+\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k^2 = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
+\end{equation}
+%
+\begin{equation} \label{matched_filter_eq_2}
+MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}^2_k \right \}
+\end{equation}
+%
+for $ k = 0,1,...,N-M-1 $.\\
+%
+This works because both dimensions are always in phase with each other for a given activity
 \subsection{Decimation}
@@
 
-If $\vec{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\vec{t}$:
+If $\textbf{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\textbf{t}$:
 %
@@
 %
-and $Y$ of $\vec{t}$:
+and $Y$ of $\textbf{t}$:
 %
@@
 where $M \leq N$, $I$ is a positive, fixed integer, and $(n,m) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$.
-Then we can determine the representative signal $\vec{s} \in X$ for our activity that satisfies the condition:
+Then we can determine the representative signal $\textbf{s} \in X$ for our activity that satisfies the condition:
 %
 \begin{equation} \label{s_condition}
-\sum_{y \in Y}MF_{\vec{s}}(\vec{y}) \geq \sum_{y \in Y}MF_{\vec{x}}(\vec{y}) \quad \forall \vec{x} \in X
+\sum_{y \in Y}MF_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
 \end{equation}
@@
 Figure \ref{fig:MF_performance} shows the comparison to bicycling.
-Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from for bicycling.
+Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
 %

### 2016-06-18 notes/paper/paper.tex
Incremental changes to the paper.

@@
 
-If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \textbf{a} \textbf{a}^T$.
+If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
 The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
@@
 
-To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by the following:
+To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by augmenting our reference and data with both dimensions appropriately for normalization and adding together the cross correlations as:
 %
@@
 %
+for $ k = 0,1,...,N-M-1 $.\\
+%
 \begin{equation} \label{matched_filter_eq_2}
@@
 %
-for $ k = 0,1,...,N-M-1 $.\\
+This works because both dimensions are always in phase with each other for any given activity which means that the match will happen in sinc.
 %
-This works because both dimensions are always in phase with each other for a given activity
 \subsection{Decimation}
@@
 \begin{equation} \label{s_condition}
-\sum_{y \in Y}MF_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
+\sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
 \end{equation}

### 2016-06-20 notes/paper/paper.tex
Intermediate changes
Added more to the paper. Made python script to create timing plot.

@@
 %
-\author{Craig~Euler, C.T.~Lin, Bryan~Juarez}
+\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
 %
-% make the title area
 \maketitle
@@
 We improve computational efficiency with dimensionality reduction, temporal decomposition, and pre-processing of our filters for later use.
-An assessment of our computational costs are provided as processing flop counts for the real-time specific parts of the algorithms.
+An assessment of our computational costs are provided with runtime experiments on the MSP432 micro-controller.
 \end{abstract}
@@
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
-The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
-By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
+The resulting eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ for the respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
+%
+\begin{equation} \label{project_eq}
+   \textbf{a}' = V^T \textbf{a}
+\end{equation}
+%
+We now represent our acceleration data as $\textbf{a}'$ after rotating our axis by \eqref{project_eq}.
+We make the assumption that our data is most dominate in two dimensions i.e.
+$\lambda^3 << \lambda^2$ so it is safe to assume that
+%
+\begin{equation} \label{magnitude_eq}
+||(a^1,a^2,a^3)|| = ||(a'^1,a'^2,a'^3)|| \sim = (a'^1)^2 + (a'^2)^2
+\end{equation}
+$ \forall a \in \textbf{a}. $ \\
+%
+The margin of error in the approximation is not important since we are only interested in processing in two dimensions.
+Our goal is only to minimized the margin of error so that we are not, by chance, using an axis direction where the data varies least.
+By projecting our data onto the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
 
@@
 \begin{equation} \label{cross_correlation_eq_2}
-\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k^2 = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
+\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
 \end{equation}
@@
 \begin{equation} \label{matched_filter_eq_2}
-MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}^2_k \right \}
+MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k \right \}
 \end{equation}
 %
-This works because both dimensions are always in phase with each other for any given activity which means that the match will happen in sinc.
+This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
 %
@@
 The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
-There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of improving our throughput.
+There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of reducing our processing cost.
 

### 2016-06-20 notes/paper/make_timing_plots.py

@@ -1,0 +1,21 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+freq = np.array([25, 32, 50, 62, 64, 75, 100, 128], dtype=np.float)
+freq2 = np.array([16, 32, 62, 64, 75, 100, 128], dtype=np.float)
+
+time_dec_8 = np.array([1.039, 0.1591, 0.2516, 0.3534, 0.3132, 0.503, 0.4765, 0.6255])
+time_4sec_dec_8_1ref = np.array([0.05605, 0.0947, 0.2023, 0.1781, 0.2748, 0.2807, 0.3551])
+time_4sec_dec_8_2ref = np.array([0.0826, 0.1591, 0.3534, 0.3132, 0.503, 0.4765, 0.6255])
+
+plt.figure(figsize=(12,9))
+sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', label="1 Reference")
+sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#888888', label="2 References")
+plt.title("Timing on MSP432 w/ Decimation 8", fontsize=26)
+plt.xlabel("Sampling Frequency", fontsize=26)
+plt.ylabel("Execution Time (seconds)", fontsize=26)
+plt.yticks(fontsize=20)
+plt.xticks(fontsize=20)
+plt.legend(handles=[sec4_dec8_plot_1ref, sec4_dec8_plot_2ref], loc='upper left', prop={'size':26})
+plt.savefig("one_and_two_references.png", bbox_inches="tight")

### 2016-06-20 notes/paper/paper.tex
Incremental updates. Added textbook reference for dimensionality reduction.

@@
 \usepackage{subfig}
-\usepackage{caption}
+%\usepackage{caption}
 \usepackage[english]{babel}
@@
 Many of which are used for activity monitoring or fitness.
-In this paper, we make use of a matched-filtering algorithm for real-time activity classification from data obtained with three-axis accelerometers worn by the user.
+In this paper, we make use of a matched-filtering algorithm for real-time activity classification with data obtained from three-axis accelerometers worn by the user.
 We achieve invariance to sensor orientation with dimensionality reduction.
 We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity filters for our matched filter.
-We improve computational efficiency with dimensionality reduction, temporal decomposition, and pre-processing of our filters for later use.
+We improve computational efficiency with dimensionality reduction, decimation in time, and pre-processing of our references post training for use in the matched-filter.
 An assessment of our computational costs are provided with runtime experiments on the MSP432 micro-controller.
@@
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
-The resulting eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ for the respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
-%
+The resulting unit length eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ for the respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most \cite{bishop_2006}.
+% \ref{bishop_2006}
 \begin{equation} \label{project_eq}
@@
 %
+Equality comes from the orthonormality of $V$.
 The margin of error in the approximation is not important since we are only interested in processing in two dimensions.
@@
 %
-for $ k = 0,1,...,N-M-1 $.\\
+for $ k = 0,1,...,N-M-1 $. \\
 %
@@
 %
-% Decimation with a tent filter for throughput performance
-%
 \section{Performance and Throughput}
@@
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-Samples of walking, jogging, and bicycling have been recorded with this unit for the purpose of analyzing the performance.
+Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance.
 A separate instance of walking data has been used specifically for training the classifier.
@@
 %
+\begin{figure}[!ht]
+   \centering
+   \includegraphics[width=1.0\textwidth]{one_and_two_references.png} \label{fig:timing_refs}
+   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification purposes.
+The time window used for activity classification is 4.0 seconds}
+\end{figure}
+%
 \section{Conclusion}

### 2016-06-20 notes/paper/paper.tex
Added more to the paper.

@@
 We improve computational efficiency with dimensionality reduction, decimation in time, and pre-processing of our references post training for use in the matched-filter.
-An assessment of our computational costs are provided with runtime experiments on the MSP432 micro-controller.
+An assessment of our processing time is provided with runtime experiments on the MSP432 micro-controller which shows feasability of real-time processing capability.
 \end{abstract}
@@
 %
-\section{Algorithms}
+\section{The Algorithms}
 \subsection{Activity Classification Method}
@@
 \subsection{Dimensionality Reduction}
-We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analaysis (PCA) \cite{bishop_2006}.
 We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
-By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
-By this assumption, activities that are mostly confined to two dimensions will improve our signal identification.
+By identifying this plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
 
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
-The resulting unit length eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ for the respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most \cite{bishop_2006}.
+The resulting unit length eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
 % \ref{bishop_2006}
@@
 %
-We now represent our acceleration data as $\textbf{a}'$ after rotating our axis by \eqref{project_eq}.
+We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{project_eq}.
 We make the assumption that our data is most dominate in two dimensions i.e.
@@
 %
-Equality comes from the orthonormality of $V$.
-The margin of error in the approximation is not important since we are only interested in processing in two dimensions.
-Our goal is only to minimized the margin of error so that we are not, by chance, using an axis direction where the data varies least.
+Equality comes from the orthonormality of $V$. The margin of error in the approximation is not important since we are only interested in processing in the two dimensions.
+By now we have preserved as much information that is contained in our acceleration data as possible while also reducing our dimension from three to two.
 By projecting our data onto the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
@@
    \includegraphics[width=1.0\textwidth]{one_and_two_references.png} \label{fig:timing_refs}
-   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification purposes.
+   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification with the matched-filter.
 The time window used for activity classification is 4.0 seconds}

### 2016-06-20 notes/paper/make_timing_plots.py

@@ -12,7 +12,7 @@ time_4sec_dec_8_2ref = np.array([0.0826, 0.1591, 0.3534, 0.3132, 0.503, 0.4765, 
 plt.figure(figsize=(12,9))
 sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', label="1 Reference")
 sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#888888', label="2 References")
-plt.title("Timing on MSP432 w/ Decimation 8", fontsize=26)
+plt.title("Timing on MSP432 at Decimation 8", fontsize=26)
 plt.xlabel("Sampling Frequency", fontsize=26)
 plt.ylabel("Execution Time (seconds)", fontsize=26)
 plt.yticks(fontsize=20)

### 2016-06-23 notes/paper/paper.tex
Added Bryan's portion (raw). Still need to parse through it to fit it into the paper.

@@
 %
+MSP432 role
+The Texas Instrument - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor and is used to run the real-time activity classification algorithm.
+Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754 – compliant single – precision Floating – Point Unit (FPU).
+The FPU is important for running the real-time activity classification algorithm because it gives us the ability to represent small and large numbers.
+The alternative to an FPU would be a fixed-point, the problem with fixed-point is the dilemma between precision and range.
+For this application you need to have both and the FPU gives us that.
+The 64 kB of SRAM allows the microcontroller to have sufficient space to process the data acquired when executing the real-time activity classification algorithm.
+The 256 kB is more than enough of flash memory to store the program.
+Lastly, the clock frequency of 48 MHz allows the microcontroller to have a high performance by allowing a high number of instruction cycles that ultimately allows for faster code execution.
+%
+Execution speed process
+When testing the execution speed of the real-time activity classification algorithm on the MSP432P401R, one of the General-Purpose Input/Output (GPIO) pin was used that was connected to a simple (Light-emitted diode) LED.
+To turn on the LED that was connected to the GPIO, a 3.3 Volt is required to light up the LED.
+Therefore, before entering the algorithm that handles the real-time activity classification, the GPIO pin is initially set HIGH to 3.3 Volts which lights up the LED.
+When the real-time activity classification algorithm is finished, the GPIO is set LOW to 0 Volts immediately setting the LED off.
+The execution time is then recorded by using an oscilloscope to determine how long the GPIO was set HIGH to 3.3 Volts.
+The oscilloscope used was “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer”.
+[I can show an example of this process, but i do not know of what data.
+In other words acquired the execution speed of what? If you plan on you using this piece let me know so I can get an image of the oscilliscope displaying the execution speed.]
 \section{Conclusion}

### 2016-06-25 notes/paper/make_timing_plots.py
Incremental changes. Added another timing plot.

@@ -4,10 +4,16 @@ import matplotlib.pyplot as plt
 
 freq = np.array([25, 32, 50, 62, 64, 75, 100, 128], dtype=np.float)
 freq2 = np.array([16, 32, 62, 64, 75, 100, 128], dtype=np.float)
-
 time_dec_8 = np.array([1.039, 0.1591, 0.2516, 0.3534, 0.3132, 0.503, 0.4765, 0.6255])
 time_4sec_dec_8_1ref = np.array([0.05605, 0.0947, 0.2023, 0.1781, 0.2748, 0.2807, 0.3551])
 time_4sec_dec_8_2ref = np.array([0.0826, 0.1591, 0.3534, 0.3132, 0.503, 0.4765, 0.6255])
+
+time_window = np.array([1, 2, 3, 4, 5, 6, 7, 8, 9, 10], dtype=np.float)
+# time_freq_50hz_dec_2_2ref = np.array([0.5688, 2.017, 4.34, 3.38, 12.0, 12.15, 23.14, 5.05, 37.94, 25.26, 56.65, 19.32, 85.35, 53.0, 103.21, 11.028])
+time_freq_50hz_dec_2_2ref = np.array([0.5688, 2.017, 4.34, 3.38, 12.0, 12.15, 23.14, 5.05, 37.94, 25.26])
+time_freq_62hz_dec_2_2ref = np.array([1.676, 2.569, 6.587, 3.646, 18.5, 14.28, 35.62, 7.725, 58.65, 42.6])
+time_freq_64hz_dec_2_2ref = np.array([0.2891, 1.4227, 0.865, 1.217, 1.728, 1.904, 3.63, 2.59, 4.825, 4.155])
+time_freq_75hz_dec_2_2ref = np.array([1.132, 2.377, 9.305, 4.965, 25.82, 20.48, 50.22, 11.39, 89.52, 59.22])
 
 plt.figure(figsize=(12,9))
 sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', label="1 Reference")
@@ -19,3 +25,16 @@ plt.yticks(fontsize=20)
 plt.xticks(fontsize=20)
 plt.legend(handles=[sec4_dec8_plot_1ref, sec4_dec8_plot_2ref], loc='upper left', prop={'size':26})
 plt.savefig("one_and_two_references.png", bbox_inches="tight")
+
+plt.figure(figsize=(12,9))
[…]

### 2016-06-25 notes/paper/make_graphs_walking_biking.py
Created python files to create the figures needed.

@@ -1,0 +1,41 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+walking = np.array([0.84794, 0.909459, 0.850478, 0.906831, 0.862499, 0.926355, 0.906276, 0.900198, 0.938393, 0.934762, 0.920486, 0.864496, 0.921065, 0.854258, 0.900292, 0.894288, 0.908544, 0.888207, 0.901154, 0.921692, 0.890178, 0.887596, 0.828443, 0.904484, 0.849955, 0.916847, 0.899168, 0.91797, 0.932738, 0.936772, 0.95634, 0.906997, 0.931281, 0.875598, 0.920153, 0.838532, 0.904328, 0.904448, 0.918744, 0.946283, 0.921908, 0.930042, 0.86388, 0.923708, 0.885149, 0.918485, 0.896543, 0.917104, 0.935319, 0.906593, 0.914294, 0.906969, 0.929369, 0.858822, 0.894336, 0.824241, 0.904161, 0.830148, 0.874468, 0.785672, 0.899271, 0.940611, 0.907252, 0.913564, 0.877749, 0.929613, 0.912499, 0.925567, 0.866579, 0.929623, 0.93787, 0.939557, 0.955559, 0.925966, 0.933549, 0.843215, 0.914925, 0.858983, 0.899164, 0.866985, 0.90986, 0.92087, 0.896269, 0.93171, 0.909918, 0.929025, 0.888036, 0.940737, 0.894057, 0.931365, 0.934599, 0.928244, 0.92282, 0.921015, 0.951321, 0.913612, 0.904481, 0.839105, 0.896004, 0.8588, 0.896319, 0.854178, 0.885876, 0.900081, 0.91569, 0.935342, 0.922368, 0.929162, 0.895921, 0.926157, 0.867629, 0.893603, 0.878906, 0.917411, 0.91562, 0.94121, 0.944205, 0.919567, 0.943681, 0.911371, 0.947294, 0.956737, 0.956125, 0.958828, 0.947283, 0.966719, 0.924671, 0.940748, 0.889098, 0.927789, 0.875759, 0.905913, 0.896647, 0.907511, 0.933524, 0.920492, 0.923788, 0.893768, 0.913336, 0.865062, 0.913386, 0.883637, 0.903123, 0.866881, 0.903453, 0.920731, 0.88505, 0.939967, 0.901619, 0.934523, 0.889663, 0
[…]

### 2016-06-25 notes/paper/make_graphs_walking_running.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+walking = np.array([0.84794, 0.909459, 0.850478, 0.906831, 0.862499, 0.926355, 0.906276, 0.900198, 0.938393, 0.934762, 0.920486, 0.864496, 0.921065, 0.854258, 0.900292, 0.894288, 0.908544, 0.888207, 0.901154, 0.921692, 0.890178, 0.887596, 0.828443, 0.904484, 0.849955, 0.916847, 0.899168, 0.91797, 0.932738, 0.936772, 0.95634, 0.906997, 0.931281, 0.875598, 0.920153, 0.838532, 0.904328, 0.904448, 0.918744, 0.946283, 0.921908, 0.930042, 0.86388, 0.923708, 0.885149, 0.918485, 0.896543, 0.917104, 0.935319, 0.906593, 0.914294, 0.906969, 0.929369, 0.858822, 0.894336, 0.824241, 0.904161, 0.830148, 0.874468, 0.785672, 0.899271, 0.940611, 0.907252, 0.913564, 0.877749, 0.929613, 0.912499, 0.925567, 0.866579, 0.929623, 0.93787, 0.939557, 0.955559, 0.925966, 0.933549, 0.843215, 0.914925, 0.858983, 0.899164, 0.866985, 0.90986, 0.92087, 0.896269, 0.93171, 0.909918, 0.929025, 0.888036, 0.940737, 0.894057, 0.931365, 0.934599, 0.928244, 0.92282, 0.921015, 0.951321, 0.913612, 0.904481, 0.839105, 0.896004, 0.8588, 0.896319, 0.854178, 0.885876, 0.900081, 0.91569, 0.935342, 0.922368, 0.929162, 0.895921, 0.926157, 0.867629, 0.893603, 0.878906, 0.917411, 0.91562, 0.94121, 0.944205, 0.919567, 0.943681, 0.911371, 0.947294, 0.956737, 0.956125, 0.958828, 0.947283, 0.966719, 0.924671, 0.940748, 0.889098, 0.927789, 0.875759, 0.905913, 0.896647, 0.907511, 0.933524, 0.920492, 0.923788, 0.893768, 0.913336, 0.865062, 0.913386, 0.883637, 0.903123, 0.866881, 0.903453, 0.920731, 0.88505, 0.939967, 0.901619, 0.934523, 0.889663, 0.926323, 0.901285, 0.908031, 0.909289
[…]

### 2016-06-25 notes/paper/paper.tex
Incremental updates to the paper.

--- 2016-06-20 notes/paper/paper.tex
@@
 \usepackage{subfig}
-%\usepackage{caption}
 \usepackage[english]{babel}
@@
 %
-\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
+\author{Craig~Euler, Bryan~Juarez, Melissa~Flores, C.T.~Lin}
 %
@@
 We improve computational efficiency with dimensionality reduction, decimation in time, and pre-processing of our references post training for use in the matched-filter.
-An assessment of our processing time is provided with runtime experiments on the MSP432 micro-controller which shows feasability of real-time processing capability.
+An assessment of our processing time is provided with runtime experiments on the MSP432 micro-controller which shows feasibility of real-time processing capability.
 \end{abstract}
@@
 The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
-Many of the algorithms and software structure were tailored to computational efficiency to accomidate the resource limitations on the MSP 432 micro-processor.
+Many of the algorithms and software structure were tailored to computational efficiency to accommodate the resource limitations on the MSP432 micro-processor.
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
@@
 \section{The Algorithms}
+%
 \subsection{Activity Classification Method}
@@
 \subsection{Dimensionality Reduction}
-We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analaysis (PCA) \cite{bishop_2006}.
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
 We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
@@
 The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
-There is a tradeoff between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of reducing our processing cost.
+There is a trade off between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of reducing our processing cost.
 
@@
 %
-\begin{equation} \label{trignal_filter_weights}
+\begin{equation} \label{triangle_filter_weights}
 w_k^N =
@@
 %
-\section{Performance and Throughput}
+\section{Results}
+%
+\subsection{Algorithm Performance}
 %
@@
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance.
+Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance of the algorithms described in this paper.
 A separate instance of walking data has been used specifically for training the classifier.
@@
 As we would expect, walking data matches better to walking data than the other activities.
-ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illistrate the effectiveness of the matched-filter as a classifier.
+ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
 Figure \ref{fig:MF_performance} shows the comparison to bicycling.
 Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
-%
-%\begin{figure}[!tbp]
-%\RawFloats
-%  \centering
-%     \begin{minipage}[b]{0.45\textwidth}
-%        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
-%        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
-%     \end{minipage}
-%     \hfill
-%     \begin{minipage}[b]{0.45\textwidth}
-%     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
-%        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
-%     \end{minipage}
-%\caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
-%\end{figure}
 %
@@
   \centering
-  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
   \quad
-  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
   \centering
@@
    \centering
-   \includegraphics[width=1.0\textwidth]{one_and_two_references.png} \label{fig:timing_refs}
+   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
+   \quad
+   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
    \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification with the matched-filter.
 The time window used for activity classification is 4.0 seconds}
+   \label{fig:timing}
 \end{figure}
+%
+\subsection{Throughput Performance}
+%
+To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
+The Texas Instrument - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
+Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
+The single-precision processing capability on this unit provides us with a sufficiently large dynamic range that fixed-point processing cannot provide.
+The 64 kB of SRAM provided sufficient space to process the results found in figure \ref{fig:timing} and
+the 256 kB is more than enough flash memory to store the program and data references.
+The clock frequency operates at 48 MHz which allows the microcontroller to have a high performance by allowing a high number of instruction cycles that ultimately allows for faster code execution.
+
+The “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer” oscilloscope was used for measuring the timing of the algorithms on the micro-controller.
+When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
+This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-fitlering (end of algorithm processing).
+The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
+
+Randomized data was used for the purpose of analysing the throughput performance on the device while varying the parameters.
+Figure \ref{fig:multiple_comparison} shows execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
+Because the FFT dominates the processing load, and was optimized for even powered factors, one can observe better throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even valued time lengths and sampling frequencies.
+Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than the $50$Hz.
+Figure \ref{fig:timing_refs} shows execution time over a $4.0$ second window at decimation $8$ while varying the sampling frequency and number of references.
+From this, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\%.
 %

### 2016-06-25 notes/paper/make_timing_plots.py

@@ -16,8 +16,8 @@ time_freq_64hz_dec_2_2ref = np.array([0.2891, 1.4227, 0.865, 1.217, 1.728, 1.904
 time_freq_75hz_dec_2_2ref = np.array([1.132, 2.377, 9.305, 4.965, 25.82, 20.48, 50.22, 11.39, 89.52, 59.22])
 
 plt.figure(figsize=(12,9))
-sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', label="1 Reference")
-sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#888888', label="2 References")
+sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', marker='s', ms=10, linestyle='-', label="1 Reference")
+sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#000000', marker='s', ms=10, linestyle='--', label="2 References")
 plt.title("Timing on MSP432 at Decimation 8", fontsize=26)
 plt.xlabel("Sampling Frequency", fontsize=26)
 plt.ylabel("Execution Time (seconds)", fontsize=26)
@@ -29,8 +29,8 @@ plt.savefig("one_and_two_references.png", bbox_inches="tight")
 plt.figure(figsize=(12,9))
 plt_75hz_dec2_2ref, = plt.plot(time_window, time_freq_75hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='-', color='#000000', label="75 Hz")
 plt_64hz_dec2_2ref, = plt.plot(time_window, time_freq_64hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='--', color='#000000', label="64 Hz")
-plt_50hz_dec2_2ref, = plt.plot(time_window, time_freq_50hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='-.', color='#000000', label="50 Hz")
-plt_62hz_dec2_2ref, = plt.plot(time_window, time_freq_62hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle=':', color='#000000', label="62 Hz")
[…]

### 2016-06-25 notes/paper/paper.tex
Incremental updates to the paper. Tweaks to the figures and wording on some parts.

@@
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
-The resulting unit length eigen vectors $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigen values $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
+The resulting unit length column eigenvectors of $Q$ are $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigenvalues $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
 % \ref{bishop_2006}
@@
 We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{project_eq}.
-We make the assumption that our data is most dominate in two dimensions i.e.
-$\lambda^3 << \lambda^2$ so it is safe to assume that
+If the data is mostly dominate in the two primary dimensions, i.e.
+$\lambda^3 << \lambda^2$, then it is safe to assume that
 %
 \begin{equation} \label{magnitude_eq}
-||(a^1,a^2,a^3)|| = ||(a'^1,a'^2,a'^3)|| \sim = (a'^1)^2 + (a'^2)^2
+||(a^1,a^2,a^3)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
 \end{equation}
@@
 \begin{equation} \label{triangle_filter_weights}
-w_k^N =
+w_k^D =
 \begin{cases}
-  \frac{k+1}{N^2}, & \text{if}\ 0 \leq k < N \\
-  \frac{2N - (k + 1)}{N^2}, & \text{if} N \leq k < 2N - 1
+  \frac{k+1}{D^2}, & \text{if }\ 0 \leq k < D \\
+  \frac{2D - (k + 1)}{D^2}, & \text{if } D \leq k < 2D - 1 \\
+  0, & \text{otherwise}
 \end{cases}
@@
 %
-For a decimation value of $N$. Then the data is downsampled by $N$. This results in:
+For a decimation value of $D$. Then the data is downsampled by $D$. This results in:
 %
@@
 %
-where $\{s_k^1\}_{k=0}^{M/N}$? is the decimated signal of $\{s_k^0\}_{k=0}^M$?.
+where $\{s_k^1\}_{k=0}^{M/D}$? is the decimated signal of $\{s_k^0\}_{k=0}^M$?.
 \subsection{Training the Module}
@@
 %
-The Kinetisense sensor was used for the performance analysis in this paper.
+The Kinetisense sensor was used for the algorithm performance analysis in this paper.
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance of the algorithms described in this paper.
+Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
 A separate instance of walking data has been used specifically for training the classifier.
-In figure \ref{fig:MF_performance}, \subref{fig:frac_walking_jogging} and \subref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
-As we would expect, walking data matches better to walking data than the other activities.
-ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
-Figure \ref{fig:MF_performance} shows the comparison to bicycling.
-Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
 %
@@
   \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
-  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation 8}
+  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
+Results produced with decimation 8.
+Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectivley.}
   \label{fig:MF_performance}
@@
 %
+Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
+As we would expect, walking data matches better to walking data than the other activities.
+ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
+Figure \ref{fig:MF_performance} shows the comparison to bicycling.
+Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
+%
 %\FloatBarrier
-reference to figure \ref{fig:MF_performance}
-%
-\begin{figure}[!ht]
-   \centering
-   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
-   \quad
-   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
-   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification with the matched-filter.
-The time window used for activity classification is 4.0 seconds}
-   \label{fig:timing}
-\end{figure}
 %
@@
 
+%
+\begin{figure}[!ht]
+   \centering
+   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
+   \quad
+   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
+   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 micro-controller processor.
+The time window used for (b) is 4.0 seconds.}
+   \label{fig:timing}
+\end{figure}
+%
 Randomized data was used for the purpose of analysing the throughput performance on the device while varying the parameters.

### 2016-06-25 notes/paper/make_graphs_walking_biking.py

@@ -20,8 +20,8 @@ for k in range(len(bicycling_prob)):
 bicycling_prob /= len(bicycling)
 
 plt.figure(figsize=(12,9))
-walking_plot,   = plt.plot(threshold, walking_prob,   lw=4, color='#000000', label="Walking data")
-bicycling_plot, = plt.plot(threshold, bicycling_prob, lw=4, color='#888888', label="Bicycling data")
+walking_plot,   = plt.plot(threshold, walking_prob,   lw=4, color='#000000', linestyle='-', label="Walking data")
+bicycling_plot, = plt.plot(threshold, bicycling_prob, lw=4, color='#000000', linestyle='--', label="Bicycling data")
 plt.title("Matched-Filter Correlation with Reference: Walking", fontsize=26)
 plt.ylabel("Fraction Exceeding Threshold", fontsize=26)
 plt.xlabel("Correlation Threshold", fontsize=26)

### 2016-06-25 notes/paper/make_graphs_walking_running.py

@@ -17,8 +17,8 @@ for k in range(len(jogging_prob)):
 jogging_prob /= len(jogging)
 
 plt.figure(figsize=(12,9))
-walking_plot, = plt.plot(threshold, walking_prob, lw=4, color='#000000', label="Walking data")
-jogging_plot, = plt.plot(threshold, jogging_prob, lw=4, color='#888888', label="Jogging data")
+walking_plot, = plt.plot(threshold, walking_prob, lw=4, color='#000000', linestyle='-', label="Walking data")
+jogging_plot, = plt.plot(threshold, jogging_prob, lw=4, color='#000000', linestyle='--', label="Jogging data")
 plt.title("Matched-Filter Correlation with Reference: Walking", fontsize=26)
 plt.xlabel("Correlation Threshold", fontsize=26)
 plt.ylabel("Fraction Exceeding Threshold", fontsize=26)

### 2016-06-26 notes/paper/paper.tex
Incremental changes.

@@
 We improve computational efficiency with dimensionality reduction, decimation in time, and pre-processing of our references post training for use in the matched-filter.
-An assessment of our processing time is provided with runtime experiments on the MSP432 micro-controller which shows feasibility of real-time processing capability.
+An assessment of our processing time is provided with runtime experiments on the MSP432 microcontroller which shows feasibility of real-time processing capability.
 \end{abstract}
@@
 The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
-Many of the algorithms and software structure were tailored to computational efficiency to accommodate the resource limitations on the MSP432 micro-processor.
+Many of the algorithms and software structure were tailored to computational efficiency to accommodate the resource limitations on the MSP432 microprocessor.
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
@@
 This algorithm is the most demanding on computational resources and is only ran when training or re-training the unit to identify the user\textquotesingle s activity, so this can be performed on an external device such as a smart phone or tablet.
-The purpose of the training module is to create the reference signal to be used on the micro-controller for real-time processing.
+The purpose of the training module is to create the reference signal to be used on the microcontroller for real-time processing.
 
@@
 
-The “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer” oscilloscope was used for measuring the timing of the algorithms on the micro-controller.
+The “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer” oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
 When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
@@
    \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
-   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 micro-controller processor.
+   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
 The time window used for (b) is 4.0 seconds.}

### 2016-06-27 notes/paper/paper.tex
Added timing test figure to the paper.

@@
 Many of which are used for activity monitoring or fitness.
-In this paper, we make use of a matched-filtering algorithm for real-time activity classification with data obtained from three-axis accelerometers worn by the user.
+In this paper, we make use of a matched-filtering algorithm for activity classification with data obtained from three-axis accelerometers worn by the user.
+We show real-time processing capability on the MSP432 microcontroller hardware.
 We achieve invariance to sensor orientation with dimensionality reduction.
@@
 Custom decision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-In this paper, we make use of a matched-filter method to identify an individual\textquotesingle s activity in real-time.
+In this paper, we make use of a matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
 The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
@@
 Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
-Devices such as the Fit-Bit, Apple watch, Moov, Jawbone, etc. usually have the individual actively input the activity they are performing.
 
@@
 
+\begin{figure}[!ht]
+   \centering
+   \includegraphics[width=0.45\textwidth]{32Hz_4sec_8downsample_2Reference_Pulse.PNG}
+   \caption{Test setup}
+   \label{fig:time_measure}
+\end{figure}
+%
 The “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer” oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
@@
 
-%
 \begin{figure}[!ht]

### 2016-06-27 notes/paper/paper.tex
Incremental changes.

@@
   \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
-Results produced with decimation 8.
+Results produced at decimation 8.
 Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectivley.}
@@
 To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
-The Texas Instrument - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
+The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
 Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
-The single-precision processing capability on this unit provides us with a sufficiently large dynamic range that fixed-point processing cannot provide.
-The 64 kB of SRAM provided sufficient space to process the results found in figure \ref{fig:timing} and
+The single-precision processing capability on this unit provides us with a sufficiently large dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
+The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
 the 256 kB is more than enough flash memory to store the program and data references.
-The clock frequency operates at 48 MHz which allows the microcontroller to have a high performance by allowing a high number of instruction cycles that ultimately allows for faster code execution.
+The clock frequency operates at 48 MHz which determines the execution speed.
 
@@
    \includegraphics[width=0.45\textwidth]{32Hz_4sec_8downsample_2Reference_Pulse.PNG}
-   \caption{Test setup}
+   \caption{Oscilloscope output used for measuring the processing time of the algorithms on the MSP432.
+This is a case setup of 32Hz sampling frequency over a 4 second time window with 2 references at decimation 8 showing the voltage output over time.
+Execution time is measured from the start to end of the ``high'' (3.3 Volts) time interval.}
    \label{fig:time_measure}
@@
 %
-The “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer” oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
+The ``Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer'' oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
 When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
-This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-fitlering (end of algorithm processing).
+This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-filtering (end of algorithm processing).
 The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
+An example can be seen in Figure \ref{fig:time_measure}.
 
@@
 Randomized data was used for the purpose of analysing the throughput performance on the device while varying the parameters.
-Figure \ref{fig:multiple_comparison} shows execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
+Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
 Because the FFT dominates the processing load, and was optimized for even powered factors, one can observe better throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even valued time lengths and sampling frequencies.
 Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than the $50$Hz.
-Figure \ref{fig:timing_refs} shows execution time over a $4.0$ second window at decimation $8$ while varying the sampling frequency and number of references.
-From this, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\%.
+Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
+Because the pre-processing execution time does not change with the number of references, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\% when processing for a single reference.
 %

### 2016-06-30 notes/paper/paper.tex
Conclusion supplied by Melissa Flores.

@@
 \section{Conclusion}
-conclusion text.
+Matched-filtering algorithms can be used for activity classification.
+They can also be performed in real-time on a microcontroller such as the MSP432.
+The algorithms consist of a training module in which the device is trained to identify the user’s activity along with a real-time activity classification module which uses the stored references that are produced by the training module in order to actively classify a user’s activity.
+Although the matched-filtering algorithms require significant processing power, the data undergoes dimensionality reduction and decimation in order to reduce the required computational resources prior to being analyzed.
+The algorithms were validated by using the Kinetisense accelerometer sensor to collect walking, jogging, and bicycling data.
+The training module was ran on the data to produce references of the activities.
+The data was compared to the walking reference and it was shown that the walking data matched well with the walking reference while the jogging and bicycling data did not match as well.
+The algorithms were also executed on the MSP432.
+Since FFT calculations dominate the processing time and work best with data that has radix 2 number of points, timing tests results demonstrate that radix 2 time-window lengths and frequency values result in faster processing times.
 %

### 2016-06-30 notes/paper/paper.tex
Updates and making the corrections suggested by Melissa.

--- 2016-06-27 notes/paper/paper.tex
@@
 \begin{abstract}
-Body worn sensors have been used in the market for many years now.
-Many of which are used for activity monitoring or fitness.
+Body worn sensors have been used in the market for many years now many of which are used for activity monitoring or fitness.
 In this paper, we make use of a matched-filtering algorithm for activity classification with data obtained from three-axis accelerometers worn by the user.
@@
 Various methods for activity classification using body-worn sensors exist.
-Custom decision tree, automatically generated decision tree, and artificial neural networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
+Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
 In this paper, we make use of a matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
@@
 Many of the algorithms and software structure were tailored to computational efficiency to accommodate the resource limitations on the MSP432 microprocessor.
-Having an a priori knowledge of the activity the individual is performing is useful for many current fitness algorithms.
+Having an understanding of what activity the individual is performing is useful for many current fitness algorithms.
 
@@
 The training module does not need to be performed in real time.
-This algorithm is the most demanding on computational resources and is only ran when training or re-training the unit to identify the user\textquotesingle s activity, so this can be performed on an external device such as a smart phone or tablet.
+This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, so this can be performed on an external device such as a smart phone or tablet.
 The purpose of the training module is to create the reference signal to be used on the microcontroller for real-time processing.
@@
 %
-Where $\textbf{x}'$ is $\textbf{x}$ that has been zero padded to the length of $\textbf{y}$ with the added restriction that the length of $\textbf{x}$ is no more than the length of $\textbf{y}$ and $FFT$ is the Fast Fourier Transform algorithm.
+where $\textbf{x}'$ is $\textbf{x}$ that has been zero padded to the length of $\textbf{y}$ with the added restriction that the length of $\textbf{x}$ is no more than the length of $\textbf{y}$ and $FFT$ is the Fast Fourier Transform algorithm.
 We are most interested where our reference $\textbf{x}$ best matches our data $\textbf{y}$.
@@
 %
-If \eqref{matched_filter_eq} passes a threshold, the corresponding signal is a match.
+If \eqref{matched_filter_eq} passes a set threshold, the corresponding signal is a match.
 %
@@
 By now we have preserved as much information that is contained in our acceleration data as possible while also reducing our dimension from three to two.
-By projecting our data onto the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
+By projecting our data onto the plane defined by the two most dominant eigenvectors, we effectively reduce our representation of our data to two dimensions.
 
@@
 %
-For a decimation value of $D$. Then the data is downsampled by $D$. This results in:
+for a decimation value of $D$. Then the data is downsampled by $D$. This results in:
 %
@@
 %
-where $M \leq N$, $I$ is a positive, fixed integer, and $(n,m) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$.
+where $M \leq N$, $I$ is a positive, fixed integer, and $(m,n) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$.
 Then we can determine the representative signal $\textbf{s} \in X$ for our activity that satisfies the condition:
@@
 Results produced at decimation 8.
-Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectivley.}
+Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
   \label{fig:MF_performance}
@@
 As we would expect, walking data matches better to walking data than the other activities.
-ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
-Figure \ref{fig:MF_performance} shows the comparison to bicycling.
+ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
+Figures \ref{fig:frac_walking_bicycling} and \ref{fig:roc_walking_bicycling} show the comparison to bicycling.
 Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
@@
 %
-Randomized data was used for the purpose of analysing the throughput performance on the device while varying the parameters.
-Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
-Because the FFT dominates the processing load, and was optimized for even powered factors, one can observe better throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even valued time lengths and sampling frequencies.
-Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than the $50$Hz.
+Randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters.
+Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
+Because the FFT dominates the processing load, and was optimized for even-powered factors, one can observe better throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued time-lengths and sampling frequencies.
+Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that the $50$Hz.
 Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
@@
 \section{Conclusion}
-conclusion text.
+We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
+We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
+Since FFT calculations dominate the processing time and work best with data that has radix 2 number of points, timing tests results demonstrate that radix 2 time-window lengths and frequency values result in faster processing times.
+We increase our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, to reduce our computational requirements.
+The references used in the matched-filter are obtained from the training module.
+A training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
+
 %

### 2016-06-30 notes/paper/make_graphs_walking_biking.py

@@ -27,6 +27,7 @@ plt.ylabel("Fraction Exceeding Threshold", fontsize=26)
 plt.xlabel("Correlation Threshold", fontsize=26)
 plt.yticks(fontsize=20)
 plt.xticks(fontsize=20)
+plt.grid(True)
 plt.legend(handles=[walking_plot, bicycling_plot], loc='lower left', prop={'size':26})
 plt.savefig("fraction_threshold_walking_to_bicycling.png", bbox_inches="tight")
 
@@ -37,5 +38,6 @@ plt.ylabel("Walking Classified as Walking", fontsize=26)
 plt.xlabel("Bicycling Classified as Walking", fontsize=26)
 plt.yticks(np.linspace(0, 1, 11), fontsize=20)
 plt.xticks(np.linspace(0, 1, 11), fontsize=20)
+plt.grid(True)
 plt.plot(bicycling_prob, walking_prob, lw=8, color='#000000')
 plt.savefig("ROC_walk_to_bike.png", bbox_inches="tight")

### 2016-06-30 notes/paper/make_graphs_walking_running.py

@@ -24,6 +24,7 @@ plt.xlabel("Correlation Threshold", fontsize=26)
 plt.ylabel("Fraction Exceeding Threshold", fontsize=26)
 plt.yticks(fontsize=20)
 plt.xticks(fontsize=20)
+plt.grid(True)
 plt.legend(handles=[walking_plot, jogging_plot], loc='lower left', prop={'size':26})
 plt.savefig("fraction_threshold_walking_to_jogging.png", bbox_inches="tight")
 
@@ -34,5 +35,6 @@ plt.ylabel("Walking Classified as Walking", fontsize=26)
 plt.xlabel("Jogging Classified as Walking", fontsize=26)
 plt.yticks(np.linspace(0, 1, 11), fontsize=20)
 plt.xticks(np.linspace(0, 1, 11), fontsize=20)
+plt.grid(True)
 plt.plot(jogging_prob, walking_prob, lw=8, color='#000000')
 plt.savefig("ROC_walk_to_run.png", bbox_inches="tight")

### 2016-06-30 notes/paper/make_timing_plots.py

@@ -23,6 +23,7 @@ plt.xlabel("Sampling Frequency", fontsize=26)
 plt.ylabel("Execution Time (seconds)", fontsize=26)
 plt.yticks(fontsize=20)
 plt.xticks(fontsize=20)
+plt.grid(True)
 plt.legend(handles=[sec4_dec8_plot_1ref, sec4_dec8_plot_2ref], loc='upper left', prop={'size':26})
 plt.savefig("one_and_two_references.png", bbox_inches="tight")
 
@@ -36,5 +37,6 @@ plt.xlabel("Time Window Length (seconds)", fontsize=26)
 plt.ylabel("Execution Time (seconds)", fontsize=26)
 plt.yticks(fontsize=20)
 plt.xticks(fontsize=20)
+plt.grid(True)
 plt.legend(handles=[plt_75hz_dec2_2ref, plt_64hz_dec2_2ref, plt_62hz_dec2_2ref, plt_50hz_dec2_2ref], loc='upper left', prop={'size':26})
 plt.savefig("more_time_plots.png", bbox_inches="tight")

### 2016-07-01 notes/paper/paper.tex
Updates to the paper.

@@
 %
-\section{The Algorithms}
+\section{The Methodology}
 %
@@
 %
-\begin{equation} \label{cross_correlation_eq}
-(\textbf{x} \star \textbf{y}) = \left \{\sum_{i=0}^{M}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
+\begin{equation} \label{eq:cross_correlation}
+(\textbf{x} \star \textbf{y}) = \left \{\sum_{i=0}^{M-1}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
 \end{equation}
@@
 which is simply a moving dot product.
-We can then normalize \eqref{cross_correlation_eq} by the following:
+We can then normalize \eqref{eq:cross_correlation} by the following:
 %
-\begin{equation} \label{norm_cross_correlation_eq}
+\begin{equation} \label{eq:norm_cross_correlation}
 \widehat{(\textbf{x} \star \textbf{y})}_k = \frac{(\textbf{x} \star \textbf{y})_k}{||\textbf{x}|| \ || \widetilde{\textbf{y}}_k || }, \quad k = 0,1,...,N-M-1
@@
 where $|| \cdot ||$ is the usual $\ell_2$ norm and $\widetilde{\textbf{y}}_k = \{y_p\}_{p=k}^{M+k-1}$.
-\eqref{norm_cross_correlation_eq} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
-We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
+\eqref{eq:norm_cross_correlation} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
+We improve our computational efficiency by applying the convolution theorem to \eqref{eq:cross_correlation} and replacing it with:
 %
-\begin{equation} \label{conv_theorem}
+\begin{equation} \label{eq:conv_theorem}
 (\textbf{x} \star \textbf{y}) = FFT^{-1}(FFT(\textbf{x}') FFT(\textbf{y})^*)
@@
 %
-\begin{equation} \label{matched_filter_eq}
+\begin{equation} \label{eq:matched_filter}
 MF_{\textbf{x}}(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}_k \right \}
@@
 %
-If \eqref{matched_filter_eq} passes a set threshold, the corresponding signal is a match.
+If \eqref{eq:matched_filter} passes a set threshold, the corresponding signal is a match.
 %
@@
 % \ref{bishop_2006}
-\begin{equation} \label{project_eq}
+\begin{equation} \label{eq:project}
    \textbf{a}' = V^T \textbf{a}
@@
 %
-We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{project_eq}.
+We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{eq:project}.
 If the data is mostly dominate in the two primary dimensions, i.e.
@@
 %
-\begin{equation} \label{magnitude_eq}
+\begin{equation} \label{eq:magnitude}
 ||(a^1,a^2,a^3)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
@@
 
-To compute the matched-filter output for two dimensions, we generalize \eqref{matched_filter_eq} by augmenting our reference and data with both dimensions appropriately for normalization and adding together the cross correlations as:
+To compute the matched-filter output for two dimensions, we generalize \eqref{eq:matched_filter} by augmenting our reference and data with both dimensions appropriately for normalization and adding together the cross correlations as:
 %
-\begin{equation} \label{cross_correlation_eq_2}
+\begin{equation} \label{eq:cross_correlation_2}
 \widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
@@
 %
-\begin{equation} \label{matched_filter_eq_2}
+\begin{equation} \label{eq:matched_filter_2}
 MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k \right \}
@@
 
-For our application, we use a triangle filter prior to downsampling. This is achieved by convolving our data with the following weights:
+For our application, we use a triangle filter prior to downsampling. This is achieved by applying the following weights:
 %
-\begin{equation} \label{triangle_filter_weights}
+\begin{equation} \label{eq:triangle_filter_weights}
 w_k^D =
 \begin{cases}
-  \frac{k+1}{D^2}, & \text{if }\ 0 \leq k < D \\
-  \frac{2D - (k + 1)}{D^2}, & \text{if } D \leq k < 2D - 1 \\
+  \frac{D+k}{D^2}, & \text{if }\ -D < k \leq 0 \\
+  \frac{D-k}{D^2}, & \text{if } D < k < D \\
   0, & \text{otherwise}
@@
 %
-for a decimation value of $D$. Then the data is downsampled by $D$. This results in:
+and convolve it with our data to get
 %
-\begin{equation} \label{decimated_signal}
-s_k^1 = \sum_{p=0}^{2N-1} w_{p+N(1-k)}^N s_{kN - (p+1)}^0 ?
+\begin{equation} \label{eq:convolve}
+s'_k = \sum_{i=0}^{N} s_i w_{k-i}
 \end{equation}
 %
-where $\{s_k^1\}_{k=0}^{M/D}$? is the decimated signal of $\{s_k^0\}_{k=0}^M$?.
+followed by a downsample
+%
+\begin{equation} \label{eq:downsample}
+s''_k = s'_{(k+1)D-1}, \quad k = 0, 1, 2, ..., M/D.
+\end{equation}
+%
+One can reduce the processing cost by combining \eqref{eq:convolve} and \eqref{eq:downsample} together in such a way that we only process the points that we keep.
+%
 \subsection{Training the Module}
@@
 %
-\begin{equation} \label{X_subsets_of_training_eq}
+\begin{equation} \label{eq:X_subsets_of_training_eq}
 X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=mI \right \}
@@
 %
-\begin{equation} \label{Y_subsets_of_training_eq}
+\begin{equation} \label{eq:Y_subsets_of_training_eq}
 Y := \left \{ \{t_k\}_{k=p}^{p+N-1} | p=nI \right \}
@@
 %
-\begin{equation} \label{s_condition}
+\begin{equation} \label{eq:s_condition}
 \sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
@@
 %
-\section{Results}
+\section{Performance and Throughput}
 %
@@
 Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
-The single-precision processing capability on this unit provides us with a sufficiently large dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
+The single-precision processing capability on this unit provides us with dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
 The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
@@
    \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
-The time window used for (b) is 4.0 seconds.}
+The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
    \label{fig:timing}
@@
 Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
-Because the FFT dominates the processing load, and was optimized for even-powered factors, one can observe better throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued time-lengths and sampling frequencies.
+Because the FFT dominates the processing load, and was optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
 Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that the $50$Hz.
@@
 We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
-Since FFT calculations dominate the processing time and work best with data that has radix 2 number of points, timing tests results demonstrate that radix 2 time-window lengths and frequency values result in faster processing times.
+Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the procesing time.
 We increase our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, to reduce our computational requirements.

### 2016-07-01 notes/paper/make_timing_plots.py

@@ -16,8 +16,8 @@ time_freq_64hz_dec_2_2ref = np.array([0.2891, 1.4227, 0.865, 1.217, 1.728, 1.904
 time_freq_75hz_dec_2_2ref = np.array([1.132, 2.377, 9.305, 4.965, 25.82, 20.48, 50.22, 11.39, 89.52, 59.22])
 
 plt.figure(figsize=(12,9))
-sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', marker='s', ms=10, linestyle='-', label="1 Reference")
-sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#000000', marker='s', ms=10, linestyle='--', label="2 References")
+sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', marker='s', ms=14, linestyle='-', label="1 Reference")
+sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#000000', marker='^', ms=14, linestyle='--', label="2 References")
 plt.title("Timing on MSP432 at Decimation 8", fontsize=26)
 plt.xlabel("Sampling Frequency", fontsize=26)
 plt.ylabel("Execution Time (seconds)", fontsize=26)
@@ -28,10 +28,10 @@ plt.legend(handles=[sec4_dec8_plot_1ref, sec4_dec8_plot_2ref], loc='upper left',
 plt.savefig("one_and_two_references.png", bbox_inches="tight")
 
 plt.figure(figsize=(12,9))
-plt_75hz_dec2_2ref, = plt.plot(time_window, time_freq_75hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='-', color='#000000', label="75 Hz")
-plt_64hz_dec2_2ref, = plt.plot(time_window, time_freq_64hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='--', color='#000000', label="64 Hz")
-plt_62hz_dec2_2ref, = plt.plot(time_window, time_freq_62hz_dec_2_2ref, lw=4, marker='s', ms=10, linestyle='-.', color='#000000', label="62 Hz")
[…]

### 2016-07-03 notes/paper/paper.tex
fix
Edits made to the paper. Nearing final changes before commiting it to submission.

@@
 \begin{abstract}
-Body worn sensors have been used in the market for many years now many of which are used for activity monitoring or fitness.
-In this paper, we make use of a matched-filtering algorithm for activity classification with data obtained from three-axis accelerometers worn by the user.
-We show real-time processing capability on the MSP432 microcontroller hardware.
-We achieve invariance to sensor orientation with dimensionality reduction.
-We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity filters for our matched filter.
-We improve computational efficiency with dimensionality reduction, decimation in time, and pre-processing of our references post training for use in the matched-filter.
-An assessment of our processing time is provided with runtime experiments on the MSP432 microcontroller which shows feasibility of real-time processing capability.
+Having information of the user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor a user\textquotesingle s activity and fitness.
+In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
+We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
+Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benifit of making our data invarient to sensor orientation when applied.
+Data decimation in time is an additional throughput enhancement that we apply early to our data.
+We make use of an instance-based learning algorithm to train the device to learn the individual\textquotesingle s motion patterns and store that information as activity templates for use in our matched-filter.
 \end{abstract}
@@
 Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-In this paper, we make use of a matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
-The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and have been studied in the past \cite{giannakis_tsatsanis_1990}.
-Many of the algorithms and software structure were tailored to computational efficiency to accommodate the resource limitations on the MSP432 microprocessor.
-Having an understanding of what activity the individual is performing is useful for many current fitness algorithms.
+In this paper, we make use of the matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
+The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and has been studied in the past \cite{giannakis_tsatsanis_1990}.
+The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller (we use the MSP432 microcontroller).
 
-The algorithms described in this paper are broken into two main modules: Training the device to identify the user\textquotesingle s activity, and the real-time activity classification itself.
+The algorithms described in this paper are broken into two main modules: The real-time activity classification and training the device to identify the user\textquotesingle s activity.
 
 The training module does not need to be performed in real time.
-This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, so this can be performed on an external device such as a smart phone or tablet.
-The purpose of the training module is to create the reference signal to be used on the microcontroller for real-time processing.
+This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, which means that this can be performed on an external device such as a smart phone or tablet.
+The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.
 
-The second module is the real-time activity classification on the unit.
-This module reads in the reference(s) stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
+The real-time activity classification module is intended to be performed on a microcontroler.
+This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
 Both of these modules use the same principles and hence the same algorithm kernels.
@@
 Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
-We will discuss how we develop our set of templates for use in our matched-filter.
+We will discuss how we develop our set of templates for use in our matched-filter in section \ref{sec:training}.
 
-The matched filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
+The matched-filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
 The cross correlation of $\textbf{x}$ with $\textbf{y}$ is defined as:
@@
 \begin{equation} \label{eq:cross_correlation}
-(\textbf{x} \star \textbf{y}) = \left \{\sum_{i=0}^{M-1}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
+(\textbf{x} \star \textbf{y}) := \left \{\sum_{i=0}^{M-1}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
 \end{equation}
@@
 \begin{equation} \label{eq:norm_cross_correlation}
-\widehat{(\textbf{x} \star \textbf{y})}_k = \frac{(\textbf{x} \star \textbf{y})_k}{||\textbf{x}|| \ || \widetilde{\textbf{y}}_k || }, \quad k = 0,1,...,N-M-1
+\widehat{(\textbf{x} \star \textbf{y})}_k := \frac{(\textbf{x} \star \textbf{y})_k}{||\textbf{x}|| \ || \widetilde{\textbf{y}}_k || }, \quad k = 0,1,...,N-M-1
 \end{equation}
@@
 \begin{equation} \label{eq:conv_theorem}
-(\textbf{x} \star \textbf{y}) = FFT^{-1}(FFT(\textbf{x}') FFT(\textbf{y})^*)
+(\textbf{x} \star \textbf{y}) := FFT^{-1}(FFT(\textbf{x}') FFT(\textbf{y})^*)
 \end{equation}
@@
 %
-If \eqref{eq:matched_filter} passes a set threshold, the corresponding signal is a match.
+If \eqref{eq:matched_filter} passes a set threshold, then the corresponding signal $\textbf{y}$ is classified as a match to the reference $\textbf{x}$.
 %
@@
 
-If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data over a specified time window in three dimensions then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
+If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (where each $a_i$ is represented as a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
 The resulting unit length column eigenvectors of $Q$ are $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigenvalues $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
@@
 \begin{equation} \label{eq:project}
-   \textbf{a}' = V^T \textbf{a}
+   \textbf{a}' := V^T \textbf{a}
 \end{equation}
@@
 
-To compute the matched-filter output for two dimensions, we generalize \eqref{eq:matched_filter} by augmenting our reference and data with both dimensions appropriately for normalization and adding together the cross correlations as:
+To compute the matched-filter output for two dimensions, we generalize \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
 %
 \begin{equation} \label{eq:cross_correlation_2}
-\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k = \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
+\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k := \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
 \end{equation}
@@
 This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
+Here, the superscripts $1$ and $2$ represent the primary and secondary principle components of our data respectively.
 %
@@
 Decimation is the first step applied to our data before any additional processing takes place.
-Decimation is a process of reducing the sampling rate of a signal.
-The process consists of filtering to mitigate any possible aliasing distortion effects followed by a downsampling.
-There is a trade off between performance and throughput when we decimate our signal, therefore, we use decimation solely for the purpose of reducing our processing cost.
+Decimation is a process of reducing the sampling rate of the signal by filtering to mitigate any possible distortion effects due to aliasing followed by downsampling.
+Because real-time performance is important, we decimate our signal for the purpose of improving our throughput.
 
-For our application, we use a triangle filter prior to downsampling. This is achieved by applying the following weights:
+For a decimation value of $D$, we define our triangle filter with the following weights:
 %
 \begin{equation} \label{eq:triangle_filter_weights}
-w_k^D =
+w_k^D :=
 \begin{cases}
@@
 \begin{equation} \label{eq:convolve}
-s'_k = \sum_{i=0}^{N} s_i w_{k-i}
+s'_k := \sum_{i=0}^{N} s_i w_{k-i}
 \end{equation}
@@
 \begin{equation} \label{eq:downsample}
-s''_k = s'_{(k+1)D-1}, \quad k = 0, 1, 2, ..., M/D.
+s''_k := s'_{(k+1)D-1}, \quad k = 0, 1, 2, ..., N/D.
 \end{equation}
 %
-One can reduce the processing cost by combining \eqref{eq:convolve} and \eqref{eq:downsample} together in such a way that we only process the points that we keep.
+The processing cost is reduced by only processing points in \eqref{eq:convolve} that we keep in \eqref{eq:downsample}.
 %
-\subsection{Training the Module}
+\subsection{Training the Module} \label{sec:training}
 We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
-For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle s motion signature.
+For our application, we develop a reference template for our matched-filter directly from the person\textquotesingle s motion signature.
 We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal $s$ of our individual’s activity to be our template for our matched-filter.
+For a given activity, we attempt to find the representative periodic signal $\textbf{s}$ of our individual\textquotesingle s activity to be our template for our matched-filter.
 
@@
 \begin{equation} \label{eq:s_condition}
-\sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}) \quad \forall \textbf{x} \in X
+\sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}), \quad \forall \textbf{x} \in X
 \end{equation}
@@
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
+Samples of walking, jogging, and bicycling have been recorded with this unit and was attached to the ankle of the user.
 A separate instance of walking data has been used specifically for training the classifier.
@@
 Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
-As we would expect, walking data matches better to walking data than the other activities.
+As we would expect, the walking data reference matches better to walking data than to the other activities.
+The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
 ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
-Figures \ref{fig:frac_walking_bicycling} and \ref{fig:roc_walking_bicycling} show the comparison to bicycling.
-Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
+Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
 %
@@
 Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
-The single-precision processing capability on this unit provides us with dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
+The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
 The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
 the 256 kB is more than enough flash memory to store the program and data references.
-The clock frequency operates at 48 MHz which determines the execution speed.
+The clock frequency operates at 48 MHz which drives the execution speed.
 
@@
 %
-Randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters.
+Because the accelerometer was not connected to the microcontroller at the time of writing this paper, randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters which accurately models the processing load we would expect when we do have the accelerometer connected to the microcontroller.
 Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
@@
 Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the procesing time.
-We increase our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, to reduce our computational requirements.
-The references used in the matched-filter are obtained from the training module.
-A training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
+We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
+The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
 

### 2016-07-03 notes/paper/paper.tex
Spell checking to the paper.

@@
 We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
-Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benifit of making our data invarient to sensor orientation when applied.
+Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation when applied.
 Data decimation in time is an additional throughput enhancement that we apply early to our data.
@@
 
-The real-time activity classification module is intended to be performed on a microcontroler.
+The real-time activity classification module is intended to be performed on a microcontroller.
 This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
@@
 We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
-Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the procesing time.
+Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the processing time.
 We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.

### 2016-07-03 notes/paper/paper.tex
Some more touchups to the paper.

@@
 The resulting unit length column eigenvectors of $Q$ are $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigenvalues $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
+Here, we use superscripts to identify the axis directions in ascending order to represent the primary, secondary, and tertiary principal axis directions respectively.
 % \ref{bishop_2006}
@@
 \begin{equation} \label{eq:magnitude}
-||(a^1,a^2,a^3)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
+||(a_x,a_y,a_z)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
 \end{equation}
@@
 This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
-Here, the superscripts $1$ and $2$ represent the primary and secondary principle components of our data respectively.
+Here, the superscripts $1$ and $2$ represent the primary and secondary principal components of our data respectively.
 %

### 2016-07-04 notes/paper/paper.tex
Modifications to the title and abstract of the paper.

@@
 % paper title
-\title{Real-Time Activity Classification by Match Filtering using Body-Worn Accelerometers}
+\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
 %
-\author{Craig~Euler, Bryan~Juarez, Melissa~Flores, C.T.~Lin}
+\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
 %
@@
 \begin{abstract}
-Having information of the user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor a user\textquotesingle s activity and fitness.
+Having information of a user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor the user\textquotesingle s activity and fitness.
 In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.

### 2016-09-24 notes/paper/paper.tex
Updates to the graphs

@@
   \quad
+  \centering
   \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
@@
   \quad
-  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
+  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
   \centering
   \quad
-  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
+  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
   \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.

### 2016-09-24 notes/paper/make_graphs_walking_biking.py

@@ -22,22 +22,22 @@ bicycling_prob /= len(bicycling)
 plt.figure(figsize=(12,9))
 walking_plot,   = plt.plot(threshold, walking_prob,   lw=4, color='#000000', linestyle='-', label="Walking data")
 bicycling_plot, = plt.plot(threshold, bicycling_prob, lw=4, color='#000000', linestyle='--', label="Bicycling data")
-plt.title("Matched-Filter Correlation with Reference: Walking", fontsize=26)
-plt.ylabel("Fraction Exceeding Threshold", fontsize=26)
-plt.xlabel("Correlation Threshold", fontsize=26)
-plt.yticks(fontsize=20)
-plt.xticks(fontsize=20)
+plt.title("Correlations with Walking", fontsize=40)
+plt.ylabel("Fraction Exceeding Threshold", fontsize=40)
+plt.xlabel("Correlation Threshold", fontsize=40)
+plt.yticks(fontsize=40)
+plt.xticks(fontsize=40)
 plt.grid(True)
-plt.legend(handles=[walking_plot, bicycling_plot], loc='lower left', prop={'size':26})
+plt.legend(handles=[walking_plot, bicycling_plot], loc='lower left', prop={'size':34})
 plt.savefig("fraction_threshold_walking_to_bicycling.png", bbox_inches="tight")
 
 plt.figure(figsize=(12, 9))
 plt.ylim(0,1)
-plt.title("ROC Curve (Walking vs. Bicycling)", fontsize=26)
-plt.ylabel("Walking Classified as Walking", fontsize=26)
-plt.xlabel("Bicycling Classified as Walking", fontsize=26)
-plt.yticks(np.linspace(0, 1, 11), fontsize=20)
-plt.xticks(np.linspace(0, 1, 11), fontsize=20)
+plt.title("ROC Curve (Walking vs. Bicycling)", fontsize=40)
+plt.ylabel("Walking Classified as Walking", fontsize=40)
+plt.xlabel("Bicycling Classified as Walking", fontsize=40)
+plt.yticks(np.linspace(0, 1, 6), fontsize=40)
+plt.xticks(np.linspace(0, 1, 6), fontsize=40)
 plt.grid(True)
 plt.plot(bicycling_prob, walking_prob, lw=8, color='#000000')
 plt.savefig("ROC_walk_to_bike.png", bbox_inches="tight")

### 2016-09-24 notes/paper/make_graphs_walking_running.py

@@ -19,22 +19,22 @@ jogging_prob /= len(jogging)
 plt.figure(figsize=(12,9))
 walking_plot, = plt.plot(threshold, walking_prob, lw=4, color='#000000', linestyle='-', label="Walking data")
 jogging_plot, = plt.plot(threshold, jogging_prob, lw=4, color='#000000', linestyle='--', label="Jogging data")
-plt.title("Matched-Filter Correlation with Reference: Walking", fontsize=26)
-plt.xlabel("Correlation Threshold", fontsize=26)
-plt.ylabel("Fraction Exceeding Threshold", fontsize=26)
-plt.yticks(fontsize=20)
-plt.xticks(fontsize=20)
+plt.title("Correlations with Walking", fontsize=40)
+plt.xlabel("Correlation Threshold", fontsize=40)
+plt.ylabel("Fraction Exceeding Threshold", fontsize=40)
+plt.yticks(fontsize=40)
+plt.xticks(fontsize=40)
 plt.grid(True)
-plt.legend(handles=[walking_plot, jogging_plot], loc='lower left', prop={'size':26})
+plt.legend(handles=[walking_plot, jogging_plot], loc='lower left', prop={'size':34})
 plt.savefig("fraction_threshold_walking_to_jogging.png", bbox_inches="tight")
 
 plt.figure(figsize=(12, 9))
-plt.ylim(0,1)
-plt.title("ROC Curve (Walking vs. Jogging)", fontsize=26)
-plt.ylabel("Walking Classified as Walking", fontsize=26)
-plt.xlabel("Jogging Classified as Walking", fontsize=26)
-plt.yticks(np.linspace(0, 1, 11), fontsize=20)
-plt.xticks(np.linspace(0, 1, 11), fontsize=20)
+plt.ylim(0, 1)
+plt.title("ROC Curve (Walking vs. Jogging)", fontsize=40)
+plt.ylabel("Walking Classified as Walking", fontsize=40)
+plt.xlabel("Jogging Classified as Walking", fontsize=40)
+plt.yticks(np.linspace(0, 1, 6), fontsize=40)
+plt.xticks(np.linspace(0, 1, 6), fontsize=40)
 plt.grid(True)
 plt.plot(jogging_prob, walking_prob, lw=8, color='#000000')
 plt.savefig("ROC_walk_to_run.png", bbox_inches="tight")

### 2016-09-26 notes/paper/paper.tex
Incremetnal changes.

@@
 
-To compute the matched-filter output for two dimensions, we generalize \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
+Classification methods that are achieved from multi-dimensional feature spaces have been explored \cite{survey_multi_view_machine_learning}.
+In this paper, we compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
 %
@@
    \centering
-   \includegraphics[width=0.45\textwidth]{32Hz_4sec_8downsample_2Reference_Pulse.PNG}
+   \includegraphics[width=0.45\textwidth]{reference_pulse_32Hz_4sec_8downsample_2.png}
    \caption{Oscilloscope output used for measuring the processing time of the algorithms on the MSP432.
@@
 Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
-Because the FFT dominates the processing load, and was optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
-Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that the $50$Hz.
+Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
+Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
 Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
 Because the pre-processing execution time does not change with the number of references, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\% when processing for a single reference.
+%
+\begin{figure}[!ht]
+   \centering
+   \includegraphics[width=0.6\textwidth]{flops_graph.png}
+   \caption{An estimate of the flops used to accomplish the main processing tasks was made.
+This was accomplished by tallying all the low level operations with in addition to using the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW \cite{FFTW}.
+Although the FFT used on the MSP432 was custom, off-line implementations of the algorithms made use of FFTW}
+   \label{fig:flops_count}
+\end{figure}
 %

### 2016-09-26 notes/paper/make_flop_bar_graph.py

@@ -1,0 +1,20 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+flops = ( 3.45, 3.42, 10.22, 5.43, 8.52, 2.98, 25.56, 3.42, 25.56, 0.71, 10.71)
+names = ("Demeaning", "Signal Power", "Covariance matrix", "Eigen vectors/values", "Orient axis", "Signal norm", "Signal to frequency", "Conjugate multiply", "Frequency to correlation", "Find max correlation", "Normalize the correlation")
+
+fig, ax = plt.subplots()
+index = np.arange(len(flops))
+width = 0.5
+opacity = 1.0
+ax.set_xticks(index + width/2.0)
+rects1 = plt.bar(index, flops, width, alpha=opacity, color='#000000')
+plt.xlabel('')
+plt.ylabel("Measured Flops (% of Processing)", fontsize=16)
+plt.title("Processing Distribution", fontsize=26)
+plt.xticks(index + width/2.0, names, rotation=90, fontsize=14)
+plt.tight_layout()
+plt.savefig("flops_graph.png", bbox_inches="tight")

### 2016-09-26 notes/paper/paper.tex
Incremental changes

@@
 We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
-Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation when applied.
+Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation.
 Data decimation in time is an additional throughput enhancement that we apply early to our data.
@@
    \includegraphics[width=0.6\textwidth]{flops_graph.png}
-   \caption{An estimate of the flops used to accomplish the main processing tasks was made.
-This was accomplished by tallying all the low level operations with in addition to using the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW \cite{FFTW}.
+   \caption{An estimate of the flops used to accomplish the main processing tasks.
+This was accomplished by tallying each of the low level operations in addition to using the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW documentation \cite{FFTW}.
 Although the FFT used on the MSP432 was custom, off-line implementations of the algorithms made use of FFTW}

### 2016-09-26 notes/paper/make_flop_bar_graph.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 
 
 flops = ( 3.45, 3.42, 10.22, 5.43, 8.52, 2.98, 25.56, 3.42, 25.56, 0.71, 10.71)
-names = ("Demeaning", "Signal Power", "Covariance matrix", "Eigen vectors/values", "Orient axis", "Signal norm", "Signal to frequency", "Conjugate multiply", "Frequency to correlation", "Find max correlation", "Normalize the correlation")
+names = ("Data demeaning", "Signal power", "Covariance Matrix", "Eigen-vectors/values", "Projection onto axis", "Signal norm", "FFT", "Conjugate multiply", "Inverse FFT", "Find max correlation", "Normalizing correlation")
 
 fig, ax = plt.subplots()
 index = np.arange(len(flops))

### 2016-09-27 notes/paper/paper.tex
Incremental changes.

@@
    \centering
-   \includegraphics[width=0.6\textwidth]{flops_graph.png}
-   \caption{An estimate of the flops used to accomplish the main processing tasks.
-This was accomplished by tallying each of the low level operations in addition to using the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW documentation \cite{FFTW}.
-Although the FFT used on the MSP432 was custom, off-line implementations of the algorithms made use of FFTW}
+   \includegraphics[width=0.95\textwidth]{flops_graph.png}
+   \caption{An estimate of the processing distribution based on flop counts.
+This estimate was obtained from the source code that was used for the performance assessment.
+The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for FFTW \cite{FFTW} which was used for this performance assessment for real-FFTs.
+A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used (usual standard for testing)}
    \label{fig:flops_count}
 \end{figure}
+
+An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
+In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
+Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
+This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
+FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
 %

### 2016-09-27 notes/paper/make_flop_bar_graph.py

@@ -3,8 +3,8 @@ import numpy as np
 import matplotlib.pyplot as plt
 
 
-flops = ( 3.45, 3.42, 10.22, 5.43, 8.52, 2.98, 25.56, 3.42, 25.56, 0.71, 10.71)
-names = ("Data demeaning", "Signal power", "Covariance Matrix", "Eigen-vectors/values", "Projection onto axis", "Signal norm", "FFT", "Conjugate multiply", "Inverse FFT", "Find max correlation", "Normalizing correlation")
+flops = ( 3.02, 3.00, 8.95, 4.76, 7.46, 2.61, 22.38, 3.00, 22.38, 22.45)
+names = ("Data demeaning", "Signal power", "Covariance Matrix", "Eigen-vectors/values", "Projection onto axis", "Signal norm", "FFT", "Conjugate multiply", "Inverse FFT", "Normalization & add. proc.")
 
 fig, ax = plt.subplots()
 index = np.arange(len(flops))
@@ -12,9 +12,10 @@ width = 0.5
 opacity = 1.0
 ax.set_xticks(index + width/2.0)
 rects1 = plt.bar(index, flops, width, alpha=opacity, color='#000000')
+plt.title("Computational Cost Estimate", fontsize=26)
 plt.xlabel('')
-plt.ylabel("Measured Flops (% of Processing)", fontsize=16)
-plt.title("Processing Distribution", fontsize=26)
-plt.xticks(index + width/2.0, names, rotation=90, fontsize=14)
+plt.ylabel("Flops (% of Processing)", fontsize=16)
+plt.yticks(np.linspace(0, 25, 6), fontsize=16)
+plt.xticks(index + width/2.0, names, rotation=90, fontsize=16)
 plt.tight_layout()
 plt.savefig("flops_graph.png", bbox_inches="tight")

### 2016-09-28 mc_code/training_main.c
Fixed bug in MC training code.

@@ -65,7 +65,7 @@ void training_main(
             data_time_length,
             sampling_freq,
             1,
-            workspace);
+            (void*)workspace_float);
 
       float sum_data_correlation = 0.0f;
       

### 2016-09-28 notes/paper/paper.tex
Incremental updates to the paper

@@
-\documentclass[journal]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 \usepackage{blindtext}
@@
 %
-\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
+\author{Craig~Euler craig.euler@gmail.com, C.T.~Lin ct.lin@csun.edu,\\Bryan~Juarez bryan.juarez.974@my.csun.edu, Melissa~Flores melissa.flores.455@my.csun.edu\\College of Engineering and Computer Science\\California State University, Northridge}
 %
@@
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
+Similar to other methods that apply subspace projections \cite{low_rank_subspace}, we seek to analyze our data in a lower dimensional subspace by a projection onto the two-dimension plane that best represents our data.
 We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
@@
 
-Classification methods that are achieved from multi-dimensional feature spaces have been explored \cite{survey_multi_view_machine_learning}.
+Classification methods that make use of multi-dimensional feature spaces have been explored \cite{survey_multi_view_machine_learning}.
 In this paper, we compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
@@
    \centering
-   \includegraphics[width=0.95\textwidth]{flops_graph.png}
+   \includegraphics[width=0.99\textwidth]{flops_graph.png}
    \caption{An estimate of the processing distribution based on flop counts.
 This estimate was obtained from the source code that was used for the performance assessment.
-The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for FFTW \cite{FFTW} which was used for this performance assessment for real-FFTs.
-A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used (usual standard for testing)}
+The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW \cite{FFTW} which was used for this performance assessment.
+A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used (usual standard for our testing).}
    \label{fig:flops_count}
@@
 We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
-We have shown that real-time processing can be achieved with timing results obtained from the MSP432 microcontroller.
+We have shown that real-time processing on a low-powered micro-controller can be achieved with timing results obtained from the MSP432 microcontroller.
 Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the processing time.

### 2016-09-29 notes/paper/paper.tex
incremental changes to the paper
Edits to the paper.

@@
 In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
-We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
+We also show the real-time processing capability of our algorithms on the MSP432P401R low-powered microcontroller.
 Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation.
@@
 Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-In this paper, we make use of the matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
-The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and has been studied in the past \cite{giannakis_tsatsanis_1990}.
-The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller (we use the MSP432 microcontroller).
+The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual\textquotesingle s activity for the purpose of real-time processing on a low-powered micro-controller.
+The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
+In this paper, we use the MSP432 microcontroller for our timing results.
 
-The algorithms described in this paper are broken into two main modules: The real-time activity classification and training the device to identify the user\textquotesingle s activity.
+The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user\textquotesingle s activity.
 
@@
 
-The real-time activity classification module is intended to be performed on a microcontroller.
+The real-time activity classification module is intended to be performed on a low-powered microcontroller.
 This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
@@
 If \eqref{eq:matched_filter} passes a set threshold, then the corresponding signal $\textbf{y}$ is classified as a match to the reference $\textbf{x}$.
+
+Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
+Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on such limiting hardware resources.
+Sections \ref{sec:dim_red} and \ref{sec:decimation} will go into methods that will help reduce the computational burden of the matched-filter.
 %
-\subsection{Dimensionality Reduction}
+\subsection{Dimensionality Reduction} \label{sec:dim_red}
+Classification methods that make use of multi-dimensional feature spaces have increased in popularity and many methods exist \cite{survey_multi_view_machine_learning}.
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
@@
 %
-Equality comes from the orthonormality of $V$. The margin of error in the approximation is not important since we are only interested in processing in the two dimensions.
-By now we have preserved as much information that is contained in our acceleration data as possible while also reducing our dimension from three to two.
-By projecting our data onto the plane defined by the two most dominant eigenvectors, we effectively reduce our representation of our data to two dimensions.
+Where equality comes from the orthonormality of $V$.
+By now, we have preserved as much information that is contained in our acceleration data as possible in the process of reducing our dimensions from three to two.
 
-Classification methods that make use of multi-dimensional feature spaces have been explored \cite{survey_multi_view_machine_learning}.
 In this paper, we compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
@@
 %
-\subsection{Decimation}
+\subsection{Decimation} \label{sec:decimation}
 Decimation is the first step applied to our data before any additional processing takes place.
@@
 Samples of walking, jogging, and bicycling have been recorded with this unit and was attached to the ankle of the user.
-A separate instance of walking data has been used specifically for training the classifier.
+A separate instance of walking data was used specifically for training the classifier.
 %
@@
 \end{figure}
-%
+
 Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
@@
 This is a case setup of 32Hz sampling frequency over a 4 second time window with 2 references at decimation 8 showing the voltage output over time.
-Execution time is measured from the start to end of the ``high'' (3.3 Volts) time interval.}
+Execution time is measured from start to end of the ``high'' (3.3 Volts) time interval.}
    \label{fig:time_measure}

### 2016-09-30 notes/paper/paper.tex
Paper edits.

@@
 Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
-Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on such limiting hardware resources.
+Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on limited hardware resources.
 Sections \ref{sec:dim_red} and \ref{sec:decimation} will go into methods that will help reduce the computational burden of the matched-filter.
@@
   \frac{D+k}{D^2}, & \text{if }\ -D < k \leq 0 \\
-  \frac{D-k}{D^2}, & \text{if } D < k < D \\
+  \frac{D-k}{D^2}, & \text{if } 0 < k < D \\
   0, & \text{otherwise}
@@
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-Samples of walking, jogging, and bicycling have been recorded with this unit and was attached to the ankle of the user.
+Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
 A separate instance of walking data was used specifically for training the classifier.
@@
 The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
-Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754-compliant single-precision Floating-Point Unit (FPU) and Memory Protection Unit (MPU).
+Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
 The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
@@
 %
-Because the accelerometer was not connected to the microcontroller at the time of writing this paper, randomized data was used for the purpose of analyzing the throughput performance on the device while varying the parameters which accurately models the processing load we would expect when we do have the accelerometer connected to the microcontroller.
-Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process and operating at decimation $2$.
+The throughput performance was assessed on the MSP432 with varying parameters and randomized data.
+This can be accomplished because the processing time is not affected by the data and this also simplifies this aspect of testing.
+Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
 Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
@@
 Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
-Because the pre-processing execution time does not change with the number of references, it's observed that matched-filtering accounts for roughly $80$\% of the processing while pre-processing accounts for the other $20$\% when processing for a single reference.
+The processing that happens on the data before matched-filtering doesn't change the execution time with the number of references.
+Therefore, one can observe that matched-filtering accounts for roughly $80$\% of the processing time.
 %
@@
    \caption{An estimate of the processing distribution based on flop counts.
-This estimate was obtained from the source code that was used for the performance assessment.
-The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for real-FFTs from FFTW \cite{FFTW} which was used for this performance assessment.
-A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used (usual standard for our testing).}
+This estimate was obtained from analyzing the source code that was used for the performance assessment.
+The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for real-FFTs for FFTW \cite{FFTW} execution which was used for this performance assessment.
+A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used.}
    \label{fig:flops_count}
@@
 We have shown that real-time processing on a low-powered micro-controller can be achieved with timing results obtained from the MSP432 microcontroller.
-Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFT dominates the processing time.
+Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFTs account for a significant amount of the processing time.
 We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.

### 2016-09-30 notes/paper/make_flop_bar_graph.py

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 
 
 flops = ( 3.02, 3.00, 8.95, 4.76, 7.46, 2.61, 22.38, 3.00, 22.38, 22.45)
-names = ("Data demeaning", "Signal power", "Covariance Matrix", "Eigen-vectors/values", "Projection onto axis", "Signal norm", "FFT", "Conjugate multiply", "Inverse FFT", "Normalization & add. proc.")
+names = ("Data demeaning", "Signal power", "Covariance Matrix", "Eigen-vectors/values", "Projection onto axis", "Signal norm", "FFT", "Conjugate multiply", "Inverse FFT", "Normalization")
 
 fig, ax = plt.subplots()
 index = np.arange(len(flops))

### 2016-09-30 notes/paper/make_timing_plots.py

@@ -18,11 +18,11 @@ time_freq_75hz_dec_2_2ref = np.array([1.132, 2.377, 9.305, 4.965, 25.82, 20.48, 
 plt.figure(figsize=(12,9))
 sec4_dec8_plot_1ref, = plt.plot(freq2, time_4sec_dec_8_1ref, lw=4, color='#000000', marker='s', ms=14, linestyle='-', label="1 Reference")
 sec4_dec8_plot_2ref, = plt.plot(freq2, time_4sec_dec_8_2ref, lw=4, color='#000000', marker='^', ms=14, linestyle='--', label="2 References")
-plt.title("Timing on MSP432 at Decimation 8", fontsize=26)
-plt.xlabel("Sampling Frequency", fontsize=26)
-plt.ylabel("Execution Time (seconds)", fontsize=26)
-plt.yticks(fontsize=20)
-plt.xticks(fontsize=20)
+plt.title("Timing on MSP432 at Decimation 8", fontsize=30)
+plt.xlabel("Sampling Frequency", fontsize=30)
+plt.ylabel("Execution Time (seconds)", fontsize=30)
+plt.yticks(fontsize=30)
+plt.xticks(fontsize=30)
 plt.grid(True)
 plt.legend(handles=[sec4_dec8_plot_1ref, sec4_dec8_plot_2ref], loc='upper left', prop={'size':26})
 plt.savefig("one_and_two_references.png", bbox_inches="tight")
@@ -32,11 +32,11 @@ plt_75hz_dec2_2ref, = plt.plot(time_window, time_freq_75hz_dec_2_2ref, lw=4, mar
 plt_64hz_dec2_2ref, = plt.plot(time_window, time_freq_64hz_dec_2_2ref, lw=4, marker='^', ms=14, linestyle='--', color='#000000', label="64 Hz")
 plt_62hz_dec2_2ref, = plt.plot(time_window, time_freq_62hz_dec_2_2ref, lw=4, marker='o', ms=14, linestyle='-.', color='#000000', label="62 Hz")
 plt_50hz_dec2_2ref, = plt.plot(time_window, time_freq_50hz_dec_2_2ref, lw=4, marker='D', ms=14, linestyle=':', color='#000000', label="50 Hz")
-plt.title("Timing on MSP432 at Decimation 2 with 2 References", fontsize=26)
-plt.xlabel("Time Window Length (seconds)", fontsize=26)
[…]

### 2016-10-10 notes/poster/poster.tex
Commiting start of poster.

\documentclass[unknownkeysallowed,final]{beamer}
\usetheme{RJH} %RJH}
\usepackage[orientation=landscape,size=a2,scale=1.4,debug]{beamerposter}
\usepackage[absolute,overlay]{textpos}
\setlength{\TPHorizModule}{1cm}
\setlength{\TPVertModule}{1cm}

\usepackage{amsmath,amsthm, amssymb, latexsym}
\usepackage{multirow}
\usepackage{rotating}

\usepackage{array,booktabs,tabularx}
\newcolumntype{Z}{>{\centering\arraybackslash}X} % centered tabularx columns
\newcommand{\pphantom}{\textcolor{ta3aluminium}} % phantom introduces a vertical space in p formatted table columns??!!
\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}

\title{\normalsize{Efficient Techniques for Simulations of Kinetic Equations of Gas Dynamics}}
\author{\small{Craig Euler, \hspace{5mm} College of Science and Mathematics ,\hspace{5mm} California State University Northridge}}
\footer{}
\date{}
% \includegraphics[scale=.2]{CSUN_seal.png}}

\begin{document}
\tiny{}
\begin{frame}{}

	\begin{textblock}{19.5}(1,4)

\begin{block}{\small{Introduction}}
Numerical simulations of gas flows over sharp leading edges of air vehicles are challenging because they require the solution of model kinetic equations. These equations lead to stiff problems in regimes transitional from continuum to free molecular flow. The main difficulties in solving model kinetic equations include the loss of the conservation of mass, momentum, and energy, and low order convergence of solutions. Flows that are near continuum are well described by the Boltzmann equation with the BGK collision model:

% Boltzmann equation
\begin{equation*}
\label{ES-BGK}
\partial_{t} f(t, \vec{x}, \vec{u}) + \vec{v} \cdot \vec{\nabla}_{x} f(t, \vec{x}, \vec{v}) = \nu (f_{0} - f)
\end{equation*}
% use \ref{ES-BGK} or \eqref{ES-BGK} to get the reference for this equation

Where $f_{0}$ is the Maxwellian equilibrium distribution

% f0
\begin{equation*}
\label{f0}
f_{0} = f_{M} = \frac{\rho(t, \vec{x})}{\sqrt{(2 \pi RT(t, \vec{x}))^{3}}} \exp \left( -\frac{( \vec{v}- \vec{\bar{u}}(t, \vec{x}))^{2}}{2RT} \right)
\end{equation*}
% use \ref{f0} or \eqref{f0} to get the reference for this equation

\end{block}

\begin{block}{\small{Reduction to One Dimension}}
We assume that there is no mass transfer in the $y$ and $z$ directions (examples: gas between two parallel plates or in an infinitely wide pipe). In this case, the BGK equation reduces to

%A one dimensional reduction is performed on \eqref{ES-BGK} by assuming that no mass transfer occurs in two of the three directions in space, in this case $v_{2}$ and $v_{3}$. By considering the fallowing substitutions:

% f1
%\begin{equation*}
%\label{f1}
%f^{1} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
%\end{equation*}
% use \ref{f1} or \eqref{f1} to get the reference for this equation

% f2
%\begin{equation*}
%\label{f2}
%f^{2} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} v_{2}^2 f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
%\end{equation*}
% use \ref{f2} or \eqref{f2} to get the reference for this equation

%then by integrating \eqref{ES-BGK} over all velocity space we are left with the following reduction with $j=1,2$:

% First PDE evolution equation for f1 and f2
\begin{equation*}
\label{bgk1d1}
\partial_{t} f^{1,2}(t,x,v) + v \partial_{x} f^{1,2}(t,x,v) = Q^{1,2}(f^{1,2},v)
\lefteqn{\hspace{20mm}(1)}
\end{equation*}

%Where

\begin{equation*}
\label{Q1}
Q^{1}(f^{1},v) = \nu \left( \frac{\rho(t, x)}{\sqrt{2 \pi RT(t, x)}} \exp \left( - \frac{(v - \bar{u})^{2}}{2RT} \right) - f^{1}(t, x, v) \right)
\end{equation*}

\begin{equation*}
\label{Q2}
Q^{2}(f^{2},v) = \nu \left( \rho(t, x) \sqrt{ \frac{RT(t, x)}{2 \pi}} \exp \left( - \frac{(v - \bar{u})^{2}}{2RT} \right) - f^{2}(t, x, v) \right)
\end{equation*}

%and

% Density in 1D
%\begin{equation*}
%\label{density_1d}
%\rho(t,x) = \int_{-\infty}^{\infty} f^{1}(t, x, v) dv_{1}
%\end{equation*}
% use \ref{density_1d} or \eqref{density_1d} to get the reference for this equation

% Momentum in 1D
%\begin{equation*}
%\label{momentum_1d}
%\bar{u}(t,x) = \frac{1}{\rho(t,x)}\int_{ -\infty}^{\infty} v_{1} f^{1}(t, x, v_{1}) dv_{1}
%\end{equation*}
% use \ref{momentum_1d} or \eqref{momentum_1d} to get the reference for this equation

% Temperature in 1D
%\begin{equation*}
%\label{temperature_1d}
%T(t,x) = \frac{1}{3R \rho(t,x)} \int_{-\infty}^{\infty} \left[ (v_{1} - \bar{u})^{2} f^{1}(t, x, v_{1}) + 2 f^{2}(t, x, v_{1}) \right]dv_{1}
%\end{equation*}
% use \ref{temperature_1d} or \eqref{temperature_1d} to get the reference for this equation

Where $f^{1} = \int f \, dv \, dw $ can be a reduced molecular distribution function and $f^{2} = \int v^{2} f \, dv \, dw $.
\end{block}

\begin{block}{\small{DG Velocity Discretization}}
We let $V=[v_{L}, v_{R}]$ be an interval large enough so that the first moment integrals of the distribution function outside of it are negligible and let it be partitioned into subintervals $I_{i}=[v_{i-1/2},v_{1+1/2}]$. Let $\chi_{p}$ and $\omega_{p}$, $p=1,\ldots,s$ denote the nodes and weights of the Gaussian quadrature of order $P$ on the interval $[-1,1]$. On $[v_{i-1/2},v_{i+1/2}]$ we define

\begin{equation*}
\label{Chi}
\chi_{p,i} = \frac{v_{i+1/2} + v_{i-1/2}}{2} + \chi_{p}\frac{v_{i+1/2} - v_{i-1/2}}{2}.
\end{equation*}
% use \ref{Chi} or \eqref{Chi} to get the reference for this equation

Our basis functions $\varphi_{p,i}(v)$ are
\begin{equation*}
\varphi_{p,i}(v) = \prod\limits_{q=1,s \atop q \neq p} \frac{v-\chi_{q,i}}{\chi_{p,i} - \chi_{q,i}}.
\end{equation*}
\end{block}

	\end{textblock}

	\begin{textblock}{18}(21.8,4)

 \begin{block}{\small{}}
Notice that basis functions satisfy the orthogonality properties

\begin{equation*}
\int_{v_{i-1/2}}^{v_{i+1/2}} \phi_{p,i}(v) \phi_{q,i}(v) = \frac{\Delta v_{i}}{2} \omega_{p} \delta_{p,q}
\end{equation*}

and

\begin{equation*}
\int_{v_{i-1/2}}^{v_{i+1/2}} v \phi_{p,i}(v) \phi_{q,i}(v) = \frac{\Delta v_{i}}{2} \chi_{p,q} \omega_{p} \delta_{p,q},
\end{equation*}

where $\delta_{p,q}$ is the Kronecker delta function.

The discrete velocity approximations of $f^{1,2}(t,x,v)$ are defined by

\begin{equation*}
\label{eq0x}
f^{1,2}(t,x,v)=\sum_{p=1} ^{s} f_{p,i}^{1,2}(t,x) \varphi_{p,i}(v).
\end{equation*}
% use \ref{base} or \eqref{base} to get the reference for this equation
Substituting the discrete velocity approximations into (1) and multiplying by our basis functions and integrating through velocity, after simplification we arrive at

\begin{equation*}
\label{eqint}
\partial_{t} f_{q,i}^{1,2}(t,x) + \chi_{p,i} \partial_{x} f_{q,i}^{1,2}(t,x) = Q^{1,2}(f^{1,2},\chi_{p,i}).
\end{equation*}

Notice that these equations have the form of a first order symmetric hyperbolic system.

\end{block}

\begin{block}{\small{Clawpack}}
Clawpack is a software package developed by LeVeque et al [1]. It is designed to provide solutions to Hyperbolic PDEs in 1 and 2 dimensions and of first or second orders. Current implementations of Clawpack include Geoclaw for Tsunami modelling and other geophysical flows. In our implementation, we seek to extend Clawpack to use for the solution of the model Boltzmann equations.
\end{block}

\begin{block}{\small{One Dimensional Heat Transfer}}
Nitrogen gas at 300K between two infinitely long parallel plates. The plate on the left is at 0m and is heated to 1000K. The plate on the right is at 0.1m and is heated to 300K. At 0.03 seconds the solution is observed to be near steady state.\\[2mm]
Our first experiment is to study the relative error in the total mass. The number of cells in space ranged from 10-100 and the number of cells through velocity ranged from 6 to 16 with a scheme order of 10 for velocity approximation.
We observed by varying the number of velocity cells we can reduce the error to a factor of $10^{-10}$. It is observed that varying the number of cells in the spatial variable $x$ has little effect on the conservation of mass as seen in the table below.

\end{block}
	\end{textblock}

	\begin{textblock}{17.3}(41,4)

\begin{block}{\small{}}

\begin{center}
	\begin{tabular}{ cc || c | c | c | c | c | c | c | c | c | r |}

& & \multicolumn{4}{| c |}{Number of velocity cells}\\
& & 6 & 8 & 12 & 16\\ \hline \hline
\multirow{10}{*}{\begin{sideways}{Number of spatial cells}\end{sideways}}
& 10 & 5.30E-07 & 1.83E-09 & 1.26E-09 & 2.16E-10\\ \cline{2-6}
& 20 & 5.33E-07 & 1.34E-09 & 7.81E-10 & 4.33E-10\\ \cline{2-6}
& 30 & 5.24E-07 & 1.44E-08 & 1.02E-08 & 9.34E-09\\ \cline{2-6}
& 40 & 5.33E-07 & 2.53E-09 & 7.89E-10 & 6.15E-10\\ \cline{2-6}
& 50 & 5.34E-07 & 2.12E-09 & 1.26E-09 & 3.06E-11\\ \cline{2-6}
& 60 & 5.54E-07 & 1.63E-08 & 1.93E-08 & 2.02E-08\\ \cline{2-6}
& 70 & 5.13E-07 & 2.25E-08 & 1.94E-08 & 1.93E-08\\ \cline{2-6}
& 80 & 5.34E-07 & 3.18E-09 & 2.73E-10 & 1.19E-09\\ \cline{2-6}
& 90 & 5.25E-07 & 1.24E-08 & 9.60E-09 & 9.79E-09\\ \cline{2-6}
& 100 & 5.33E-07 & 2.54E-09 &  5.10E-10 & 1.14E-10\\ \hline

\hline
	\end{tabular}
\end{center}

The convergence of the L2 norm of the error in macroparameters with respect to the resolution in the spatial variable can be seen in the table below. The solutions are compared to solutions on 1000 cells. The velocity discretization is by a scheme of order 10 on 10 velocity cells.

\begin{center}
	\begin{tabular}{ lc || c | c | c | c |}

& & \multicolumn{4}{| c |}{Number of spatial cells}\\
& & 50 & 100 & 150 & 200\\ \hline \hline
& Density & 0.03054 & 0.01737 & 0.01198 & 0.008234\\ \cline{2-6}
& Momentum & 17.06 & 8.383 & 5.368 & 3.842\\ \cline{2-6}
& Temperature & 0.03967 & 0.02408 & 0.01652 & 0.01062\\ \hline

\hline
	\end{tabular}
\end{center}

\end{block}

\begin{block}{\small{Steady State Solution}}
\begin{center}
\includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
\end{center}
\end{block}

\begin{block}{\small{References}}
% http://depts.washington.edu/clawpack/users-4.6/about.html#authors
[1] R. J. LeVeque, M. J. Berger, et. al., Clawpack Software 4.5.1, www.clawpack.org, June 2011
\end{block}

	\end{textblock}

\end{frame}
\end{document}

### 2016-10-10 notes/poster/poster.tex
Added more poster specifics

@@
 
-\title{\normalsize{Efficient Techniques for Simulations of Kinetic Equations of Gas Dynamics}}
-\author{\small{Craig Euler, \hspace{5mm} College of Science and Mathematics ,\hspace{5mm} California State University Northridge}}
+% Poster size can be: 36" wide by 44" tall
+
+\title{\normalsize{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}}
+\author{\small{Craig~Euler craig.euler@gmail.com, C.T.~Lin ct.lin@csun.edu,\\Bryan~Juarez bryan.juarez.974@my.csun.edu, Melissa~Flores melissa.flores.455@my.csun.edu\\College of Engineering and Computer Science\\California State University, Northridge}}
+
 \footer{}
 \date{}
-% \includegraphics[scale=.2]{CSUN_seal.png}}
 
@@
 
-	\begin{textblock}{19.5}(1,4)
+\begin{textblock}{19.5}(1, 7)
 
 \begin{block}{\small{Introduction}}
-Numerical simulations of gas flows over sharp leading edges of air vehicles are challenging because they require the solution of model kinetic equations.
-These equations lead to stiff problems in regimes transitional from continuum to free molecular flow.
-The main difficulties in solving model kinetic equations include the loss of the conservation of mass, momentum, and energy, and low order convergence of solutions.
-Flows that are near continuum are well described by the Boltzmann equation with the BGK collision model:
+
+Various methods for activity classification using body-worn sensors exist.
+Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
+%The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual\textquotesingle s activity for the purpose of real-time processing on a low-powered micro-controller.
+The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
+In this paper, we use the MSP432 microcontroller for our timing results.
+
+%The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user\textquotesingle s activity.
+
+The training module does not need to be performed in real time.
+%This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, which means that this can be performed on an external device such as a smart phone or tablet.
+The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.
+
+The real-time activity classification module is intended to be performed on a low-powered microcontroller.
+%This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
+Both of these modules use the same principles and hence the same algorithm kernels.
 
@@
 We assume that there is no mass transfer in the $y$ and $z$ directions (examples: gas between two parallel plates or in an infinitely wide pipe). In this case, the BGK equation reduces to
-
-%A one dimensional reduction is performed on \eqref{ES-BGK} by assuming that no mass transfer occurs in two of the three directions in space, in this case $v_{2}$ and $v_{3}$.
-By considering the fallowing substitutions:
-
-% f1
-%\begin{equation*}
-%\label{f1}
-%f^{1} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
-%\end{equation*}
-% use \ref{f1} or \eqref{f1} to get the reference for this equation
-
-% f2
-%\begin{equation*}
-%\label{f2}
-%f^{2} (t,x,v_{1}) = \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} v_{2}^2 f(t, \vec{x}, \vec{v}) dv_{2} dv_{3}
-%\end{equation*}
-% use \ref{f2} or \eqref{f2} to get the reference for this equation
-
-%then by integrating \eqref{ES-BGK} over all velocity space we are left with the following reduction with $j=1,2$:
 
@@
 \begin{block}{\small{References}}
-% http://depts.washington.edu/clawpack/users-4.6/about.html#authors
-[1] R. J. LeVeque, M. J. Berger, et. al., Clawpack Software 4.5.1, www.clawpack.org, June 2011
+\bibliographystyle{plain}
+\bibliography{reference}
+
 \end{block}

### 2016-10-15 notes/poster/poster.tex
Incremental updates to the poster.

@@
 
+%%
+%% Text block
+%%
 \begin{textblock}{19.5}(1, 7)
@@
 \begin{block}{\small{Introduction}}
-
 Various methods for activity classification using body-worn sensors exist.
 Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-%The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual\textquotesingle s activity for the purpose of real-time processing on a low-powered micro-controller.
+The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual's activity for the purpose of real-time processing on a low-powered micro-controller.
 The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
@@
 
-%The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user\textquotesingle s activity.
+The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user's activity.
 
 The training module does not need to be performed in real time.
-%This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, which means that this can be performed on an external device such as a smart phone or tablet.
+This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user's activity, which means that this can be performed on an external device such as a smart phone or tablet.
 The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.
@@
 The real-time activity classification module is intended to be performed on a low-powered microcontroller.
-%This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
+This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual's activity.
 Both of these modules use the same principles and hence the same algorithm kernels.
+\end{block}
 
-% Boltzmann equation
-\begin{equation*}
-\label{ES-BGK}
-\partial_{t} f(t, \vec{x}, \vec{u}) + \vec{v} \cdot \vec{\nabla}_{x} f(t, \vec{x}, \vec{v}) = \nu (f_{0} - f)
-\end{equation*}
-% use \ref{ES-BGK} or \eqref{ES-BGK} to get the reference for this equation
+%%
+%% Activity Classification Method
+%%
+\begin{block}{\small{Activity Classification Method}}
 
-Where $f_{0}$ is the Maxwellian equilibrium distribution
+The matched-filter method is commonly used for extracting a signal out of noisy data.
+We use this method for identifying a user's activity from data generated by body-worn accelerometers.
+Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
+We will discuss how we develop our set of templates for use in our matched-filter in section \ref{sec:training}.
 
-% f0
-\begin{equation*}
-\label{f0}
-f_{0} = f_{M} = \frac{\rho(t, \vec{x})}{\sqrt{(2 \pi RT(t, \vec{x}))^{3}}} \exp \left( -\frac{( \vec{v}- \vec{\bar{u}}(t, \vec{x}))^{2}}{2RT} \right)
-\end{equation*}
-% use \ref{f0} or \eqref{f0} to get the reference for this equation
+The matched-filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
+The cross correlation of $\textbf{x}$ with $\textbf{y}$ is defined as:
+%
+\begin{equation} \label{eq:cross_correlation}
+(\textbf{x} \star \textbf{y}) := \left \{\sum_{i=0}^{M-1}x_{i} y_{i+k} \right \}_{k=0}^{N-M-1}
+\end{equation}
+%
+which is simply a moving dot product.
+We can then normalize \eqref{eq:cross_correlation} by the following:
+%
+\begin{equation} \label{eq:norm_cross_correlation}
+\widehat{(\textbf{x} \star \textbf{y})}_k := \frac{(\textbf{x} \star \textbf{y})_k}{||\textbf{x}|| \ || \widetilde{\textbf{y}}_k || }, \quad k = 0,1,...,N-M-1
+\end{equation}
+%
+where $|| \cdot ||$ is the usual $\ell_2$ norm and $\widetilde{\textbf{y}}_k = \{y_p\}_{p=k}^{M+k-1}$.
+\eqref{eq:norm_cross_correlation} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
+We improve our computational efficiency by applying the convolution theorem to \eqref{eq:cross_correlation} and replacing it with:
+%
+\begin{equation} \label{eq:conv_theorem}
+(\textbf{x} \star \textbf{y}) := FFT^{-1}(FFT(\textbf{x}') FFT(\textbf{y})^*)
+\end{equation}
+%
+where $\textbf{x}'$ is $\textbf{x}$ that has been zero padded to the length of $\textbf{y}$ with the added restriction that the length of $\textbf{x}$ is no more than the length of $\textbf{y}$ and $FFT$ is the Fast Fourier Transform algorithm.
+We are most interested where our reference $\textbf{x}$ best matches our data $\textbf{y}$.
+We use the resulting max correlation to define our metric for  our matched-filter output as:
+%
+\begin{equation} \label{eq:matched_filter}
+MF_{\textbf{x}}(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x} \star \textbf{y})}_k \right \}
+\end{equation}
+%
+If \eqref{eq:matched_filter} passes a set threshold, then the corresponding signal $\textbf{y}$ is classified as a match to the reference $\textbf{x}$.
+
+Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
+Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on limited hardware resources.
+Sections \ref{sec:dim_red} and \ref{sec:decimation} will go into methods that will help reduce the computational burden of the matched-filter.
+\end{block}
+\end{textblock}
+
+\begin{textblock}{18}(21.8,4)
+
+\begin{block}{\small{Dimensionality Reduction}}
+
+Classification methods that make use of multi-dimensional feature spaces have increased in popularity and many methods exist \cite{survey_multi_view_machine_learning}.
+We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
+Similar to other methods that apply subspace projections \cite{low_rank_subspace}, we seek to analyze our data in a lower dimensional subspace by a projection onto the two-dimension plane that best represents our data.
+We assume that over a short period of time, a user's limb movement is constrained mostly to a two-dimensional plane.
+By identifying this plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
+%
+If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (where each $a_i$ is represented as a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
+The resulting unit length column eigenvectors of $Q$ are $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigenvalues $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
+Here, we use superscripts to identify the axis directions in ascending order to represent the primary, secondary, and tertiary principal axis directions respectively.
+%
+\begin{equation} \label{eq:project}
+   \textbf{a}' := V^T \textbf{a}
+\end{equation}
+%
+We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{eq:project}.
+If the data is mostly dominate in the two primary dimensions, i.e.
+$\lambda^3 << \lambda^2$, then it is safe to assume that
+%
+\begin{equation} \label{eq:magnitude}
+||(a_x,a_y,a_z)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
+\end{equation}
+$ \forall a \in \textbf{a}. $ \\
+%
+Where equality comes from the orthonormality of $V$.
+By now, we have preserved as much information that is contained in our acceleration data as possible in the process of reducing our dimensions from three to two.
+
+In this paper, we compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
+%
+\begin{equation} \label{eq:cross_correlation_2}
+\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k := \frac{(\textbf{x}^1 \star \textbf{y}^1)_k + (\textbf{x}^2 \star \textbf{y}^2)_k}{||[ \textbf{x}^1, \textbf{x}^2 ]|| \ || [ \widetilde{\textbf{y}}_k^1, \widetilde{\textbf{y}}_k^2 ] || },
+\end{equation}
+%
+for $ k = 0,1,...,N-M-1 $. \\
+%
+\begin{equation} \label{eq:matched_filter_2}
+MF_{\textbf{x}}^2(\textbf{y}) := \underset{k \in [0, M-N)}{max} \left \{\widehat{(\textbf{x}^{1,2} \star \textbf{y}^{1,2})}_k \right \}
+\end{equation}
+%
+This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
+Here, the superscripts $1$ and $2$ represent the primary and secondary principal components of our data respectively.
+%
 
@@
 
-\begin{block}{\small{Reduction to One Dimension}}
-We assume that there is no mass transfer in the $y$ and $z$ directions (examples: gas between two parallel plates or in an infinitely wide pipe). In this case, the BGK equation reduces to
+\begin{block}{\small{Decimation}}
+Decimation is the first step applied to our data before any additional processing takes place.
+Decimation is a process of reducing the sampling rate of the signal by filtering to mitigate any possible distortion effects due to aliasing followed by downsampling.
+Because real-time performance is important, we decimate our signal for the purpose of improving our throughput.
 
-% First PDE evolution equation for f1 and f2
-\begin{equation*}
-\label{bgk1d1}
-\partial_{t} f^{1,2}(t,x,v) + v \partial_{x} f^{1,2}(t,x,v) = Q^{1,2}(f^{1,2},v)
-\lefteqn{\hspace{20mm}(1)}
-\end{equation*}
-
-%Where
-
-\begin{equation*}
-\label{Q1}
-Q^{1}(f^{1},v) = \nu \left( \frac{\rho(t, x)}{\sqrt{2 \pi RT(t, x)}} \exp \left( - \frac{(v - \bar{u})^{2}}{2RT} \right) - f^{1}(t, x, v) \right)
-\end{equation*}
-
-\begin{equation*}
-\label{Q2}
-Q^{2}(f^{2},v) = \nu \left( \rho(t, x) \sqrt{ \frac{RT(t, x)}{2 \pi}} \exp \left( - \frac{(v - \bar{u})^{2}}{2RT} \right) - f^{2}(t, x, v) \right)
-\end{equation*}
-
-%and
-
-% Density in 1D
-%\begin{equation*}
-%\label{density_1d}
-%\rho(t,x) = \int_{-\infty}^{\infty} f^{1}(t, x, v) dv_{1}
-%\end{equation*}
-% use \ref{density_1d} or \eqref{density_1d} to get the reference for this equation
-
-% Momentum in 1D
-%\begin{equation*}
-%\label{momentum_1d}
-%\bar{u}(t,x) = \frac{1}{\rho(t,x)}\int_{ -\infty}^{\infty} v_{1} f^{1}(t, x, v_{1}) dv_{1}
-%\end{equation*}
-% use \ref{momentum_1d} or \eqref{momentum_1d} to get the reference for this equation
-
-% Temperature in 1D
-%\begin{equation*}
-%\label{temperature_1d}
-%T(t,x) = \frac{1}{3R \rho(t,x)} \int_{-\infty}^{\infty} \left[ (v_{1} - \bar{u})^{2} f^{1}(t, x, v_{1}) + 2 f^{2}(t, x, v_{1}) \right]dv_{1}
-%\end{equation*}
-% use \ref{temperature_1d} or \eqref{temperature_1d} to get the reference for this equation
-
-Where $f^{1} = \int f \, dv \, dw $ can be a reduced molecular distribution function and $f^{2} = \int v^{2} f \, dv \, dw $.
-\end{block}
-
-\begin{block}{\small{DG Velocity Discretization}}
-We let $V=[v_{L}, v_{R}]$ be an interval large enough so that the first moment integrals of the distribution function outside of it are negligible and let it be partitioned into subintervals $I_{i}=[v_{i-1/2},v_{1+1/2}]$.
-Let $\chi_{p}$ and $\omega_{p}$, $p=1,\ldots,s$ denote the nodes and weights of the Gaussian quadrature of order $P$ on the interval $[-1,1]$.
-On $[v_{i-1/2},v_{i+1/2}]$ we define
-
-\begin{equation*}
-\label{Chi}
-\chi_{p,i} = \frac{v_{i+1/2} + v_{i-1/2}}{2} + \chi_{p}\frac{v_{i+1/2} - v_{i-1/2}}{2}.
-\end{equation*}
-% use \ref{Chi} or \eqref{Chi} to get the reference for this equation
-
-Our basis functions $\varphi_{p,i}(v)$ are
-\begin{equation*}
-\varphi_{p,i}(v) = \prod\limits_{q=1,s \atop q \neq p} \frac{v-\chi_{q,i}}{\chi_{p,i} - \chi_{q,i}}.
-\end{equation*}
+For a decimation value of $D$, we define our triangle filter with the following weights:
+%
+\begin{equation} \label{eq:triangle_filter_weights}
+w_k^D :=
+\begin{cases}
+  \frac{D+k}{D^2}, & \text{if }\ -D < k \leq 0 \\
+  \frac{D-k}{D^2}, & \text{if } 0 < k < D \\
+  0, & \text{otherwise}
+\end{cases}
+\end{equation}
+%
+and convolve it with our data to get
+%
+\begin{equation} \label{eq:convolve}
+s'_k := \sum_{i=0}^{N} s_i w_{k-i}
+\end{equation}
+%
+followed by a downsample
+%
+\begin{equation} \label{eq:downsample}
+s''_k := s'_{(k+1)D-1}, \quad k = 0, 1, 2, ..., N/D.
+\end{equation}
+%
+The processing cost is reduced by only processing points in \eqref{eq:convolve} that we keep in \eqref{eq:downsample}.
 \end{block}
@@
 
-\begin{textblock}{18}(21.8,4)
+%%
+%% Text block
+%%
+\begin{textblock}{17.3}(41,4)
+\begin{block}{\small{Training the Module}}
 
- \begin{block}{\small{}}
-Notice that basis functions satisfy the orthogonality properties
+We are able to identify an individual's activity by matching the signal to a reference template.
+For our application, we develop a reference template for our matched-filter directly from the person's motion signature.
+We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
+For a given activity, we attempt to find the representative periodic signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.
 
-\begin{equation*}
-\int_{v_{i-1/2}}^{v_{i+1/2}} \phi_{p,i}(v) \phi_{q,i}(v) = \frac{\Delta v_{i}}{2} \omega_{p} \delta_{p,q}
-\end{equation*}
+If $\textbf{t} = \{t_k\}_{k=0}^{N_t}$ is our training set over $N_t$ data points, we define a collection of subsets $X$ of $\textbf{t}$:
+%
+\begin{equation} \label{eq:X_subsets_of_training_eq}
+X := \left \{ \{t_k\}_{k=p}^{p+M-1} | p=mI \right \}
+\end{equation}
+%
+and $Y$ of $\textbf{t}$:
+%
+\begin{equation} \label{eq:Y_subsets_of_training_eq}
+Y := \left \{ \{t_k\}_{k=p}^{p+N-1} | p=nI \right \}
+\end{equation}
+%
+where $M \leq N$, $I$ is a positive, fixed integer, and $(m,n) \in \mathbb{Z}^2$ where $(m,n)$ vary such that $0 \leq (m,n)I$ and $(m,n)I + (M,N) - 1 \leq N_t$.
+Then we can determine the representative signal $\textbf{s} \in X$ for our activity that satisfies the condition:
+%
+\begin{equation} \label{eq:s_condition}
+\sum_{y \in Y}MF^2_{\textbf{s}}(\textbf{y}) \geq \sum_{y \in Y}MF^2_{\textbf{x}}(\textbf{y}), \quad \forall \textbf{x} \in X
+\end{equation}
 
-and
-
-\begin{equation*}
-\int_{v_{i-1/2}}^{v_{i+1/2}} v \phi_{p,i}(v) \phi_{q,i}(v) = \frac{\Delta v_{i}}{2} \chi_{p,q} \omega_{p} \delta_{p,q},
-\end{equation*}
-
-where $\delta_{p,q}$ is the Kronecker delta function.
-
-The discrete velocity approximations of $f^{1,2}(t,x,v)$ are defined by
-
-\begin{equation*}
-\label{eq0x}
-f^{1,2}(t,x,v)=\sum_{p=1} ^{s} f_{p,i}^{1,2}(t,x) \varphi_{p,i}(v).
-\end{equation*}
-% use \ref{base} or \eqref{base} to get the reference for this equation
-Substituting the discrete velocity approximations into (1) and multiplying by our basis functions and integrating through velocity, after simplification we arrive at
-
-\begin{equation*}
-\label{eqint}
-\partial_{t} f_{q,i}^{1,2}(t,x) + \chi_{p,i} \partial_{x} f_{q,i}^{1,2}(t,x) = Q^{1,2}(f^{1,2},\chi_{p,i}).
-\end{equation*}
-
-Notice that these equations have the form of a first order symmetric hyperbolic system.
-
-\end{block}
-
-\begin{block}{\small{Clawpack}}
-Clawpack is a software package developed by LeVeque et al [1].
-It is designed to provide solutions to Hyperbolic PDEs in 1 and 2 dimensions and of first or second orders.
-Current implementations of Clawpack include Geoclaw for Tsunami modelling and other geophysical flows.
-In our implementation, we seek to extend Clawpack to use for the solution of the model Boltzmann equations.
-\end{block}
-
-\begin{block}{\small{One Dimensional Heat Transfer}}
-Nitrogen gas at 300K between two infinitely long parallel plates.
-The plate on the left is at 0m and is heated to 1000K.
-The plate on the right is at 0.1m and is heated to 300K.
-At 0.03 seconds the solution is observed to be near steady state.\\[2mm]
-Our first experiment is to study the relative error in the total mass.
-The number of cells in space ranged from 10-100 and the number of cells through velocity ranged from 6 to 16 with a scheme order of 10 for velocity approximation.
-We observed by varying the number of velocity cells we can reduce the error to a factor of $10^{-10}$.
-It is observed that varying the number of cells in the spatial variable $x$ has little effect on the conservation of mass as seen in the table below.
-
-\end{block}
-\end{textblock}
-
-\begin{textblock}{17.3}(41,4)
-
-\begin{block}{\small{}}
+We chose this method for its simplicity and robustness against outliers in our training set.
+We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
 
 \begin{center}
-\begin{tabular}{ cc || c | c | c | c | c | c | c | c | c | r |}
-
-& & \multicolumn{4}{| c |}{Number of velocity cells}\\
-& & 6 & 8 & 12 & 16\\ \hline \hline
-\multirow{10}{*}{\begin{sideways}{Number of spatial cells}\end{sideways}}
-& 10 & 5.30E-07 & 1.83E-09 & 1.26E-09 & 2.16E-10\\ \cline{2-6}
-& 20 & 5.33E-07 & 1.34E-09 & 7.81E-10 & 4.33E-10\\ \cline{2-6}
-& 30 & 5.24E-07 & 1.44E-08 & 1.02E-08 & 9.34E-09\\ \cline{2-6}
-& 40 & 5.33E-07 & 2.53E-09 & 7.89E-10 & 6.15E-10\\ \cline{2-6}
-& 50 & 5.34E-07 & 2.12E-09 & 1.26E-09 & 3.06E-11\\ \cline{2-6}
-& 60 & 5.54E-07 & 1.63E-08 & 1.93E-08 & 2.02E-08\\ \cline{2-6}
-& 70 & 5.13E-07 & 2.25E-08 & 1.94E-08 & 1.93E-08\\ \cline{2-6}
-& 80 & 5.34E-07 & 3.18E-09 & 2.73E-10 & 1.19E-09\\ \cline{2-6}
-& 90 & 5.25E-07 & 1.24E-08 & 9.60E-09 & 9.79E-09\\ \cline{2-6}
-& 100 & 5.33E-07 & 2.54E-09 &  5.10E-10 & 1.14E-10\\ \hline
-
-\hline
-\end{tabular}
-\end{center}
-
-The convergence of the L2 norm of the error in macroparameters with respect to the resolution in the spatial variable can be seen in the table below.
-The solutions are compared to solutions on 1000 cells.
-The velocity discretization is by a scheme of order 10 on 10 velocity cells.
-
-\begin{center}
-\begin{tabular}{ lc || c | c | c | c |}
-
-& & \multicolumn{4}{| c |}{Number of spatial cells}\\
-& & 50 & 100 & 150 & 200\\ \hline \hline
-& Density & 0.03054 & 0.01737 & 0.01198 & 0.008234\\ \cline{2-6}
-& Momentum & 17.06 & 8.383 & 5.368 & 3.842\\ \cline{2-6}
-& Temperature & 0.03967 & 0.02408 & 0.01652 & 0.01062\\ \hline
-
-\hline
-\end{tabular}
-\end{center}
-
-\end{block}
-
-\begin{block}{\small{Steady State Solution}}
-\begin{center}
-\includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
+% \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
 \end{center}
@@
 \bibliography{reference}
-
 \end{block}
-
 \end{textblock}

### 2016-10-16 notes/poster/poster.tex
Incremental additions to the poster. Added softlinks to the python scripts that generate the figures. Poster now has entirety of paper contents.

@@
 \begin{block}{\small{Dimensionality Reduction}}
-
 Classification methods that make use of multi-dimensional feature spaces have increased in popularity and many methods exist \cite{survey_multi_view_machine_learning}.
@@
 %
-
 \end{block}
@@
 \begin{textblock}{17.3}(41,4)
+
 \begin{block}{\small{Training the Module}}
@@
 
-\begin{center}
+%\begin{center}
 % \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
-\end{center}
+%\end{center}
 \end{block}
 
+\begin{block}{\small{Performance}}
+%The Kinetisense sensor was used for the algorithm performance analysis in this paper.
+%This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
+%Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
+%A separate instance of walking data was used specifically for training the classifier.
+%%
+%\begin{figure}[!ht]
+%  %\captionsetup[subfigure]{labelformat=empty}
+%  \centering
+%  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+%  \quad
+%  \centering
+%  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+%  \centering
+%  \quad
+%  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
+%  \centering
+%  \quad
+%  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
+%  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
+Results produced at decimation 8.
+Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
+%  \label{fig:MF_performance}
+%\end{figure}
+%
+%Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
+%As we would expect, the walking data reference matches better to walking data than to the other activities.
+The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
+%ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
+%Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
+%
+%To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
+%The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
+%Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
+%The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
+%The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
+%the 256 kB is more than enough flash memory to store the program and data references.
+%The clock frequency operates at 48 MHz which drives the execution speed.
+%
+%\begin{figure}[!ht]
+%   \centering
+%   \includegraphics[width=0.45\textwidth]{reference_pulse_32Hz_4sec_8downsample_2.png}
+%   \caption{Oscilloscope output used for measuring the processing time of the algorithms on the MSP432.
+This is a case setup of 32Hz sampling frequency over a 4 second time window with 2 references at decimation 8 showing the voltage output over time.
+%Execution time is measured from start to end of the ``high'' (3.3 Volts) time interval.}
+%   \label{fig:time_measure}
+%\end{figure}
+%%
+%The ``Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer'' oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
+%When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
+%This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-filtering (end of algorithm processing).
+%The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
+%An example can be seen in Figure \ref{fig:time_measure}.
+%
+%\begin{figure}[!ht]
+%   \centering
+%   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
+%   \quad
+%   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
+%   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
+The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
+%   \label{fig:timing}
+%\end{figure}
+%%
+%The throughput performance was assessed on the MSP432 with varying parameters and randomized data.
+%This can be accomplished because the processing time is not affected by the data and this also simplifies this aspect of testing.
+%Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
+%Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
+Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
+%Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
+%The processing that happens on the data before matched-filtering doesn't change the execution time with the number of references.
+%Therefore, one can observe that matched-filtering accounts for roughly $80$\% of the processing time.
+%%
+%\begin{figure}[!ht]
+%   \centering
+%   \includegraphics[width=0.99\textwidth]{flops_graph.png}
+%   \caption{An estimate of the processing distribution based on flop counts.
+This estimate was obtained from analyzing the source code that was used for the performance assessment.
+The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for real-FFTs for FFTW \cite{FFTW} execution which was used for this performance assessment.
+A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used.}
+%   \label{fig:flops_count}
+%\end{figure}
+%
+%An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
+%In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
+%Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
+%This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
+%FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
+\end{block}
+%
+\begin{block}{\small{Conclusion}}
+%We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
+%We have shown that real-time processing on a low-powered micro-controller can be achieved with timing results obtained from the MSP432 microcontroller.
+%Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFTs account for a significant amount of the processing time.
+%We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
+%The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
+\end{block}
+%
 \begin{block}{\small{References}}

### 2016-10-16 notes/poster/make_flop_bar_graph.py

@@ -1,0 +1,1 @@
+../paper/make_flop_bar_graph.py

### 2016-10-16 notes/poster/make_graphs_walking_biking.py

@@ -1,0 +1,1 @@
+../paper/make_graphs_walking_biking.py

### 2016-10-16 notes/poster/make_graphs_walking_running.py

@@ -1,0 +1,1 @@
+../paper/make_graphs_walking_running.py

### 2016-10-16 notes/poster/make_timing_plots.py

@@ -1,0 +1,1 @@
+../paper/make_timing_plots.py

### 2016-10-19 notes/poster/poster.tex
Added abstract.

@@
 \begin{textblock}{19.5}(1, 7)
+
+\begin{block}{\small{Abstract}}
+Having information of a user's activity can provide great use in modern-day devices such as ones that track and monitor the user's activity and fitness.
+In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
+We also show the real-time processing capability of our algorithms on the MSP432P401R low-powered microcontroller.
+Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making     our data invariant to sensor orientation.
+Data decimation in time is an additional throughput enhancement that we apply early to our data.
+We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity templates for use in our matched-filter.
+\end{block}
 

### 2016-10-19 notes/poster/poster.tex
Incremental changes to the poster. Specifically to the introduction.

@@
 Having information of a user's activity can provide great use in modern-day devices such as ones that track and monitor the user's activity and fitness.
-In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
+We demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
 We also show the real-time processing capability of our algorithms on the MSP432P401R low-powered microcontroller.
@@
 \begin{block}{\small{Introduction}}
-Various methods for activity classification using body-worn sensors exist.
-Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual's activity for the purpose of real-time processing on a low-powered micro-controller.
-The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
-In this paper, we use the MSP432 microcontroller for our timing results.
+We adopt the matched-filter method for classification to identify an individual's activity in real-time processing on a low-powered micro-controller.
+Our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
+Timing tests were performed on the MSP432 microcontroller.
 
-The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user's activity.
+Two main algorithms are described here: The activity classification module for real-time processing and the training module to train the device to identify the user's activity for the purpose of real-time activity classification.
 
-The training module does not need to be performed in real time.
-This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user's activity, which means that this can be performed on an external device such as a smart phone or tablet.
-The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.
-
-The real-time activity classification module is intended to be performed on a low-powered microcontroller.
-This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual's activity.
-Both of these modules use the same principles and hence the same algorithm kernels.
+Because training module does not need to be performed in real time, this can be performed on an external device such as a smart phone or tablet where processing resources are in greater abundance.
+Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.
 \end{block}

### 2016-10-22 notes/poster/poster.tex
Incremental changes to the poster.

@@
 
+%%%%%%%%%%%%
+% Abstract %
+%%%%%%%%%%%%
 \begin{block}{\small{Abstract}}
@@
 
+%%%%%%%%%%%%%%%%
+% Introduction %
+%%%%%%%%%%%%%%%%
 \begin{block}{\small{Introduction}}
@@
 
-%%
-%% Activity Classification Method
-%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Activity Classification Method %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{block}{\small{Activity Classification Method}}
-
-The matched-filter method is commonly used for extracting a signal out of noisy data.
-We use this method for identifying a user's activity from data generated by body-worn accelerometers.
-Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
-We will discuss how we develop our set of templates for use in our matched-filter in section \ref{sec:training}.
-
+We use the matched-filter method for identifying a user's activity from data generated by body-worn accelerometers.
 The matched-filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
@@
 %
-which is simply a moving dot product.
 We can then normalize \eqref{eq:cross_correlation} by the following:
@@
 where $|| \cdot ||$ is the usual $\ell_2$ norm and $\widetilde{\textbf{y}}_k = \{y_p\}_{p=k}^{M+k-1}$.
-\eqref{eq:norm_cross_correlation} is now bounded by $[-1,1]$ and has any bias toward high energy removed.
+\eqref{eq:norm_cross_correlation} is now bounded by $[-1,1]$.
 We improve our computational efficiency by applying the convolution theorem to \eqref{eq:cross_correlation} and replacing it with:
@@
 We are most interested where our reference $\textbf{x}$ best matches our data $\textbf{y}$.
-We use the resulting max correlation to define our metric for  our matched-filter output as:
+We use the resulting max correlation as our metric for determining our matched-filter output as:
 %
@@
 Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
-Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on limited hardware resources.
-Sections \ref{sec:dim_red} and \ref{sec:decimation} will go into methods that will help reduce the computational burden of the matched-filter.
 \end{block}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Dimensionality Reduction %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{block}{\small{Dimensionality Reduction}}
-Classification methods that make use of multi-dimensional feature spaces have increased in popularity and many methods exist \cite{survey_multi_view_machine_learning}.
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
-Similar to other methods that apply subspace projections \cite{low_rank_subspace}, we seek to analyze our data in a lower dimensional subspace by a projection onto the two-dimension plane that best represents our data.
-We assume that over a short period of time, a user's limb movement is constrained mostly to a two-dimensional plane.
-By identifying this plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
-%
+We assume that over a short period of time, the user's limb movement is constrained mostly to a two-dimensional plane.
+We project the acceleration data onto this plane and re-define our new axis accordingly.
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (where each $a_i$ is represented as a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
@@
 We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{eq:project}.
-If the data is mostly dominate in the two primary dimensions, i.e.
-$\lambda^3 << \lambda^2$, then it is safe to assume that
-%
-\begin{equation} \label{eq:magnitude}
-||(a_x,a_y,a_z)||^2 = ||(a'^1,a'^2,a'^3)||^2 \sim = (a'^1)^2 + (a'^2)^2
-\end{equation}
-$ \forall a \in \textbf{a}. $ \\
-%
-Where equality comes from the orthonormality of $V$.
-By now, we have preserved as much information that is contained in our acceleration data as possible in the process of reducing our dimensions from three to two.
-
-In this paper, we compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter} by augmenting our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
+We compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter}.
+We augment our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:
 %
@@
 %
-This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
 Here, the superscripts $1$ and $2$ represent the primary and secondary principal components of our data respectively.
-%
 \end{block}
 
+%%%%%%%%%%%%%%
+% Decimation %
+%%%%%%%%%%%%%%
 \begin{block}{\small{Decimation}}
@@
 Decimation is a process of reducing the sampling rate of the signal by filtering to mitigate any possible distortion effects due to aliasing followed by downsampling.
-Because real-time performance is important, we decimate our signal for the purpose of improving our throughput.
+Decimation helps improve processing throughput.
 
@@
 %
-The processing cost is reduced by only processing points in \eqref{eq:convolve} that we keep in \eqref{eq:downsample}.
 \end{block}
@@
 \end{textblock}
-
-%%
-%% Text block
-%%
 \begin{textblock}{17.3}(41,4)
 
+%%%%%%%%%%%%%%%%%%%%%%%
+% Training the Module %
+%%%%%%%%%%%%%%%%%%%%%%%
 \begin{block}{\small{Training the Module}}
-
 We are able to identify an individual's activity by matching the signal to a reference template.
-For our application, we develop a reference template for our matched-filter directly from the person's motion signature.
-We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.
+We develop a reference template for our matched-filter directly from a subset of the person's motion signature.
+The individual performs a specified activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
+For a given activity, we attempt to find the representative signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.
 

### 2016-10-25 mc_code/preprocessing/down_sample.c
Fixed downsampling routine.

@@ -22,12 +22,17 @@ int down_sample (float *data,
    for (k = 0; k < window ; k++) weights[k] *= norm;
 
    float val;
-   for (new_ind = 0, ind = 0; new_ind < N; ind += downsamp_fact, new_ind++)
+   for (new_ind = 0, ind = 0; new_ind < N-1; ind += downsamp_fact, new_ind++)
    {
       val = 0.0f;
       for (k = 0; k < window; k++) val += data[ind + k] * weights[k];
       data[new_ind] = val;
    }
+
+   norm = 1.0f / (0.5f * (float)(downsamp_fact * (downsamp_fact + 1)));
+   val = 0.0f;
+   for (k = 0; k < window/2; k++) val += data[ind + k] * weights[k];
+   data[new_ind] = val;
 
    return sampling_freq;
 }

### 2016-10-29 notes/poster/example.tex
Transfered contents to the new poster template.

--- 2016-09-30 notes/paper/paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage{blindtext}
-\usepackage{graphicx}
-\usepackage{subfig}
+\documentclass{sciposter}
+\usepackage{lipsum}
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multicol}
+\usepackage{graphicx,url}
 \usepackage[english]{babel}   
-\usepackage{pinyin}
-\usepackage{natbib}
-\usepackage{notoccite}
-\usepackage{amssymb}
-\usepackage{textcomp}
-\usepackage{floatrow}
-\usepackage{amsmath}
-%
+\usepackage[utf8]{inputenc}
+%\usepackage{fancybullets}
+\newtheorem{Def}{Definition}
+
+\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
+
+\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
+
+\institute 
+{College of Engineering and Computer Science\\
+California State University Northridge}
+
+\email{craig.euler@gmail.com}
+
 \begin{document}
-%
-% paper title
-\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
-%
-\author{Craig~Euler craig.euler@gmail.com, C.T.~Lin ct.lin@csun.edu,\\Bryan~Juarez bryan.juarez.974@my.csun.edu, Melissa~Flores melissa.flores.455@my.csun.edu\\College of Engineering and Computer Science\\California State University, Northridge}
-%
+\conference{{\bf IEEE 2016}, Anaheim CA December 19}
+
 \maketitle
-%
+
+%%% Begin of Multicols-Enviroment
+\begin{multicols}{3}
+
+%%%%%%%%%%%%
+% Abstract %
+%%%%%%%%%%%%
 \begin{abstract}
-Having information of a user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor the user\textquotesingle s activity and fitness.
-In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
+Having information of a user's activity can provide great use in modern-day devices such as ones that track and monitor the user's activity and fitness.
+We demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
 We also show the real-time processing capability of our algorithms on the MSP432P401R low-powered microcontroller.
@@
 Data decimation in time is an additional throughput enhancement that we apply early to our data.
-We make use of an instance-based learning algorithm to train the device to learn the individual\textquotesingle s motion patterns and store that information as activity templates for use in our matched-filter.
+We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity templates for use in our matched-filter.
 \end{abstract}
-%
+
+%%%%%%%%%%%%%%%%
+% Introduction %
+%%%%%%%%%%%%%%%%
 \section{Introduction}
-Various methods for activity classification using body-worn sensors exist.
-Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
-The use of the matched-filter method for classification has been studied in the past \cite{giannakis_tsatsanis_1990} and we seek to adopt this method for our use to identify an individual\textquotesingle s activity for the purpose of real-time processing on a low-powered micro-controller.
-The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
-In this paper, we use the MSP432 microcontroller for our timing results.
+We adopt the matched-filter method for classification to identify an individual's activity in real-time processing on a low-powered micro-controller.
+Our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller.
+Timing tests were performed on the MSP432 microcontroller.
 
-The algorithms described in this paper are used in two main modules: The activity classification module for real-time processing and the training module to train the device to identify the user\textquotesingle s activity.
+Two main algorithms are described here: The activity classification module for real-time processing and the training module to train the device to identify the user's activity for the purpose of real-time activity classification.
 
-The training module does not need to be performed in real time.
-This algorithm is the most demanding on computational resources and is only executed when training or re-training the unit to identify the user\textquotesingle s activity, which means that this can be performed on an external device such as a smart phone or tablet.
-The purpose of the training module is to create the reference signals to be used on the microcontroller for the real-time activity classification processing.
+Because training module does not need to be performed in real time, this can be performed on an external device such as a smart phone or tablet where processing resources are in greater abundance.
+Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.
 
-The real-time activity classification module is intended to be performed on a low-powered microcontroller.
-This module reads in the references stored on the unit to be used as templates that the matched-filter will use for determining the individual\textquotesingle s activity.
-Both of these modules use the same principles and hence the same algorithm kernels.
-%
-\section{The Methodology}
-%
-\subsection{Activity Classification Method}
-The matched-filter method is commonly used for extracting a signal out of noisy data.
-We use this method for identifying a user\textquotesingle s activity from data generated by body-worn accelerometers.
-Because the matched-filter method requires use of an existing reference template to identify the desired signal, we must develop our template from a training set.
-We will discuss how we develop our set of templates for use in our matched-filter in section \ref{sec:training}.
-
+%%%%%%%%%%%%%%%
+% Methodology %
+%%%%%%%%%%%%%%%
+\section{Methodology}
+We use the matched-filter method for identifying a user's activity from data generated by body-worn accelerometers.
 The matched-filter is based on the cross correlation of the data $\textbf{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\textbf{x} = \{x\}_{k=0}^{M-1}$.
@@
 Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
-Despite this reduction in processing cost, the FFTs are still an expensive algorithm for real-time processing on limited hardware resources.
-Sections \ref{sec:dim_red} and \ref{sec:decimation} will go into methods that will help reduce the computational burden of the matched-filter.
-%
-\subsection{Dimensionality Reduction} \label{sec:dim_red}
-Classification methods that make use of multi-dimensional feature spaces have increased in popularity and many methods exist \cite{survey_multi_view_machine_learning}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Dimensionality Reduction %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Dimensionality Reduction}
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
-Similar to other methods that apply subspace projections \cite{low_rank_subspace}, we seek to analyze our data in a lower dimensional subspace by a projection onto the two-dimension plane that best represents our data.
-We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
-By identifying this plane of motion, we then project the acceleration data onto this plane and re-define our new axis accordingly.
-
+We assume that over a short period of time, the user's limb movement is constrained mostly to a two-dimensional plane.
+We project the acceleration data onto this plane and re-define our new axis accordingly.
 If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (where each $a_i$ is represented as a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
@@
 Here, we use superscripts to identify the axis directions in ascending order to represent the primary, secondary, and tertiary principal axis directions respectively.
-% \ref{bishop_2006}
+%
 \begin{equation} \label{eq:project}
@@
 %
-This works because both dimensions are always in phase with each other for any given activity and therefore the match will happen in sync.
 Here, the superscripts $1$ and $2$ represent the primary and secondary principal components of our data respectively.
-%
-\subsection{Decimation} \label{sec:decimation}
+
+%%%%%%%%%%%%%%
+% Decimation %
+%%%%%%%%%%%%%%
+\section{Decimation}
 Decimation is the first step applied to our data before any additional processing takes place.
 Decimation is a process of reducing the sampling rate of the signal by filtering to mitigate any possible distortion effects due to aliasing followed by downsampling.
-Because real-time performance is important, we decimate our signal for the purpose of improving our throughput.
+Decimation helps improve processing throughput.
 
@@
 \end{equation}
-%
-The processing cost is reduced by only processing points in \eqref{eq:convolve} that we keep in \eqref{eq:downsample}.
-%
-\subsection{Training the Module} \label{sec:training}
-We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
-For our application, we develop a reference template for our matched-filter directly from the person\textquotesingle s motion signature.
-We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
-For a given activity, we attempt to find the representative periodic signal $\textbf{s}$ of our individual\textquotesingle s activity to be our template for our matched-filter.
+
+%%%%%%%%%%%%%%%%%%%%%
+% Activity Training %
+%%%%%%%%%%%%%%%%%%%%%
+\section{Activity Training}
+We are able to identify an individual's activity by matching the signal to a reference template.
+We develop a reference template for our matched-filter directly from a subset of the person's motion signature.
+The individual performs a specified activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
+For a given activity, we attempt to find the representative signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.
 
@@
 We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
-%
-\section{Performance and Throughput}
-%
-\subsection{Algorithm Performance}
-%
+
+\begin{center}
+ \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
+\end{center}
+
+%%%%%%%%%%%%%%%
+% Performance %
+%%%%%%%%%%%%%%%
+\section{Performance}
 The Kinetisense sensor was used for the algorithm performance analysis in this paper.
@@
 %
-\begin{figure}[!ht]
-  %\captionsetup[subfigure]{labelformat=empty}
-  \centering
-  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
-  \quad
-  \centering
-  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
-  \centering
-  \quad
-  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
-  \centering
-  \quad
-  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
-  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
+%\begin{figure}[!ht]
+%  %\captionsetup[subfigure]{labelformat=empty}
+%  \centering
+%  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+%  \quad
+%  \centering
+%  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+%  \centering
+%  \quad
+%  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
+%  \centering
+%  \quad
+%  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
+%  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
 Results produced at decimation 8.
 Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
-  \label{fig:MF_performance}
-\end{figure}
+%  \label{fig:MF_performance}
+%\end{figure}
 
@@
 Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
-%
-%\FloatBarrier
-%
-\subsection{Throughput Performance}
-%
+
 To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
@@
 
-\begin{figure}[!ht]
-   \centering
-   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
-   \quad
-   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
-   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
+%\begin{figure}[!ht]
+%   \centering
+%   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
+%   \quad
+%   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
+%   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
 The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
-   \label{fig:timing}
-\end{figure}
+%   \label{fig:timing}
+%\end{figure}
 %
@@
 FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
-%
+
+%%%%%%%%%%%%%%
+% Conclusion %
+%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 
-%
-\appendices
-%
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-%
+%%%%%%%%%%%%%%
+% References %
+%%%%%%%%%%%%%%
 \bibliographystyle{plain}
 \bibliography{reference}
+
+\end{multicols}
+
 \end{document}

### 2016-10-29 notes/poster/example.tex
Incrimentals

@@
 \usepackage{multicol}
+\usepackage{subfig}
 \usepackage{graphicx,url}
@@
 
-\begin{center}
- \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
-\end{center}
-
 %%%%%%%%%%%%%%%
@@
 A separate instance of walking data was used specifically for training the classifier.
-%
-%\begin{figure}[!ht]
-%  %\captionsetup[subfigure]{labelformat=empty}
-%  \centering
-%  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
-%  \quad
-%  \centering
-%  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
-%  \centering
-%  \quad
-%  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
-%  \centering
-%  \quad
-%  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
-%  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
+
+\begin{figure}[!ht]
+
+\centering
+\subfigure[Jogging]{\includegraphics[width=0.35\textwidth]{fraction_threshold_walking_to_jogging.png}}
+\subfigure[Bicycling]{\includegraphics[width=0.35\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+
+\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
 Results produced at decimation 8.
 Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
-%  \label{fig:MF_performance}
-%\end{figure}
+  \label{fig:MF_performance}
+\end{figure}
 

### 2016-10-29 notes/poster/poster.tex
Misc comment removed.
Incrementals

@@
-\documentclass[unknownkeysallowed,final]{beamer}
-\usetheme{RJH} %RJH}
-\usepackage[orientation=landscape,size=a2,scale=1.4,debug]{beamerposter}
-\usepackage[absolute,overlay]{textpos}
-\setlength{\TPHorizModule}{1cm}
-\setlength{\TPVertModule}{1cm}
+\documentclass{sciposter}
+\usepackage{lipsum}
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multicol}
+\usepackage{subfig}
+\usepackage{graphicx,url}
+\usepackage[english]{babel}   
+\usepackage[utf8]{inputenc}
+%\usepackage{fancybullets}
+\newtheorem{Def}{Definition}
 
-\usepackage{amsmath,amsthm, amssymb, latexsym}
-\usepackage{multirow}
-\usepackage{rotating}
+\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
 
-\usepackage{array,booktabs,tabularx}
-\newcolumntype{Z}{>{\centering\arraybackslash}X} % centered tabularx columns
-\newcommand{\pphantom}{\textcolor{ta3aluminium}} % phantom introduces a vertical space in p formatted table columns??!!
-\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}
+\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
 
-% Poster size can be: 36" wide by 44" tall
+\institute 
+{College of Engineering and Computer Science\\
+California State University Northridge}
 
-\title{\normalsize{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}}
-\author{\small{Craig~Euler craig.euler@gmail.com, C.T.~Lin ct.lin@csun.edu,\\Bryan~Juarez bryan.juarez.974@my.csun.edu, Melissa~Flores melissa.flores.455@my.csun.edu\\College of Engineering and Computer Science\\California State University, Northridge}}
-
-\footer{}
-\date{}
+\email{craig.euler@gmail.com}
 
 \begin{document}
-\tiny{}
-\begin{frame}{}
+\conference{{\bf IEEE 2016}, Anaheim CA December 19}
 
-%%
-%% Text block
-%%
-\begin{textblock}{19.5}(1, 7)
+\maketitle
+
+%%% Begin of Multicols-Enviroment
+\begin{multicols}{3}
 
@@
 %%%%%%%%%%%%
-\begin{block}{\small{Abstract}}
+\begin{abstract}
 Having information of a user's activity can provide great use in modern-day devices such as ones that track and monitor the user's activity and fitness.
@@
 We make use of an instance-based learning algorithm to train the device to learn the individual's motion patterns and store that information as activity templates for use in our matched-filter.
-\end{block}
+\end{abstract}
 
@@
 %%%%%%%%%%%%%%%%
-\begin{block}{\small{Introduction}}
+\section{Introduction}
 We adopt the matched-filter method for classification to identify an individual's activity in real-time processing on a low-powered micro-controller.
@@
 Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.
-\end{block}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Activity Classification Method %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{block}{\small{Activity Classification Method}}
+%%%%%%%%%%%%%%%
+% Methodology %
+%%%%%%%%%%%%%%%
+\section{Methodology}
 We use the matched-filter method for identifying a user's activity from data generated by body-worn accelerometers.
@@
 Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
-\end{block}
-\end{textblock}
-
-\begin{textblock}{18}(21.8,4)
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{block}{\small{Dimensionality Reduction}}
+\section{Dimensionality Reduction}
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
@@
 Here, the superscripts $1$ and $2$ represent the primary and secondary principal components of our data respectively.
-\end{block}
 
@@
 %%%%%%%%%%%%%%
-\begin{block}{\small{Decimation}}
+\section{Decimation}
 Decimation is the first step applied to our data before any additional processing takes place.
@@
 \end{equation}
-%
-\end{block}
 
-\end{textblock}
-\begin{textblock}{17.3}(41,4)
-
-%%%%%%%%%%%%%%%%%%%%%%%
-% Training the Module %
-%%%%%%%%%%%%%%%%%%%%%%%
-\begin{block}{\small{Training the Module}}
+%%%%%%%%%%%%%%%%%%%%%
+% Activity Training %
+%%%%%%%%%%%%%%%%%%%%%
+\section{Activity Training}
 We are able to identify an individual's activity by matching the signal to a reference template.
@@
 
-%\begin{center}
-% \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
-%\end{center}
-\end{block}
+%%%%%%%%%%%%%%%
+% Performance %
+%%%%%%%%%%%%%%%
+\section{Performance}
+The Kinetisense sensor was used for the algorithm performance analysis in this paper.
+This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
+Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
+A separate instance of walking data was used specifically for training the classifier.
 
-\begin{block}{\small{Performance}}
-%The Kinetisense sensor was used for the algorithm performance analysis in this paper.
-%This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
-%Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
-%A separate instance of walking data was used specifically for training the classifier.
-%%
-%\begin{figure}[!ht]
-%  %\captionsetup[subfigure]{labelformat=empty}
-%  \centering
-%  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
-%  \quad
-%  \centering
-%  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
-%  \centering
-%  \quad
-%  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
-%  \centering
-%  \quad
-%  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
-%  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
+\begin{figure}[!ht]
+\centering
+\subfigure[Jogging]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+\subfigure[Bicycling]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
 Results produced at decimation 8.
 Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
-%  \label{fig:MF_performance}
-%\end{figure}
+  \label{fig:MF_performance}
+\end{figure}
+
+Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
+As we would expect, the walking data reference matches better to walking data than to the other activities.
+The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
+ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
+Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
+
+To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
+The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
+Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
+The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
+The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
+the 256 kB is more than enough flash memory to store the program and data references.
+The clock frequency operates at 48 MHz which drives the execution speed.
+
+The ``Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer'' oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
+When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
+This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-filtering (end of algorithm processing).
+The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
+An example can be seen in Figure \ref{fig:time_measure}.
+
+\begin{figure}[!ht]
+\centering
+\subfigure[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
+\subfigure[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
+\caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
+The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
+\label{fig:timing}
+\end{figure}
 %
-%Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
-%As we would expect, the walking data reference matches better to walking data than to the other activities.
-The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
-%ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
-%Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
-%
-%To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
-%The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
-%Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
-%The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
-%The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
-%the 256 kB is more than enough flash memory to store the program and data references.
-%The clock frequency operates at 48 MHz which drives the execution speed.
-%
-%\begin{figure}[!ht]
-%   \centering
-%   \includegraphics[width=0.45\textwidth]{reference_pulse_32Hz_4sec_8downsample_2.png}
-%   \caption{Oscilloscope output used for measuring the processing time of the algorithms on the MSP432.
-This is a case setup of 32Hz sampling frequency over a 4 second time window with 2 references at decimation 8 showing the voltage output over time.
-%Execution time is measured from start to end of the ``high'' (3.3 Volts) time interval.}
-%   \label{fig:time_measure}
-%\end{figure}
-%%
-%The ``Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer'' oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
-%When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
-%This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-filtering (end of algorithm processing).
-%The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
-%An example can be seen in Figure \ref{fig:time_measure}.
-%
-%\begin{figure}[!ht]
-%   \centering
-%   \subfloat[\label{fig:multiple_comparison}]{\includegraphics[width=0.45\textwidth]{more_time_plots.png}}
-%   \quad
-%   \subfloat[\label{fig:timing_refs}]{\includegraphics[width=0.45\textwidth]{one_and_two_references.png}}
-%   \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
-The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
-%   \label{fig:timing}
-%\end{figure}
-%%
-%The throughput performance was assessed on the MSP432 with varying parameters and randomized data.
-%This can be accomplished because the processing time is not affected by the data and this also simplifies this aspect of testing.
-%Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
-%Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
+The throughput performance was assessed on the MSP432 with varying parameters and randomized data.
+This can be accomplished because the processing time is not affected by the data and this also simplifies this aspect of testing.
+Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
+Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
 Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
-%Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
-%The processing that happens on the data before matched-filtering doesn't change the execution time with the number of references.
-%Therefore, one can observe that matched-filtering accounts for roughly $80$\% of the processing time.
-%%
-%\begin{figure}[!ht]
-%   \centering
-%   \includegraphics[width=0.99\textwidth]{flops_graph.png}
-%   \caption{An estimate of the processing distribution based on flop counts.
-This estimate was obtained from analyzing the source code that was used for the performance assessment.
-The cost of the FFT is based on the $2.5 N log_2 N$ mflops estimate for real-FFTs for FFTW \cite{FFTW} execution which was used for this performance assessment.
-A sampling rate of $128$ Hz with the matched-filter applied over a $4$ second time window and $1.5$ seconds of reference data was used.}
-%   \label{fig:flops_count}
-%\end{figure}
-%
-%An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
-%In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
-%Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
-%This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
-%FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
-\end{block}
-%
-\begin{block}{\small{Conclusion}}
-%We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
-%We have shown that real-time processing on a low-powered micro-controller can be achieved with timing results obtained from the MSP432 microcontroller.
-%Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFTs account for a significant amount of the processing time.
-%We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
-%The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
-\end{block}
-%
-\begin{block}{\small{References}}
+Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
+The processing that happens on the data before matched-filtering doesn't change the execution time with the number of references.
+Therefore, one can observe that matched-filtering accounts for roughly $80$\% of the processing time.
+
+An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
+In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
+Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
+This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
+FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
+
+%%%%%%%%%%%%%%
+% Conclusion %
+%%%%%%%%%%%%%%
+\section{Conclusion}
+We have demonstrated excellent activity classification capability of the matched-filter method using data obtained from a Kinetisense tri-axis accelerometer sensor.
+We have shown that real-time processing on a low-powered micro-controller can be achieved with timing results obtained from the MSP432 microcontroller.
+Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFTs account for a significant amount of the processing time.
+We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
+The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
+
+%%%%%%%%%%%%%%
+% References %
+%%%%%%%%%%%%%%
 \bibliographystyle{plain}
 \bibliography{reference}
-\end{block}
-\end{textblock}
 
-\end{frame}
+\end{multicols}
+
 \end{document}

### 2016-10-29 notes/poster/poster.tex
Incremental edits to the poster.

@@
 \section{Performance}
-The Kinetisense sensor was used for the algorithm performance analysis in this paper.
+The Kinetisense sensor was used for the algorithm performance analysis.
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
@@
 \centering
-\subfigure[Jogging]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
-\subfigure[Bicycling]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
-\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking.
-Results produced at decimation 8.
-Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
+\subfigure[\label{fig:frac_walking_jogging} Jogging]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
+\subfigure[\label{fig:frac_walking_bicycling} Bicycling]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
+\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8.}
   \label{fig:MF_performance}
@@
 Figures \ref{fig:frac_walking_jogging} and \ref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
-As we would expect, the walking data reference matches better to walking data than to the other activities.
-The tail in figure \ref{fig:frac_walking_jogging} is attributed to brief moments of walking that was recorded during the jogging data collection.
-ROC curves were produced from these corresponding results in figures \ref{fig:roc_walking_jogging} and \ref{fig:roc_walking_bicycling} to illustrate the effectiveness of the matched-filter as a classifier.
-Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from our classifier for bicycling.
 

### 2016-10-30 notes/poster/poster.tex
Incrimentals to the poster.

@@
 
-\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
+\title{{\fontsize{100}{120}\selectfont Real-Time Activity Classification by Matched Filtering Using Body-Worn Accelerometers}}
 
@@
 
-The ``Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer'' oscilloscope was used for measuring the timing of the algorithms on the microcontroller.
-When testing the execution speed, one of the General-Purpose Input/Output (GPIO) pins was connected to a Light-emitted diode (LED) that activates at 3.3 Volts (set high).
-This is activated immediately before the beginning of decimation (start of algorithm processing) and deactivated immediately at the end of the matched-filtering (end of algorithm processing).
-The execution time is then recorded on the oscilloscope to determine how long the GPIO was set high.
-An example can be seen in Figure \ref{fig:time_measure}.
-
 \begin{figure}[!ht]
@@
 %
-The throughput performance was assessed on the MSP432 with varying parameters and randomized data.
-This can be accomplished because the processing time is not affected by the data and this also simplifies this aspect of testing.
 Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
-Because the FFT dominates the processing load, and a custom FFT was written specifically for this unit and optimized for even-powered factors, one expects best throughput at radix 2 valued time-window lengths and sampling frequencies followed by other even-valued, non-radix 2, time-lengths and sampling frequencies.
-Both $62$Hz and $50$Hz have only one factor of $2$ hence the expectation that a sampling frequency of $62$Hz processing time is longer than that of the $50$Hz.
 Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
-The processing that happens on the data before matched-filtering doesn't change the execution time with the number of references.
-Therefore, one can observe that matched-filtering accounts for roughly $80$\% of the processing time.
-
-An assessment of the processing costs associated with each algorithm in the process was made as seen in figure \ref{fig:flops_count}.
-In addition, timing tests were done for comparison on an Intel i7-4500U 1.80 GHz processor.
-Processing time came out to $12.0$ micro-seconds for dimensionality reduction processing and $114.0$ micro-seconds for matched-filter processing on the remaining two dimensions.
-This proportion shows relative consistency with figure \ref{fig:flops_count} as we would expect.
-FFT calls account for the bulk of the processing distribution and are part of the main processing kernel for the matched-filtering process.
 

### 2016-11-05 notes/poster/poster.tex
Incrementals
Updates to the poster.

@@
 \newtheorem{Def}{Definition}
+
+% Poster size can be 36" wide by 44" tall (A0 paper size)
 
@@
 
-%%% Begin of Multicols-Enviroment
 \begin{multicols}{3}
@@
 
-Two main algorithms are described here: The activity classification module for real-time processing and the training module to train the device to identify the user's activity for the purpose of real-time activity classification.
+Two main algorithms are described here: Activity classification for real-time processing and training to train the device to identify the user's activity for the purpose of real-time activity classification.
 
@@
 \eqref{eq:norm_cross_correlation} is now bounded by $[-1,1]$.
-We improve our computational efficiency by applying the convolution theorem to \eqref{eq:cross_correlation} and replacing it with:
+We improve our computational efficiency from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$ by applying the convolution theorem to \eqref{eq:cross_correlation} and replacing it with:
 %
@@
 
-Applying the convolution theorem to $\eqref{eq:conv_theorem}$ changes the computational complexity or the cross correlation from $\mathcal{O}(n^2)$ to $\mathcal{O}(n log_2n)$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006}.
-We assume that over a short period of time, the user's limb movement is constrained mostly to a two-dimensional plane.
+We assume that over a short period of time, the user's limb movement is constrained mostly to two dimensions.
 We project the acceleration data onto this plane and re-define our new axis accordingly.
-If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (where each $a_i$ is represented as a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
+If we let $\textbf{a} = \{a_i\}_{i=0}^{N}$ represent our demeaned acceleration data (with each $a_i$ being a column) over a specified time window in three dimensions, then the covariance matrix of our acceleration data is represented by the real-symmetric $3 \times 3$ matrix $Q = \textbf{a} \textbf{a}^T$.
 The resulting unit length column eigenvectors of $Q$ are $V = (\textbf{v}^1,\textbf{v}^2,\textbf{v}^3)$ with their respective eigenvalues $\lambda^1 \geq \lambda^2 \geq \lambda^3$ of this matrix are orthonormal and point in the directions where the data varies most in descending order for each orthogonal direction.
@@
 We now represent our acceleration data as $\textbf{a}'$ after projecting our acceleration data $\textbf{a}$ onto our rotated axis $V$ by \eqref{eq:project}.
-We compute the matched-filter output for two dimensions by generalizing \eqref{eq:matched_filter}.
+We compute the matched-filter output by generalizing \eqref{eq:matched_filter} for two dimensions.
 We augment our reference and signal with both dimensions appropriately for normalization and adding together the cross correlations as:

### 2016-11-06 mc_code/training_example.c
Updated the number of training examples from 4 to 40.

@@ -18,7 +18,7 @@ int main()
    float *reference_x = (float*)malloc( 600 );
    float *reference_y = (float*)malloc( 600 );
    float *reference_z = (float*)malloc( 600 );
-   const int num_samples = 4;
+   const int num_samples = 40;
    void  *workspace = malloc( 200000 );
 
    /*

### 2016-11-07 notes/poster/poster.tex
Incrementals to poster.

@@
 We are able to identify an individual's activity by matching the signal to a reference template.
-We develop a reference template for our matched-filter directly from a subset of the person's motion signature.
-The individual performs a specified activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
+We develop our reference for our matched-filter directly from a subset of the person's motion signature.
+The individual performs a specified activity over a specified amount of time and we select the sub-interval of time that we find best represents the user's motion signature.
 For a given activity, we attempt to find the representative signal $\textbf{s}$ of our individual's activity to be our template for our matched-filter.
@@
 The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
-The 64 kB of SRAM provides sufficient space to process the results found in figure \ref{fig:timing} and
-the 256 kB is more than enough flash memory to store the program and data references.
-The clock frequency operates at 48 MHz which drives the execution speed.
+The 64 kB of SRAM provides sufficient space to process our algorithms.
+The 256 kB is more than enough flash memory to store the program and data references.
 

### 2016-11-14 notes/poster/poster.tex
Incrementals to the poster

@@
 
-Because training module does not need to be performed in real time, this can be performed on an external device such as a smart phone or tablet where processing resources are in greater abundance.
+Because training module does not need to be performed in real time, this can be done on an external device such as a smart phone or tablet where processing resources are in greater abundance.
 Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.
@@
 
-%%%%%%%%%%%%%%%
-% Performance %
-%%%%%%%%%%%%%%%
-\section{Performance}
-The Kinetisense sensor was used for the algorithm performance analysis.
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Performance Assessment %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Performance Assessment}
+The Kinetisense sensor was used for the algorithm performance assessment.
 This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.

### 2016-12-04 notes/poster/poster.tex
Updates to the poster.

@@
 We chose this method for its simplicity and robustness against outliers in our training set.
-We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
 
+\vfill
+\columnbreak
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
-A separate instance of walking data was used specifically for training the classifier.
+A separate instance of walking data was used for training the classifier.
 
@@
 
-To assess the real-time processing potential of the algorithms outlined in this paper, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
+To assess the real-time processing potential of the algorithms outlined, a throughput assessment was performed on the MSP432P401R microcontroller with varying parameters.
 The Texas Instruments - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor.
-Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, an IEEE 754-compliant single-precision Floating-Point Unit (FPU), and Memory Protection Unit (MPU).
-The single-precision processing capability on this unit provides us with the dynamic range necessary to process the algorithms that fixed-point processing cannot provide.
-The 64 kB of SRAM provides sufficient space to process our algorithms.
-The 256 kB is more than enough flash memory to store the program and data references.
+This controller has a clock frequency of 48 MHz, 64 kB SRAM which provides sufficient space for processing our algorithms, 256 kB Flash Memory to store the program and data, an IEEE 754-compliant single-precision Floating-Point Unit (FPU) that provides the dynamic range necessary to process the algorithms, and Memory Protection Unit (MPU).
 
@@
 \caption{Timing results with varying sampling frequencies, time-window lengths, and number of references used for the matched-filter on the MSP432 microcontroller processor.
+Figure (a) is the measured execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process at decimation $2$.
 The time window used for (b) is 4.0 seconds with timings measured at sampling frequencies of $16, 32, 62, 64, 75, 100,$ and $128$ Hz.}
@@
 %
-Figure \ref{fig:multiple_comparison} shows the execution time with varying time-window lengths and sampling frequencies while maintaining two references used in the matched-filter process while operating at decimation $2$.
-Figure \ref{fig:timing_refs} shows the execution time over a $4.0$ second time window at decimation $8$ while varying the sampling frequency and number of references.
 
@@
 Timing results have demonstrated that radix 2 time-window lengths and frequency values result in faster processing times as expected given that the FFTs account for a significant amount of the processing time.
-We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction, which reduced our computational requirements.
+We increased our throughput with the use of data-compression techniques, namely decimation and dimensionality reduction.
 The references used in the matched-filter are obtained from the training module where a training set is provided by the user through some specified activity and the best representative motion signature of the individual is extracted through the use of an instance-based learning algorithm.
